### 2017-06-07 draft.tex
First draft

\documentclass[a4paper,10pt, twocolumn]{article}

% Wider margins (compared to default)
\usepackage[margin=2.0cm]{geometry}

% For misc. computations
\usepackage{calc}
\usepackage{enumitem}

% English support (typography and hyphenation)
\usepackage[american]{babel}
\usepackage{csquotes}

% For math
\usepackage{amsmath}

% Unicode encoding
\usepackage[utf8]{inputenc}

% Color box
\usepackage{tikz,lipsum,lmodern}
\usepackage[most]{tcolorbox}

% Better default font (Libertine and Inconsolata)
% \usepackage[ttscale=.875]{libertine}
% \usepackage[scaled=0.96]{zi4}

\usepackage{mathspec}
\setmainfont{Minion Pro Cond}
\setmathsfont(Digits,Greek,Latin)[Numbers={Proportional}]{Minion Pro}
\setmathrm{Minion Pro}
\setsansfont{MyriadPro-Cond}

\usepackage{nicefrac}

% Biber
\usepackage[backend=biber,
            style=apa,
%            maxcitenames=3,
%            uniquelist=false,
%            maxbibnames=99,
%            apabackref=false,
            apamaxprtauth=99,
            natbib=true]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

% Graphics
\usepackage{graphicx}

% Figure caption
\usepackage[labelsep=period]{caption}
\renewcommand{\captionfont}{\small\sffamily}
\renewcommand{\captionlabelfont}{\small\sffamily\bfseries}

% Hyperref
\usepackage{xcolor}
\definecolor{blendedblue}{rgb}{0.2, 0.2, 0.6}
\definecolor{blendedred}{rgb}{0.8, 0.2, 0.2}
\usepackage[bookmarks=true,
            breaklinks=true,
            pdfborder={0 0 0},
            citecolor=blendedblue,
            colorlinks=true,
            linkcolor=blendedblue,
            urlcolor=blendedblue,
            citecolor=blendedblue,
            linktocpage=false,
            hyperindex=true,
            linkbordercolor=white]{hyperref}
\usepackage{hyperref}
\hypersetup{colorlinks=true}

% Bibliography file
\bibliography{article.bib}

% Headers
\usepackage{fancyhdr}
\pagestyle{fancy}
% \fancyhf{}
\rhead{\footnotesize \sf page \thepage}
\lhead{\footnotesize \sf Rougier et al. 2017
       \textbullet~The ReScience Initiative}
\rfoot{}
\cfoot{}
\lfoot{}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \textbf{\huge\@title\\}
  \vspace{5mm}
  \@author
\end{flushleft}\egroup
}
\makeatother

%% \newtcbox{\orcid}{enhanced,nobeforeafter,tcbox raise base,boxrule=0.4pt,top=0mm,bottom=0mm,
%%   right=0mm,left=4mm,arc=1pt,boxsep=2pt,before upper={\vphantom{dlg}},
%%   colframe=green!50!black,coltext=green!25!black,colback=green!10!white,
%%   overlay={\begin{tcbclipinterior}\fill[green!75!blue!50!white] (frame.south west)
%%     rectangle node[text=white,font=\sffamily\bfseries\tiny,rotate=0] {ID} ([xshift=4mm]frame.north west);\end{tcbclipinterior}}}

\usepackage{tikz}
\usetikzlibrary{positioning,shapes,shadows,arrows}
\newcommand{\orcid}[1]{
    \tikz[baseline=-0.5ex]{ 
        \tikzset{lib/.style={
            rectangle split,
            rectangle split parts=2,
            rectangle split horizontal,
            rectangle split part fill={green!75!blue!50!white,green!10!white},
            rectangle split draw splits=false,
            rounded corners=1pt,
            rectangle split part align={right,right},
            draw=green!50!black,
            minimum height=8pt}
        }
        \node[lib] (var){
        \nodepart[text=green!25!black]{two} \footnotesize \href{http://orcid.org/#1}{#1}};
        \node[text=white,font=\sffamily\bfseries\footnotesize,rotate=0] at ([xshift=6pt]var.west) {ID};
    }
}

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$,
  \textbf{Konrad Hinsen}$^{4,5}$,
  \textbf{Thomas Arildsen}$^{?}$,
  \textbf{Lorena Barba}$^{?}$,
  \textbf{Fabien Benureau}$^{?}$,
  \textbf{C. Titus Brown}$^{?}$,
  \textbf{Georgios Detorakis}$^{?}$,
  \textbf{Emmanuelle Gouillart}$^{?}$,
  \textbf{Pierre de Buyl}$^{?}$,
  \textbf{Benoît Girard}$^{?}$,
  \textbf{Olivia Guest}$^{?}$,
  \textbf{Mehdi Khamassi}$^{?}$,
  \textbf{Etienne Roesch}$^{?}$,
  \textbf{Joseph Stachelek}$^{?}$,
  \textbf{Owen Petchey}$^{?}$,
  \textbf{Timothée Poisot}$^{?}$,
  \textbf{Karthik Ram}$^{?}$,
  \textbf{Yoav Ram}$^{?}$
  \textbf{Federico Vaggi}$^{?}$,
  \textbf{Julien Vitay}$^{?}$,
  \textbf{Tiziano Zito}$^{?}$\\
  \begin{footnotesize}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France
    $^{2}$Institut des Maladies Neurodégénératives, Université de Bordeaux,
          CNRS, UMR 5293, Bordeaux, France
    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS, UMR 5800, Talence, France
    $^{4}$Centre de Biophysique Moléculaire,
          CNRS UPR4301, Orléans Cedex 2
    $^{5}$Synchrotron SOLEIL, Division Expériences,
          Gif sur Yvette, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}

\date{}

\begin{document}

\twocolumn[
\maketitle
\begin{small}
  \noindent
  \textbf{} \par
  \textbf{Keywords:} Open Science, Computational Science,
                     Reproducibility, Replicability
\end{small}
\vspace{10mm}
]

\section*{Introduction}
There is a replication crisis in Science. It has been recently highlighted in
medicine \citep{ioannidis:2005}, in psychology \citep{nosek:2015}, in
political sciences \citep{janz:2015} and even more recently in biomedical
sciences \citep{iqbal:2016}. The reasons for such non-reproducibility are as
diverse as these domains can be. In medicine, the {\em study power and bias, the
number of other studies on the same question, and, importantly, the ratio of
true to no relationships among the relationships probed in each scientific
field} are important criterion as reported by \citep{ioannidis:2005}. In psychology,
the infamous p-value seems to be the root of all evil while in biomedical
sciences, \citep{iqbal:2016} identified a {\em lack of access to full datasets and
detailed protocols for both clinical and non-clinical biomedical
investigation}. Surprisingly enough, computational sciences (in the broad
sense) and computer sciences are no exception even though they rely mostly on
code and data that are assumed to be not prone to the aforementioned
problems.\\

When \citep{collberg:2014, collberg:2015} decided to measure precisely the
extent of the problem, they investigated the availability of the code and data,
and {\em the extent to which this code would actually build with reasonable
  effort}. The results were dramatic: on the 515 potentially reproducible
papers (out of 613) targeted by the study, authors managed to ultimately run
only 102 of them. Less than 20\%. It is to be underlined that authors only
studied the possibility to run the code. They did not even check for the
correctness of the code (does the code actually implements what is advertised
in the paper) nor the replicability of the results (does the run lead to the
same results as in the paper).  \citep{topalidou:2015a} encountered the same
problem when they tried to replicate a model from the computational
neuroscience literature: source code were not part of the supplementary section
of the paper and no link nor repository were given in the main text. When they
finally get their hands on the code (after contacting the corresponding
author), it was only to realize it cannot be compiled and was mostly
unusable.\\

Confronted to the problem, a small but growing number of journals and
publishers have decided to react and have adopted explicit data and software
policies. See for example the Plos
\href{http://journals.plos.org/plosone/s/materials-and-software-sharing}{Materials
  and Software Sharing} and
\href{http://journals.plos.org/plosone/s/data-availability}{Data Availability}
or the
\href{https://elifesciences.org/elife-news/inside-elife-forking-software-used-elife-papers-github}{recent
  annoucement} by eLife on forking software used in eLife papers to GitHub.
Such policy will guarantee access to code and data in a proper format
\citep{perkel:2016} but this won't guarantee reproducilbility nor
correctness. At the educational level, things have started to change with a
growing literature on best practices for making code reproducible
\citep{sandve:2013, crook:2013, wilson:2014, halchenko:2015, janz:2015,
  hinsen:2015}. Original initiative such as software and data carpentry
\citep{wilson:2016} are worth to be mentionned since their goal is {\em to make
  scientists more productive, and their work more reliable, by teaching them
  basic computing skills}. Obviously, such best practices could be as well
applied to already published research software or code, provided the original
author(s) is willing to take the challenge of re-implementing his/her own
software for the sake of Science. This is unlikely since, unfortunately, the
incentives for doing such a time-consuming task are low or nonexistent.
Furthermore, if the original author did some mistake in his/her original
implementation, chances are that he/she'll reproduce the same mistake over and
over again (just an educated guess, we have no data supporting this
assertion).\\

%% At this point, the question is what do we do? Do we have to declare
%% the research to be lost once and for all because the associated software or
%% code is nowhere to be found / lost / damaged / malfunctioning / not runnable /
%% not usable / does not give original results / etc. We would doom ourselves by
%% doing so

% As you may have guessed by now, this was the main motivation for
 %the creation of the ReScience journal\citep{^2].

\section*{Reproducibility is harder than you think}

\citeauthor{Mesnard:2016} explains in \citep{Mesnard:2016} that writing
reproducible and replicable computational fluid dynamics simulation is harder
than you think. In fact, there are several different reasons for
non-reproducibility that, for the most part, largely depends on the specific
scientifc domain. However, from our publishing experience, there are also some
common behaviors that can be identified. Missing code and/or data, unknown
dependencies, inaccurate or imprecise description appears to be shared
characteristics of a lot of work.\\

To be extended...

\section*{The ReScience initiative}

Writing a replication might be a daunting task that is usually hardly or not
rewarded. Nevertheless, some people are actually willing to replicate
computational research. The motivation for doing so is very diverse and range
from the simple student who want to train oneself in order to get familiar with
a specific scientific domain up to the senior researcher that has a critical
need of a specific piece of code (see Box 1). If these people write a brand new
open source implementation of some published research, chances are this new
implementation may be of great interest for other people as well, includign
original authors. The question is where to publish such replication. To the
best of our knowledge, no journal would accept to publish a single successful
replication in computational science. This has been the main motivation for the
creation of the ReScience journal (\url{rescience.github.io}) by Konrad Hinsen
and Nicolas Rougier in 2015.\\

\begin{tcolorbox}[breakable, pad at break*=1mm,
                  colback=black!2.5, arc=0pt, outer arc=0pt, boxrule=0pt]
\begin{footnotesize}
\textbf{Box 1.} Authors having  published in Rescience explain their motivation.\\

\textbf{(\cite{stachelek:2016})} I was motivated to replicate the results of
the original paper because I feel that working through code supplements to blog
posts has really helped me learn how to science. I could have published my
replication as a blog post but I wanted the exposure and permanency that goes
along with journal articles. This was my first experience with formal
replication. I think the review was useful because it forced me to consider how
the replication would be used by people other than myself. I have not yet
experienced any new interactions following publication. However, I did notify
the author of the original implementation about the replication's
publication. I think this may lead to future correspondence. The original
author suggested that he would consider submitting his own replications to
ReScience in the future.\\

\textbf{(\cite{topalidou:2015b})} Our initial motivation and the main reason
for replicating the model is that we needed it in order to collaborate with our
neurobiologist colleagues. When we arrived in our new lab, the model has just
been published (2013) but the original author left the lab a few months before
our arrival. There were no public repository, no version control and the paper
describing the model was incomplete and partly inaccurate. We managed to get
our hands on the original sources (6,000 lines of Delphi) only to realize we
could not compile them. It took us three months to replicate it using 250 lines
of Python. But at this time, there were no place to publish this kind of
replication and share the new code with colleagues. Since then, we have refined
the model and made new predictions that have been confirmed. Our initial
replication effort really gave the model a second life.\\

\textbf{(\cite{viejo:2016})} Replicating previous work is a relatively routine
task every time we want to build a new model: either because we want to build
on it, or because we want to compare to it. We also give replication tasks to
M.Sc. students every year, as projects. In all these cases, we are confronted
to incomplete or inaccurate model descriptions, as well as to the impossibility
to obtain the original results. Contacting the original authors sometimes
solves the problem, but not so often (because of the {\em dog ate my hard
  drive} syndrom). We thus accumulate knowledge, internal to the lab, about
which model work, which doesn't, and how a given model has to be parameterized
to really work. Without any place to publish it, this knowledge is
wasted. Publishing it in ReScience, opening the discussion publicly, will be a
progress for all of us. \par
\end{footnotesize}
\end{tcolorbox}

ReScience is an open peer-reviewed journal that targets computational research
and encourages the explicit replication of already published research,
promoting new and open-source implementations in order to ensure that the
original research is reproducible. In less than two years of existence, 12
articles have been published and 3 are currently under review
(\href{https://github.com/ReScience/ReScience-submission/pull/20}{\#20},
\href{https://github.com/ReScience/ReScience-submission/pull/27}{\#27},
\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#30}). The
editorial board covers a wide range of computational sciences (see
\url{http://rescience.github.io/board/}) and there are more than 70 registered
reviewers that have volunteered. The computational domains of published work
are in computational neuroscience, neuroimaging, computational ecology and
computer graphics with a majority in computational neuroscience. There is a
strong bias in favor of successful replication (100\%) and experience has
taught us researcher are reluctant to publish a failed replication (even when
there is a way to prove the original work is wrong). For a young researcher,
there is a social/professional risk in publishing an article where he/she shows
that the results from a senior researcher are wrong. Until we implement a
certified anonymized submission process, this strong bias will most likely
remain.\\

One of the specificity of the ReScience journal is its publishing chain that is
radically different from any other traditional scientific journals since
ReScience lives on GitHub. Each submission takes the form of a pull request
that is first considered by a member of the editorial board, who may decide to
reject the submission, or assign it to two reviewers for further review and
tests. The reviewers evaluate the code and the accompanying material in
continuous interaction with the authors through the discussion section. If both
reviewers managed to run the code and obtain the same results as the ones
advertised in the accompanying material, the submission is
accepted. Furthermore, an author cannot submit a replication of his/her own
research, nor the research of close collaborators. Mistakes in the
implementation of research questions and methods are often due to biases
authors invariably have, consciously or not. One's biases will inevitably carry
over to how one approaches a replication. Perhaps even more importantly, this
aims at the cross-fertilization of research and trying to replicate the work of
one’s peers might pave the way for a future collaboration, or may give rise to
new ideas as a result of the replication effort.\\

The main criterion for acceptation is the actual replication of the research
with a clear statement by the authors explaining why they think they have
replicated the paper (same figures, same graphics, same behavior,
etc.). However, the clarity of the code is an important criterion because
uncommented or obfuscated code is as bad as no code at all. A code without the
accompanying article is also a criterion for rejection since we’re not human
compilers (well not all of us at least). The role of the reviewer is thus to
ensure the proposed submission is actually replicable. This means:
%
\begin{itemize}
\item One should be able to run the proposed implementation on hi/her computer
\item One should obtain the same results as indicated in the accompanying paper
\item These results must correspond to the original paper
\end{itemize}
%
The goal of the review is thus to help the author to meet ReScience quality
standards through discussion. More specifically, since ReScience targets
replication of original research, there is no need to judge the relevance or
novelty of the research. The review concentrates on how easy it would be for
another researcher to run the proposed implementation. This should be viewed in
light of the standards in the field. If a given tool/library/software is
mainstream in a field, it is ok to use them, but if a brand new standalone
implementation is proposed, this must not rejected on this criterion.

%% It has been said many times by many authors in the litterature that
%% reproducibility is the cornerstone of Science and we, as a scientific
%% community, should aim at such reproducibility. However, good intention are not
%% sufficient and a given computational results can be declared reproducible if
%% and only if it has been actually replicated in a the sense of a brand new
%% open-source and documented implementation.

%% ReScience already published 4 articles and as shown above, the original
%% motivations of these authors are all different and this might become even more
%% obvious and diverse with future publications. But, beyond these motivations,
%% publishing in ReScience may be especially important for students since this
%% represent a unique opportunity to show the community a given student is able to
%% read a scientific article, to have a deep understanding of it, to write a new
%% implementation and to eventually write a scientific article describing his/her
%% work. Although the ReScience publishing model is a bit different from other
%% academic journals, it can give students a first experience at peer-reviewed
%% scholarly publishing, including meeting standards of scientific rigor and
%% addressing reviewers' comments.  Furthermore, publishing in ReScience is a way
%% to actively contribute to open science while adding to one's publication
%% record.

%\Discussion*{Discussion}
%\subsection*{An Utopia for Tomorrow}

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{CoScience}
  \caption{\textbf{A} The ReScience publication chain starts from an original
    research by authors A, published in a journal, in proceedings or as a
    preprint. This article constitutes the base material for authors B that
    will attempt to replicate the work based on its description. Success or
    failure to replicate is not a criterion for rejection even though failure
    to replicate will requires more precaution to ensure this is not a
    misunderstanding or a bug in the new code. After review and once published,
    a feedback is given to original author and editor to inform them the work
    has been replicated (or not). \textbf{B} The CoScience proposal would
    require for the replication to happen before the actual publication. In
    case of failure, nothing will be published, in case of success, the
    publication will be endorsed by authors A and authors B with identified
    roles and will be certified as reproducible because it has beenactually
    replicated by an independent group.}
\end{figure}

\section*{Discussion}

% -> Short-term vs long-term reproducibility
The code accompanying a ReScience replication ensures only a short term
reproducibility. Even if a piece of code is written enforcing best practices,
is reviewed and tested, it suffers from the same problem as any other piece of
code, i.e. it depends on a software stack whose stability is not guaranteed in
the long term. \citep{Mesnard:2016} illustrated this problem very clearly when
they tried to reproduce their own work two years apart. Even though Barba's
group is committed to reproducible software, they did not escape the many
problems one can face when trying to re-run a piece of code. This means the
newly produced code for ReScience will be deprecated at some point in the
future. It can be a matter of months or years (or even decades), but in the
end, it will be deprecated. However, the long-term value of a ReScience
publication is not the actual code but the accompanying article. If you
consider the original article with missing or incomplete information and the
new article with missing and checked information, you have a complete and
consistent description of the original work. This means than 5, 10 or 20 years
from now, one should be able to replicate the work thanks to these two
articles. Of course, the new code can also help, but the true value of a
replication is the accompanying article.

% -> Long term storage: Software Heritage

% -> Computational vs Experimental: ReScience X (Etienne Roesch)

% -> Post vs Pre replication: CoScience, an utopia for tomorrow

% -------------------------------------------------------------- References ---
\renewcommand*{\bibfont}{\footnotesize}
\printbibliography[title=References]

\end{document}

### 2017-06-07 draft.tex
Revision (spelling, grammar, style, ...)

@@
 \section*{Introduction}
-There is a replication crisis in Science. It has been recently highlighted in
-medicine \citep{ioannidis:2005}, in psychology \citep{nosek:2015}, in
-political sciences \citep{janz:2015} and even more recently in biomedical
+There is a replication crisis in Science. It has recently been highlighted in
+medicine \citep{ioannidis:2005}, psychology \citep{nosek:2015}, the
+political sciences \citep{janz:2015}, and even more recently in the biomedical
 sciences \citep{iqbal:2016}. The reasons for such non-reproducibility are as
-diverse as these domains can be. In medicine, the {\em study power and bias, the
+diverse as these domains are. In medicine, the {\em study power and bias, the
 number of other studies on the same question, and, importantly, the ratio of
 true to no relationships among the relationships probed in each scientific
-field} are important criterion as reported by \citep{ioannidis:2005}. In psychology,
-the infamous p-value seems to be the root of all evil while in biomedical
+field} are important causes, as reported by \citep{ioannidis:2005}. In psychology,
+the infamous p-value seems to be the root of all evil, while in the biomedical
 sciences, \citep{iqbal:2016} identified a {\em lack of access to full datasets and
 detailed protocols for both clinical and non-clinical biomedical
-investigation}. Surprisingly enough, computational sciences (in the broad
-sense) and computer sciences are no exception even though they rely mostly on
-code and data that are assumed to be not prone to the aforementioned
+investigation}. Surprisingly enough, the computational sciences (in the broad
+sense) and computer sciences are no exception, even though they rely mostly on
+code and data that are believed to be not prone to the aforementioned
 problems.\\
 
-When \citep{collberg:2014, collberg:2015} decided to measure precisely the
-extent of the problem, they investigated the availability of the code and data,
+When \citep{collberg:2014, collberg:2015} decided to measure the
+extent of the problem precisely, they investigated the availability of code and data,
 and {\em the extent to which this code would actually build with reasonable
-  effort}. The results were dramatic: on the 515 potentially reproducible
-papers (out of 613) targeted by the study, authors managed to ultimately run
-only 102 of them. Less than 20\%. It is to be underlined that authors only
-studied the possibility to run the code. They did not even check for the
-correctness of the code (does the code actually implements what is advertised
-in the paper) nor the replicability of the results (does the run lead to the
+  effort}. The results were dramatic: of the 515 potentially reproducible
+papers (out of 613) targeted by the study, the authors managed to ultimately run
+only 102, i.e. less than 20\%. It is to be underlined that the authors only
+investigated the possibility to run the code. They did not check for the
+correctness of the code (does the code actually implement what is advertised
+in the paper), nor the replicability of the results (does the run lead to the
 same results as in the paper).  \citep{topalidou:2015a} encountered the same
 problem when they tried to replicate a model from the computational
-neuroscience literature: source code were not part of the supplementary section
-of the paper and no link nor repository were given in the main text. When they
-finally get their hands on the code (after contacting the corresponding
-author), it was only to realize it cannot be compiled and was mostly
+neuroscience literature: source code was not part of the supplementary section
+of the paper and no link or repository was provided in the main text. When they
+finally got their hands on the code, after contacting the corresponding
+author, it was only to realize that it could not be compiled and was mostly
 unusable.\\
 
-Confronted to the problem, a small but growing number of journals and
+Confronted with this problem, a small but growing number of journals and
 publishers have decided to react and have adopted explicit data and software
-policies. See for example the Plos
+policies. See for example the PLOS instructions on
 \href{http://journals.plos.org/plosone/s/materials-and-software-sharing}{Materials
   and Software Sharing} and
-\href{http://journals.plos.org/plosone/s/data-availability}{Data Availability}
+on \href{http://journals.plos.org/plosone/s/data-availability}{Data Availability},
 or the
@@
   annoucement} by eLife on forking software used in eLife papers to GitHub.
-Such policy will guarantee access to code and data in a proper format
-\citep{perkel:2016} but this won't guarantee reproducilbility nor
+Such policies will ensure access to code and data in a well-defined format
+\citep{perkel:2016} but this will not guarantee reproducilbility, nor
 correctness. At the educational level, things have started to change with a
@@
 \citep{sandve:2013, crook:2013, wilson:2014, halchenko:2015, janz:2015,
-  hinsen:2015}. Original initiative such as software and data carpentry
-\citep{wilson:2016} are worth to be mentionned since their goal is {\em to make
+  hinsen:2015}. Original initiatives such as Software and Data Carpentry
+\citep{wilson:2016} are worth mentioning since their goal is {\em to make
   scientists more productive, and their work more reliable, by teaching them
-  basic computing skills}. Obviously, such best practices could be as well
-applied to already published research software or code, provided the original
-author(s) is willing to take the challenge of re-implementing his/her own
-software for the sake of Science. This is unlikely since, unfortunately, the
-incentives for doing such a time-consuming task are low or nonexistent.
-Furthermore, if the original author did some mistake in his/her original
-implementation, chances are that he/she'll reproduce the same mistake over and
-over again (just an educated guess, we have no data supporting this
+  basic computing skills}. Obviously, such best practices could be applied as well to already published research software or code, provided the original
+authors are willing to take on the challenge of re-implementing their own
+software for the sake of better science. This is unlikely since, unfortunately, the
+incentives for doing such time-consuming work are low or nonexistent.
+Furthermore, if the original authors made mistakes in their original
+implementation, chances are that they will reproduce the same mistakes again (just an educated guess, we have no data supporting this
 assertion).\\
@@
 
-\citeauthor{Mesnard:2016} explains in \citep{Mesnard:2016} that writing
-reproducible and replicable computational fluid dynamics simulation is harder
+\citeauthor{Mesnard:2016} explains in \citep{Mesnard:2016} that performing
+reproducible and replicable simulations in computational fluid dynamics is harder
 than you think. In fact, there are several different reasons for
-non-reproducibility that, for the most part, largely depends on the specific
+non-reproducibility that, for the most part, are specific to each
 scientifc domain. However, from our publishing experience, there are also some
@@
 dependencies, inaccurate or imprecise description appears to be shared
-characteristics of a lot of work.\\
+characteristic of a lot of non-reproducible work.\\
 
@@
 
-Writing a replication might be a daunting task that is usually hardly or not
-rewarded. Nevertheless, some people are actually willing to replicate
-computational research. The motivation for doing so is very diverse and range
-from the simple student who want to train oneself in order to get familiar with
-a specific scientific domain up to the senior researcher that has a critical
-need of a specific piece of code (see Box 1). If these people write a brand new
-open source implementation of some published research, chances are this new
-implementation may be of great interest for other people as well, includign
-original authors. The question is where to publish such replication. To the
-best of our knowledge, no journal would accept to publish a single successful
+Writing a replication is a daunting task that is traditionally hardly or not
+at all rewarded. Nevertheless, some people are actually willing to replicate
+computational research. The motivations for doing so are very diverse (see Box 1). Students may want familiarize themselves with
+a specific scientific domain, and acquire relevant practical experience by replicating important published work. Senior researchers may critically
+need a specific piece of code for a research project and therefore re-implement a published computational method. If these people write a brand new
+open source implementation of already published research, chances are that this new
+implementation may be of great interest for other people as well, including
+the original authors. The question is where to publish such a replication. To the
+best of our knowledge, no major journal would accept to publish a single successful
 replication in computational science. This has been the main motivation for the
@@
 for replicating the model is that we needed it in order to collaborate with our
-neurobiologist colleagues. When we arrived in our new lab, the model has just
-been published (2013) but the original author left the lab a few months before
-our arrival. There were no public repository, no version control and the paper
+neurobiologist colleagues. When we arrived in our new lab, the model had just
+been published (2013) but the original author had left the lab a few months before
+our arrival. There was no public repository nor version control, and the paper
 describing the model was incomplete and partly inaccurate. We managed to get
@@
 could not compile them. It took us three months to replicate it using 250 lines
-of Python. But at this time, there were no place to publish this kind of
-replication and share the new code with colleagues. Since then, we have refined
+of Python. But at this time, there was no place to publish this kind of
+replication to share the new code with colleagues. Since then, we have refined
 the model and made new predictions that have been confirmed. Our initial
@@
 M.Sc. students every year, as projects. In all these cases, we are confronted
-to incomplete or inaccurate model descriptions, as well as to the impossibility
+with incomplete or inaccurate model descriptions, as well as with the impossibility
 to obtain the original results. Contacting the original authors sometimes
@@
   drive} syndrom). We thus accumulate knowledge, internal to the lab, about
-which model work, which doesn't, and how a given model has to be parameterized
+which model works and which doesn't, and how a given model has to be parameterized
 to really work. Without any place to publish it, this knowledge is
@@
 editorial board covers a wide range of computational sciences (see
-\url{http://rescience.github.io/board/}) and there are more than 70 registered
-reviewers that have volunteered. The computational domains of published work
+\url{http://rescience.github.io/board/}) and more than 70 volunteers have registered to be reviewers. The computational domains of published work
 are in computational neuroscience, neuroimaging, computational ecology and
 computer graphics with a majority in computational neuroscience. There is a
-strong bias in favor of successful replication (100\%) and experience has
-taught us researcher are reluctant to publish a failed replication (even when
-there is a way to prove the original work is wrong). For a young researcher,
-there is a social/professional risk in publishing an article where he/she shows
-that the results from a senior researcher are wrong. Until we implement a
+strong bias towards successful replication (100\%) and experience has
+taught us that researchers are reluctant to publish failed replications, even when they can prove that the original work is wrong. For young researchers,
+there is a social/professional risk in publishing articles that show
+results from a senior researcher to be wrong. Until we implement a
 certified anonymized submission process, this strong bias will most likely
@@
 
-One of the specificity of the ReScience journal is its publishing chain that is
+One of the specificities of the ReScience journal is its publishing chain that is
 radically different from any other traditional scientific journals since
@@
 continuous interaction with the authors through the discussion section. If both
-reviewers managed to run the code and obtain the same results as the ones
+reviewers manage to run the code and obtain the same results as the ones
 advertised in the accompanying material, the submission is
@@
 implementation of research questions and methods are often due to biases
-authors invariably have, consciously or not. One's biases will inevitably carry
-over to how one approaches a replication. Perhaps even more importantly, this
-aims at the cross-fertilization of research and trying to replicate the work of
+authors invariably have, consciously or not. Such biases will inevitably carry
+over to how one approaches a replication. Perhaps even more importantly, 
+cross-fertilization is generally useful in research, and trying to replicate the work of
 one’s peers might pave the way for a future collaboration, or may give rise to
@@
 replicated the paper (same figures, same graphics, same behavior,
-etc.). However, the clarity of the code is an important criterion because
-uncommented or obfuscated code is as bad as no code at all. A code without the
+etc.). However, the clarity of the code is an important criterion as well because
+uncommented or obfuscated code is no better than no code at all. A code without an
 accompanying article is also a criterion for rejection since we’re not human
 compilers (well not all of us at least). The role of the reviewer is thus to
-ensure the proposed submission is actually replicable. This means:
+ensure that the proposed submission is actually replicable. This means:
 %
 \begin{itemize}
-\item One should be able to run the proposed implementation on hi/her computer
-\item One should obtain the same results as indicated in the accompanying paper
-\item These results must correspond to the original paper
+\item They are able to run the proposed implementation on their computers.
+\item They obtain the same results as indicated in the accompanying paper.
+\item These results are sufficiently close to the ones reported in the original paper being replicated.
 \end{itemize}
 %
-The goal of the review is thus to help the author to meet ReScience quality
+The goal of the review is thus to help the author to meet the ReScience quality
 standards through discussion. More specifically, since ReScience targets
@@
   \includegraphics[width=1.0\columnwidth]{CoScience}
-  \caption{\textbf{A} The ReScience publication chain starts from an original
-    research by authors A, published in a journal, in proceedings or as a
-    preprint. This article constitutes the base material for authors B that
-    will attempt to replicate the work based on its description. Success or
-    failure to replicate is not a criterion for rejection even though failure
-    to replicate will requires more precaution to ensure this is not a
-    misunderstanding or a bug in the new code. After review and once published,
-    a feedback is given to original author and editor to inform them the work
-    has been replicated (or not). \textbf{B} The CoScience proposal would
-    require for the replication to happen before the actual publication. In
-    case of failure, nothing will be published, in case of success, the
-    publication will be endorsed by authors A and authors B with identified
-    roles and will be certified as reproducible because it has beenactually
-    replicated by an independent group.}
+  \caption{\textbf{A} The ReScience publication chain starts from an
+    original research by authors A, published in a journal, in
+    conference proceedings, or as a preprint. This article constitutes
+    the base material for authors B who attempt to replicate the work
+    based on its description. Success or failure to replicate is not a
+    criterion for acceptance or rejection, even though failure to
+    replicate requires more precaution to ensure this is not a
+    misunderstanding or a bug in the new code. After review, the
+    replication is published, and feedback is given to original
+    authors (and editors) to inform them the work has been replicated
+    (or not). \textbf{B} The CoScience proposal would require the
+    replication to happen \textit{before} the actual publication. In
+    case of failure, nothing will be published. In case of success,
+    the publication will be endorsed by authors A and authors B with
+    identified roles and will be certified as reproducible because it
+    has been replicated by an independent group.}
 \end{figure}
@@
 % -> Short-term vs long-term reproducibility
-The code accompanying a ReScience replication ensures only a short term
-reproducibility. Even if a piece of code is written enforcing best practices,
-is reviewed and tested, it suffers from the same problem as any other piece of
+The code accompanying a ReScience replication ensures only short-term
+reproducibility. Even if a piece of code is written following best practices,
+and then reviewed and tested, it suffers from the same problem as any other piece of
 code, i.e. it depends on a software stack whose stability is not guaranteed in
 the long term. \citep{Mesnard:2016} illustrated this problem very clearly when
-they tried to reproduce their own work two years apart. Even though Barba's
-group is committed to reproducible software, they did not escape the many
+they tried to reproduce their own work performed two years earlier. Even though Barba's
+group is committed to reproducible research practices, they did not escape the many
 problems one can face when trying to re-run a piece of code. This means the
-newly produced code for ReScience will be deprecated at some point in the
-future. It can be a matter of months or years (or even decades), but in the
-end, it will be deprecated. However, the long-term value of a ReScience
+newly produced code for ReScience will likely be obsolete at some point in the
+future. It can be a matter of months or years, or even decades, but ultimately, obsolescence is inevitable. Therefore, the long-term value of a ReScience
 publication is not the actual code but the accompanying article. If you

### 2017-06-07 draft.tex
New section on reproduction vs. replication

@@
 
+\section*{Replication and reproduction in computer-aided research}
+
+With the increasing recognition of the replication crisis as a problem
+for scientific research, it has become a major subject of debate, but
+unfortunately no common terminology has emerged so far. One reason for
+this diverse use of terms is that each field of research has its own
+specific technical and social obstacles on the road to published
+results and findings that can be verified by other scientists. Here we
+briefly summarize the obstacles that arise from the use of computers
+and software in scientific research, and introduce the terminology we
+will use in the rest of this article.
+
+\textit{Reproducing} the result of a computation means running the
+same software on the same input data and obtaining the same results.
+Obstacles to reproducibility are the loss of parts of the software or
+input data, lack of a computing environment that is sufficiently
+similar to the one used initially, and insufficient instructions for
+making the software work. An obstacle specific to numerical
+computations is the use of floating-point arithmetic, whose rules are
+subject to slightly different interpretations by different compilers
+and runtime support systems.
+
+Publishing a reproducible computational result implies publishing all
+the software and all the input data, or references to previously
+published software and data, along with the traditional article
+describing the work. An obvious added value is the availability of the
+software and data, which helps readers to gain a better understanding
+of the work, and can be re-used in other research projects. In
+addition, reproducibly published results are more trustworthy, because
+many common mistakes in working with computers can be excluded:
+mistyping parameter values or input file names, updating the software
+but forgetting to mention the changes in the description of the
+method, planning to use one version of some software but actually
+using a different one, etc.
+
+Strictly speaking, reproducibility is defined in the context of
+identical computational environments. However, useful scientific
+software is expected to be robust with respect to certain changes in
+this environment. A computer program that produces different results
+when compiled using different compilers, or run on two different
+computers, would be considered suspect by most practitioners, even if
+it were demonstrably correct in one specific environment. Ultimately
+it is not the software that is of interest for science, but the models
+and methods that it implements. The software is merely a vehicle to
+perform computations based on these models and methods. If results
+depend on hard to control implementation details of the software,
+their relation to the underlying models and methods becomes unclear.
+
+\textit{Replicating} a published result means writing and then running
+new software based on the description of a computational model or
+method provided in the original publication, and obtaining results
+which support the same scientific conclusions as the original
+ones. The main obstacle to replicability is an incomplete or imprecise
+description of the models and methods.
+
+Replicability is a much stronger quality indicator than
+reproducibility. In fact, reproducibility merely guarantees that all
+the ingredients of a computation are well documented. It does not
+imply that any of them are correct and/or appropriate for implementing
+the models and methods that were meant to be applied, nor that the
+descriptions of these models and methods are correct and clear. A
+successful replication shows that two teams have produced independent
+implementations that generate equivalent results, which makes serious
+mistakes in either software unlikely. Moreover, it shows that the
+second team was able to understand the description provided by the
+first team.
+
+Replication can be attempted both for reproducible and for
+non-reproducible results. However, when an attempt to replicate
+non-reproducible work fails, yielding results so different that the
+scientific conclusions drawn from them are different, it can be very
+difficult to identify the cause of the disagreement. Reproducibility
+guarantees the existence of a precise and complete description of the
+models and methods being applied in the original work, in the form of
+software source code. The holy grail of computational science is
+therefore a reproducible replication of reproducible original work.
+
 \section*{Reproducibility is harder than you think}

### 2017-06-07 draft.tex
Extend dicussion, remove reproducibility is harder than you think section

@@
 
-\section*{Replication and reproduction in computer-aided research}
+\section*{Replication and reproduction}
 
@@
 and software in scientific research, and introduce the terminology we
-will use in the rest of this article.
+will use in the rest of this article.\\
 
@@
 depend on hard to control implementation details of the software,
-their relation to the underlying models and methods becomes unclear.
+their relation to the underlying models and methods becomes unclear.\\
 
@@
 
-\section*{Reproducibility is harder than you think}
-
-\citeauthor{Mesnard:2016} explains in \citep{Mesnard:2016} that performing
-reproducible and replicable simulations in computational fluid dynamics is harder
-than you think. In fact, there are several different reasons for
-non-reproducibility that, for the most part, are specific to each
-scientifc domain. However, from our publishing experience, there are also some
-common behaviors that can be identified. Missing code and/or data, unknown
-dependencies, inaccurate or imprecise description appears to be shared
-characteristic of a lot of non-reproducible work.\\
-
-To be extended...
-
 \section*{The ReScience initiative}
@@
 \begin{tcolorbox}[breakable, pad at break*=1mm,
-                  colback=black!2.5, arc=0pt, outer arc=0pt, boxrule=0pt]
+                  colback=black!2.5, arc=0pt, outer arc=0pt, boxrule=.25pt]
 \begin{footnotesize}
@@
 %% record.
+%% \section*{Reproducibility is harder than you think}
+
+%% \citeauthor{Mesnard:2016} explains in \citep{Mesnard:2016} that performing
+%% reproducible and replicable simulations in computational fluid dynamics is harder
+%% than you think. In fact, there are several different reasons for
+%% non-reproducibility that, for the most part, are specific to each
+%% scientifc domain. However, from our publishing experience, there are also some
+%% common behaviors that can be identified. Missing code and/or data, unknown
+%% dependencies, inaccurate or imprecise description appears to be shared
+%% characteristic of a lot of non-reproducible work.\\
+
+%% To be extended...
 
@@
     has been replicated by an independent group.}
+  \label{fig:coscience}
 \end{figure}
@@
 % -> Short-term vs long-term reproducibility
-The code accompanying a ReScience replication ensures only short-term
-reproducibility. Even if a piece of code is written following best practices,
-and then reviewed and tested, it suffers from the same problem as any other piece of
-code, i.e. it depends on a software stack whose stability is not guaranteed in
-the long term. \citep{Mesnard:2016} illustrated this problem very clearly when
-they tried to reproduce their own work performed two years earlier. Even though Barba's
-group is committed to reproducible research practices, they did not escape the many
-problems one can face when trying to re-run a piece of code. This means the
-newly produced code for ReScience will likely be obsolete at some point in the
-future. It can be a matter of months or years, or even decades, but ultimately, obsolescence is inevitable. Therefore, the long-term value of a ReScience
-publication is not the actual code but the accompanying article. If you
-consider the original article with missing or incomplete information and the
-new article with missing and checked information, you have a complete and
-consistent description of the original work. This means than 5, 10 or 20 years
-from now, one should be able to replicate the work thanks to these two
+
+There are several different reasons for non-reproducibility. For the most part,
+those reasons are specific to each scientifc domain but, from our publishing
+experience, there are also some common behaviors that can be identified.
+Missing code and/or data, unknown dependencies, inaccurate or imprecise
+description appears to be shared characteristic of a lot of non-reproducible
+work. If the code accompanying a ReScience replication can fix a lot of these
+issue, it can nonetheless only ensure short-term reproducibility. Even if a
+piece of code is written following best practices, and then reviewed and
+tested, it suffers from the same problem as any other piece of code, i.e. it
+depends on a software stack whose stability is not guaranteed in the long
+term. \citep{Mesnard:2016} illustrated this problem very clearly when they
+tried to reproduce their own work performed two years earlier. Even though
+Barba's group is committed to reproducible research practices, they did not
+escape the many problems one can face when trying to re-run a piece of code.
+This means the newly produced code for ReScience will likely be obsolete at
+some point in the future. It can be a matter of months or years, or even
+decades, but ultimately, obsolescence is inevitable. Therefore, the long-term
+value of a ReScience publication is not the actual code but the accompanying
+article. If you consider the original article with missing or incomplete
+information and the new article with missing and checked information, you have
+a complete and consistent description of the original work. 5, 10 or 20 years
+from now, anyone should be able to replicate the work thanks to these two
 articles. Of course, the new code can also help, but the true value of a
-replication is the accompanying article.
+replication is really the accompanying article.\\
+
+One immediate and legitimate question is to wonder to what extent such
+replication could be performed prior to the publication of the original
+article. This would strongly reinforce a claim because a successful and
+independent replication would have been performed prior to the publication. As
+illustrated on figure \ref{fig:coscience}, this would require for a group A to
+contact a group B and to send them their a draft of their original work (the
+one that would be normally submitted to a journal) such that group B could run
+a replication and confirm or infirm the work. In case of confirmation, a
+certified article could be later published with both group as authors (each
+group being identified according to their respective roles). However, if the
+replication failed and the original work cannot be fixed, this would prevent
+the publication. This model would improve the overall reproducibiloty and would
+slow down considerably the pace of publication we're observing
+today. Unfortunately, such scenario is highly improbable. The pressure to
+publish is so strong and the incentive for doing replication so low that it
+would most probably prevent such collaborative work. At this point, CoScience
+is mostly an utopia for tomorrow.
 

### 2017-06-08 draft.tex
Revision of the "reproduction and replication" section

@@
 unfortunately no common terminology has emerged so far. One reason for
-this diverse use of terms is that each field of research has its own
+the diverse use of terms is that each field of research has its own
 specific technical and social obstacles on the road to published
@@
 same software on the same input data and obtaining the same results.
-Obstacles to reproducibility are the loss of parts of the software or
-input data, lack of a computing environment that is sufficiently
-similar to the one used initially, and insufficient instructions for
-making the software work. An obstacle specific to numerical
-computations is the use of floating-point arithmetic, whose rules are
-subject to slightly different interpretations by different compilers
-and runtime support systems.
+The goal of a reproduction attempt is to verify that the computational
+protocol leading to the results has been recorded correctly.
+Performing computations reproducibly can be seen as a form of
+provenance tracking, the software being a detailed record of all data
+processing steps.
+
+In theory, computation is a deterministic process and exact
+reproduction should therefore be trivial. In reality, it is very
+difficult to achieve because of the complexity of today's software
+stacks and the tediousness of recording all interactions between a
+scientist and a computer.  \citeauthor{Mesnard:2016} explain in
+\citep{Mesnard:2016} how difficult it can be to reproduce a two-year
+old computation even though all possible precautions were taken at the
+time to ensure reproducibility.  The most frequent obstacles are the
+loss of parts of the software or input data, lack of a computing
+environment that is sufficiently similar to the one used initially,
+and insufficient instructions for making the software work. An
+obstacle specific to numerical computations is the use of
+floating-point arithmetic, whose rules are subject to slightly
+different interpretations by different compilers and runtime support
+systems. A large variety of research practices and support tools have
+been developed recently to facilitate reproducible computations. For a
+collection of recipes that have proven useful, see
+\citep{kitzes:2017}.
 
@@
 depend on hard to control implementation details of the software,
-their relation to the underlying models and methods becomes unclear.\\
+their relation to the underlying models and methods becomes unclear
+and unreliable.\\
 
@@
 method provided in the original publication, and obtaining results
-which support the same scientific conclusions as the original
-ones. The main obstacle to replicability is an incomplete or imprecise
+that are similar enough to be considered equivalent. What exactly
+``similar enough'' means strongly depends on the kind of computation
+being performed, and can only be judged by an expert in the field.
+The main obstacle to replicability is an incomplete or imprecise
 description of the models and methods.
@@
 non-reproducible results. However, when an attempt to replicate
-non-reproducible work fails, yielding results so different that the
-scientific conclusions drawn from them are different, it can be very
-difficult to identify the cause of the disagreement. Reproducibility
-guarantees the existence of a precise and complete description of the
-models and methods being applied in the original work, in the form of
-software source code. The holy grail of computational science is
-therefore a reproducible replication of reproducible original work.
+non-reproducible work fails, yielding results too different to be
+considered equivalent, it can be very difficult to identify the cause
+of the disagreement. Reproducibility guarantees the existence of a
+precise and complete description of the models and methods being
+applied in the original work, in the form of software source code,
+which can be analyzed during the investigation of any
+discrepancies. The holy grail of computational science is therefore a
+reproducible replication of reproducible original work.
 

### 2017-06-08 draft.tex
Revision of "The ReScience initiative"

@@
 \section*{Replication and reproduction}
-
+\label{sec:replication-reproduction}
 With the increasing recognition of the replication crisis as a problem
@@
 
-Writing a replication is a daunting task that is traditionally hardly or not
+Performing a replication is a daunting task that is traditionally hardly or not
 at all rewarded. Nevertheless, some people are actually willing to replicate
@@
 the original authors. The question is where to publish such a replication. To the
-best of our knowledge, no major journal would accept to publish a single successful
-replication in computational science. This has been the main motivation for the
+best of our knowledge, no major journal accepts publishing replications in computational science. This has been the main motivation for the
 creation of the ReScience journal (\url{rescience.github.io}) by Konrad Hinsen
@@
 
-ReScience is an open peer-reviewed journal that targets computational research
-and encourages the explicit replication of already published research,
-promoting new and open-source implementations in order to ensure that the
-original research is reproducible. In less than two years of existence, 12
+ReScience is an openly peer-reviewed journal that targets computational research
+and encourages the explicit replication of already published research. In order
+to provide the largest benefit to the scientific community, replications are
+required to be reproducible and open-source. In less than two years of existence, 12
 articles have been published and 3 are currently under review
@@
 
-One of the specificities of the ReScience journal is its publishing chain that is
-radically different from any other traditional scientific journals since
-ReScience lives on GitHub. Each submission takes the form of a pull request
-that is first considered by a member of the editorial board, who may decide to
-reject the submission, or assign it to two reviewers for further review and
-tests. The reviewers evaluate the code and the accompanying material in
-continuous interaction with the authors through the discussion section. If both
-reviewers manage to run the code and obtain the same results as the ones
-advertised in the accompanying material, the submission is
-accepted. Furthermore, an author cannot submit a replication of his/her own
-research, nor the research of close collaborators. Mistakes in the
-implementation of research questions and methods are often due to biases
-authors invariably have, consciously or not. Such biases will inevitably carry
-over to how one approaches a replication. Perhaps even more importantly, 
-cross-fertilization is generally useful in research, and trying to replicate the work of
-one’s peers might pave the way for a future collaboration, or may give rise to
-new ideas as a result of the replication effort.\\
+One of the specificities of the ReScience journal is its publishing
+chain that is radically different from any other traditional
+scientific journals since ReScience lives on GitHub. One of the
+consequences is that the whole process, from submission via reviewing
+to publication, is open for anyone to see and even comment on.\\
 
-The main criterion for acceptation is the actual replication of the research
-with a clear statement by the authors explaining why they think they have
-replicated the paper (same figures, same graphics, same behavior,
-etc.). However, the clarity of the code is an important criterion as well because
-uncommented or obfuscated code is no better than no code at all. A code without an
-accompanying article is also a criterion for rejection since we’re not human
-compilers (well not all of us at least). The role of the reviewer is thus to
-ensure that the proposed submission is actually replicable. This means:
-%
+Each submission takes the form of a pull request that is first
+considered by a member of the editorial board, who may decide to
+reject the submission if it does not respect the formal publication
+criteria of ReScience. A submission must contain
 \begin{itemize}
-\item They are able to run the proposed implementation on their computers.
-\item They obtain the same results as indicated in the accompanying paper.
-\item These results are sufficiently close to the ones reported in the original paper being replicated.
+\item a precise reference to the work being replicated,
+\item an explanation of why the authors think they have replicated the paper
+      (same figures, same graphics,same behavior, etc.),
+\item a description of any difficulties encountered during the
+      replication,
+\item open-source code that produces the replication results,
+\item an explanation of this code for human readers.
+\end{itemize}
+A complete submission therefore consists of both code and an accompanying
+article. Partial replications that cover only some of the results in the
+original work are acceptable, but need to be justified.\\
+
+If the submission respects these criteria, the editor assigns it to
+two reviewers for further evaluation and tests. The reviewers evaluate
+the code and the accompanying material in continuous interaction with
+the authors through the discussion section until both reviewers
+consider the work acceptable for publication. The goal of the review
+is thus to help the authors meet the ReScience quality standards
+through discussion. Since ReScience targets replication of already
+published work, the criteria of relevance or novelty applied by most
+traditional journals are irrelevant.
+
+For a submission to be accepted, both reviewers must consider it
+reproducible and a valid replication of the original work. As we
+explained in section~\ref{sec:replication-reproduction}, this means
+that the reviewers
+\begin{itemize}
+\item are able to run the proposed implementation on their computers,
+\item obtain the same results as indicated in the accompanying paper,
+\item consider these results sufficiently close to the ones reported in the original paper being replicated.
 \end{itemize}
 %
-The goal of the review is thus to help the author to meet the ReScience quality
-standards through discussion. More specifically, since ReScience targets
-replication of original research, there is no need to judge the relevance or
-novelty of the research. The review concentrates on how easy it would be for
-another researcher to run the proposed implementation. This should be viewed in
-light of the standards in the field. If a given tool/library/software is
-mainstream in a field, it is ok to use them, but if a brand new standalone
-implementation is proposed, this must not rejected on this criterion.
+% The review concentrates on how easy it would be for another researcher
+% to run the proposed implementation. This should be viewed in light of
+% the standards in the field. If a given tool/library/software is
+% mainstream in a field, it is ok to use them, but if a brand new
+% standalone implementation is proposed, this must not rejected on this
+% criterion.
+
+Since independent implementation is a major criterion in replication
+work, ReScience does not allow authors to submit replications of their
+own research, nor the research of close collaborators. Mistakes in the
+implementation of computational models and methods are often due to
+biases that authors invariably have, consciously or not. Such biases
+will inevitably carry over to a replication. Perhaps even more
+importantly, cross-fertilization is generally useful in research, and
+trying to replicate the work of one’s peers might pave the way for a
+future collaboration, or may give rise to new ideas as a result of the
+replication effort.
 

### 2017-06-08 draft.tex
Added all editors & active reviewers, miss publication authors

@@
 % Better default font (Libertine and Inconsolata)
-% \usepackage[ttscale=.875]{libertine}
-% \usepackage[scaled=0.96]{zi4}
+\usepackage[ttscale=.875]{libertine}
+\usepackage[scaled=0.96]{zi4}
 
-\usepackage{mathspec}
-\setmainfont{Minion Pro Cond}
-\setmathsfont(Digits,Greek,Latin)[Numbers={Proportional}]{Minion Pro}
-\setmathrm{Minion Pro}
-\setsansfont{MyriadPro-Cond}
+%% \usepackage{mathspec}
+%% \setmainfont{Minion Pro Cond}
+%% \setmathsfont(Digits,Greek,Latin)[Numbers={Proportional}]{Minion Pro}
+%% \setmathrm{Minion Pro}
+%% \setsansfont{MyriadPro-Cond}
 
@@
 \rhead{\footnotesize \sf page \thepage}
-\lhead{\footnotesize \sf Rougier et al. 2017
+\lhead{\footnotesize \sf Rougier, Hinsen et al. 2017
        \textbullet~The ReScience Initiative}
@@
 %%     rectangle node[text=white,font=\sffamily\bfseries\tiny,rotate=0] {ID} ([xshift=4mm]frame.north west);\end{tcbclipinterior}}}
+
+\newcommand{\hgap}{\hspace{1mm}}
 
@@
 \author{%
-  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$,
-  \textbf{Konrad Hinsen}$^{4,5}$,
-  \textbf{Thomas Arildsen}$^{?}$,
-  \textbf{Lorena Barba}$^{?}$,
-  \textbf{Fabien Benureau}$^{?}$,
-  \textbf{C. Titus Brown}$^{?}$,
-  \textbf{Georgios Detorakis}$^{?}$,
-  \textbf{Emmanuelle Gouillart}$^{?}$,
-  \textbf{Pierre de Buyl}$^{?}$,
-  \textbf{Benoît Girard}$^{?}$,
-  \textbf{Olivia Guest}$^{?}$,
-  \textbf{Mehdi Khamassi}$^{?}$,
-  \textbf{Etienne Roesch}$^{?}$,
-  \textbf{Joseph Stachelek}$^{?}$,
-  \textbf{Owen Petchey}$^{?}$,
-  \textbf{Timothée Poisot}$^{?}$,
-  \textbf{Karthik Ram}$^{?}$,
-  \textbf{Yoav Ram}$^{?}$
-  \textbf{Federico Vaggi}$^{?}$,
-  \textbf{Julien Vitay}$^{?}$,
-  \textbf{Tiziano Zito}$^{?}$\\
+  \begin{small}
+\textbf{Nicolas P. Rougier}$^{1,*}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Konrad Hinsen}$^{2}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Andrew Davison}$^{8}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Marc André Delsuc}$^{9}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Georgios Detorakis}$^{10}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Damien Drix}$^{11}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Pierre Enel}$^{12}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Benoît Girard}$^{13}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Emmanuelle Gouillart}$^{14}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Olivier Grisel}$^{15}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Olivia Guest}$^{16}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Matt Hall}$^{17}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Xavier Hinaut}$^{18}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Mehdi Khamassi}$^{19}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Almar Klein}$^{20}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Pietro Marchesi}$^{21}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Dan McGlinn}$^{22}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Hans Ekkehard Plesser}$^{23}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Timothée Poisot}$^{24}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Karthik Ram}$^{25}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Yoav Ram}$^{26}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Etienne Roesch}$^{27}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Cyrille Rossant}$^{28}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Aaron Shifman}$^{29}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Joseph Stachelek}$^{30}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Marcel Stimberg}$^{31}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Federico Vaggi}$^{32}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Julien Vitay}$^{33}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Anya Vostinar}$^{34}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Roman Yurchak}$^{35}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{iD-icon.pdf}},
+\textbf{Tiziano Zito}$^{36}$,
+\textbf{Ozan Çağlayan}$^{37}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{iD-icon.pdf}}\\
+\end{small}
 \begin{footnotesize}
+  \vspace{2mm}
     $^{1}$INRIA Bordeaux Sud-Ouest
-          Talence, France
-    $^{2}$Institut des Maladies Neurodégénératives, Université de Bordeaux,
-          CNRS, UMR 5293, Bordeaux, France
-    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
-          CNRS, UMR 5800, Talence, France
-    $^{4}$Centre de Biophysique Moléculaire,
-          CNRS UPR4301, Orléans Cedex 2
-    $^{5}$Synchrotron SOLEIL, Division Expériences,
+          Talence, France --
+          Institut des Maladies Neurodégénératives, Université de Bordeaux,
+          CNRS UMR 5293, Bordeaux, France -- 
+          LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
+          CNRS UMR 5800, Talence, France •
+    $^{2}$Centre de Biophysique Moléculaire,
+          CNRS UPR4301, Orléans --
+          Synchrotron SOLEIL, Division Expériences,
           Gif sur Yvette, France\\

### 2017-06-08 parse-board.py

@@ -1,0 +1,44 @@
+import re
+
+authors = [ # "rougier", "khinsen",
+           "otizonaizit", "pdebuyl", "emmanuelle",
+           "ctb", "ThomasA", "tpoisot", "karthik", "oliviaguest",
+           "labarba", "MehdiKhamassi", "benoit-girard", "vitay",
+           "gdetor", "dmcglinn", "yoavram", "FedericoV", "jsta",
+           "heplesser", "apdavison", "neuronalX", "piero-le-fou",
+           "mstimberg", "rossant", "eroesch", "damiendr", "delsuc",
+           "soolijoo", "benureau", "rth", "almarklein", "pietromarchesi",
+           "aaronshifman", "anyaevostinar","ozancaglayan", "ogrisel"]
+
+name_re = re.compile("""\* \[(?P<name>.+)\]\(https://github.com/(?P<handle>.+)\)""")
+orcid_re= re.compile("""  ORCID: \[(?P<orcid>.+)\]""")
+handle_re = re.compile("""""")
+
+board = {}
+names = []
+with open("../ReScience.github.io/04-board.md") as file:
+    for line in file.readlines():
+        match = name_re.match(line)
+        if match:
+            name  = match.group("name")
+            handle = match.group("handle")
+        match = orcid_re.match(line)
+        if match:
+            orcid = match.group("orcid")
+            board[name] = [handle, orcid]
+            if handle in authors:
+                names.append(name)
+
+names.sort(key=lambda s: s.split()[-1])
+names = ["Nicolas P. Rougier", "Konrad Hinsen"] + names
+
+for i,name in enumerate(names):
+    orcid = board[name][1]
+#    if orcid != "---":
+#        print ("\\textbf{%s}$^{%d}$ \href{http://orcid.org/%s}{\includegraphics[width=10pt]{iD-icon.pdf}}," % (name, i+1, orcid))
+#    else:
+    print ("\\textbf{%s}$^{%d}$," % (name, i+1))
+
+for i,name in enumerate(names):
+    orcid = board[name][1]
+    print("$^{%d}$ \includegraphics[width=10pt]{iD-icon.pdf} \\href{http://orcid.org/%s}{orcid.org/%s} |" % (i+1, orcid, orcid))

### 2017-06-09 authors.tex
Put authors into a separate file

\textbf{Nicolas P. Rougier}$^{1}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Konrad Hinsen}$^{2}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Ozan Çağlayan}$^{8}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Andrew Davison}$^{9}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Marc André Delsuc}$^{10}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Georgios Detorakis}$^{11}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Damien Drix}$^{12}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Pierre Enel}$^{13}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Benoît Girard}$^{14}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Emmanuelle Gouillart}$^{15}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Olivier Grisel}$^{16}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Olivia Guest}$^{17}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Matt Hall}$^{18}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Rafael Neto Henriques}$^{19}$,
%%
\textbf{Xavier Hinaut}$^{20}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Mehdi Khamassi}$^{21}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Almar Klein}$^{22}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Andrei Maksimov}$^{23}$,
%%
\textbf{Pietro Marchesi}$^{24}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Erwan Le Masson}$^{25}$,
%%
\textbf{Dan McGlinn}$^{26}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Owen Petchey}$^{27}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Hans Ekkehard Plesser}$^{28}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Timothée Poisot}$^{29}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Karthik Ram}$^{30}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Yoav Ram}$^{31}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Etienne Roesch}$^{32}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Cyrille Rossant}$^{33}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Vahid Rostami}$^{34}$,
%%
\textbf{Aaron Shifman}$^{35}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Joseph Stachelek}$^{36}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Marcel Stimberg}$^{37}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Adam Tomkins}$^{38}$,
%%
\textbf{Federico Vaggi}$^{39}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Guillaume Viejo}$^{40}$,
%%
\textbf{Julien Vitay}$^{41}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Anya Vostinar}$^{42}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Roman Yurchak}$^{43}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=10pt]{orcid}},
%%
\textbf{Tiziano Zito}$^{44}$\\

### 2017-06-09 draft.tex
Put authors into a separate file

--- 2017-06-08 draft.tex
@@
 \author{%
-  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$,
-  \textbf{Konrad Hinsen}$^{4,5}$,
-  \textbf{Thomas Arildsen}$^{?}$,
-  \textbf{Lorena Barba}$^{?}$,
-  \textbf{Fabien Benureau}$^{?}$,
-  \textbf{C. Titus Brown}$^{?}$,
-  \textbf{Georgios Detorakis}$^{?}$,
-  \textbf{Emmanuelle Gouillart}$^{?}$,
-  \textbf{Pierre de Buyl}$^{?}$,
-  \textbf{Benoît Girard}$^{?}$,
-  \textbf{Olivia Guest}$^{?}$,
-  \textbf{Mehdi Khamassi}$^{?}$,
-  \textbf{Etienne Roesch}$^{?}$,
-  \textbf{Joseph Stachelek}$^{?}$,
-  \textbf{Owen Petchey}$^{?}$,
-  \textbf{Timothée Poisot}$^{?}$,
-  \textbf{Karthik Ram}$^{?}$,
-  \textbf{Yoav Ram}$^{?}$
-  \textbf{Federico Vaggi}$^{?}$,
-  \textbf{Julien Vitay}$^{?}$,
-  \textbf{Tiziano Zito}$^{?}$\\
+  \begin{small}
+    \input{authors.tex}
+  \end{small}
 \begin{footnotesize}
+  \vspace{2mm}
     $^{1}$INRIA Bordeaux Sud-Ouest
-          Talence, France
-    $^{2}$Institut des Maladies Neurodégénératives, Université de Bordeaux,
-          CNRS, UMR 5293, Bordeaux, France
-    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
-          CNRS, UMR 5800, Talence, France
-    $^{4}$Centre de Biophysique Moléculaire,
-          CNRS UPR4301, Orléans Cedex 2
-    $^{5}$Synchrotron SOLEIL, Division Expériences,
+          Talence, France --
+          Institut des Maladies Neurodégénératives, Université de Bordeaux,
+          CNRS UMR 5293, Bordeaux, France -- 
+          LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
+          CNRS UMR 5800, Talence, France •
+    $^{2}$Centre de Biophysique Moléculaire,
+          CNRS UPR4301, Orléans --
+          Synchrotron SOLEIL, Division Expériences,
           Gif sur Yvette, France\\

### 2017-06-09 parse-board.py

@@ -1,14 +1,16 @@
 import re
 
 authors = [ # "rougier", "khinsen",
-           "otizonaizit", "pdebuyl", "emmanuelle",
+           "otizonaizit", "pdebuyl", "emmanuelle", 
            "ctb", "ThomasA", "tpoisot", "karthik", "oliviaguest",
            "labarba", "MehdiKhamassi", "benoit-girard", "vitay",
-           "gdetor", "dmcglinn", "yoavram", "FedericoV", "jsta",
+           "gdetor", "dmcglinn", "yoavram", "FedericoV", "AdamRTomkins",
            "heplesser", "apdavison", "neuronalX", "piero-le-fou",
            "mstimberg", "rossant", "eroesch", "damiendr", "delsuc",
            "soolijoo", "benureau", "rth", "almarklein", "pietromarchesi",
-           "aaronshifman", "anyaevostinar","ozancaglayan", "ogrisel"]
+           "aaronshifman", "anyaevostinar","ozancaglayan", "ogrisel",
+           "jsta", "opetchey", "aaronshifman"]
+
 
 name_re = re.compile("""\* \[(?P<name>.+)\]\(https://github.com/(?P<handle>.+)\)""")
 orcid_re= re.compile("""  ORCID: \[(?P<orcid>.+)\]""")
@@ -22,6 +24,9 @@ with open("../ReScience.github.io/04-board.md") as file:
         if match:
             name  = match.group("name")
             handle = match.group("handle")
+            # Hack for sorting without taking care of unicode
+            if name == "Ozan Çağlayan": name = "Ozan CÇağlayan"
+            
         match = orcid_re.match(line)
         if match:
             orcid = match.group("orcid")
@@ -29,16 +34,38 @@ with open("../ReScience.github.io/04-board.md") as file:
             if handle in authors:
                 names.append(name)
 
+# Adding authors by hand (they're not part of the board)
+board["Guillaume Viejo"] = ["gviejo", "---"]
+board["Andrei Maksimov"] = ["andruhamax", "---"]
+board["Erwan Le Masson"] = ["maekclena", "---"]
+board["Rafael Neto Henriques"] = ["RafaelNH", "---"]
+board["Vahid Rostami"] = ["Vahidrostami", "---"]
+
+names.extend(["Guillaume Viejo", "Andrei Maksimov", "Erwan Le Masson",
[…]

### 2017-06-09 draft.tex
Put affiliations into a separate file

@@
   \vspace{2mm}
-    $^{1}$INRIA Bordeaux Sud-Ouest
-          Talence, France --
-          Institut des Maladies Neurodégénératives, Université de Bordeaux,
-          CNRS UMR 5293, Bordeaux, France -- 
-          LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
-          CNRS UMR 5800, Talence, France •
-    $^{2}$Centre de Biophysique Moléculaire,
-          CNRS UPR4301, Orléans --
-          Synchrotron SOLEIL, Division Expériences,
-          Gif sur Yvette, France\\
+  \input{affiliations.tex}
   $^{*}$Corresponding author:

### 2017-06-09 draft.tex
Fix typo in link

@@
 best of our knowledge, no major journal accepts publishing replications in computational science. This has been the main motivation for the
-creation of the ReScience journal (\url{rescience.github.io}) by Konrad Hinsen
-and Nicolas Rougier in 2015.\\
+creation of the ReScience journal (\href{https://rescience.github.io}{rescience.github.io}) by Konrad Hinsen and Nicolas P. Rougier in September 2015.\\
 

### 2017-06-09 affiliations.tex

$^{1}$INRIA Bordeaux Sud-Ouest
      Talence, France --
      Institut des Maladies Neurodégénératives, Université de Bordeaux,
      CNRS UMR 5293, Bordeaux, France -- 
      LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
      CNRS UMR 5800, Talence, France
      %%
      •
      %%
$^{2}$Centre de Biophysique Moléculaire,
      CNRS UPR4301, Orléans --
      Synchrotron SOLEIL, Division Expériences,
      Gif sur Yvette, France
      %%
\par

### 2017-06-09 authors.tex

@@
-\textbf{Nicolas P. Rougier}$^{1}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=10pt]{orcid}},
+\textbf{Nicolas P. Rougier}$^{1}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Konrad Hinsen}$^{2}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=10pt]{orcid}},
+\textbf{Konrad Hinsen}$^{2}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=10pt]{orcid}},
+\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=10pt]{orcid}},
+\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=10pt]{orcid}},
+\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=10pt]{orcid}},
+\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=10pt]{orcid}},
+\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Ozan Çağlayan}$^{8}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=10pt]{orcid}},
+\textbf{Ozan Çağlayan}$^{8}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Andrew Davison}$^{9}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=10pt]{orcid}},
+\textbf{Andrew Davison}$^{9}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marc André Delsuc}$^{10}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=10pt]{orcid}},
+\textbf{Marc André Delsuc}$^{10}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Georgios Detorakis}$^{11}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=10pt]{orcid}},
+\textbf{Georgios Detorakis}$^{11}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Damien Drix}$^{12}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=10pt]{orcid}},
+\textbf{Damien Drix}$^{12}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre Enel}$^{13}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=10pt]{orcid}},
+\textbf{Pierre Enel}$^{13}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Benoît Girard}$^{14}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=10pt]{orcid}},
+\textbf{Benoît Girard}$^{14}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Emmanuelle Gouillart}$^{15}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=10pt]{orcid}},
+\textbf{Emmanuelle Gouillart}$^{15}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivier Grisel}$^{16}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=10pt]{orcid}},
+\textbf{Olivier Grisel}$^{16}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivia Guest}$^{17}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=10pt]{orcid}},
+\textbf{Olivia Guest}$^{17}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Matt Hall}$^{18}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=10pt]{orcid}},
+\textbf{Matt Hall}$^{18}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Xavier Hinaut}$^{20}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=10pt]{orcid}},
+\textbf{Xavier Hinaut}$^{20}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Mehdi Khamassi}$^{21}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=10pt]{orcid}},
+\textbf{Mehdi Khamassi}$^{21}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Almar Klein}$^{22}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=10pt]{orcid}},
+\textbf{Almar Klein}$^{22}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Pietro Marchesi}$^{24}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=10pt]{orcid}},
+\textbf{Pietro Marchesi}$^{24}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Dan McGlinn}$^{26}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=10pt]{orcid}},
+\textbf{Dan McGlinn}$^{26}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Owen Petchey}$^{27}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=10pt]{orcid}},
+\textbf{Owen Petchey}$^{27}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Hans Ekkehard Plesser}$^{28}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=10pt]{orcid}},
+\textbf{Hans Ekkehard Plesser}$^{28}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Timothée Poisot}$^{29}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=10pt]{orcid}},
+\textbf{Timothée Poisot}$^{29}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Karthik Ram}$^{30}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=10pt]{orcid}},
+\textbf{Karthik Ram}$^{30}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Yoav Ram}$^{31}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=10pt]{orcid}},
+\textbf{Yoav Ram}$^{31}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Etienne Roesch}$^{32}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=10pt]{orcid}},
+\textbf{Etienne Roesch}$^{32}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Cyrille Rossant}$^{33}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=10pt]{orcid}},
+\textbf{Cyrille Rossant}$^{33}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Aaron Shifman}$^{35}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=10pt]{orcid}},
+\textbf{Aaron Shifman}$^{35}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Joseph Stachelek}$^{36}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=10pt]{orcid}},
+\textbf{Joseph Stachelek}$^{36}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marcel Stimberg}$^{37}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=10pt]{orcid}},
+\textbf{Marcel Stimberg}$^{37}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Federico Vaggi}$^{39}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=10pt]{orcid}},
+\textbf{Federico Vaggi}$^{39}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Julien Vitay}$^{41}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=10pt]{orcid}},
+\textbf{Julien Vitay}$^{41}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Anya Vostinar}$^{42}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=10pt]{orcid}},
+\textbf{Anya Vostinar}$^{42}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Roman Yurchak}$^{43}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=10pt]{orcid}},
+\textbf{Roman Yurchak}$^{43}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
 %%

### 2017-06-09 authors.tex
Added author roles

@@
-\textbf{Nicolas P. Rougier}$^{1}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=8pt]{orcid}},
+\textbf{Nicolas P. Rougier}$^{1\dagger\S\star}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Konrad Hinsen}$^{2}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{orcid}},
+\textbf{Konrad Hinsen}$^{2\dagger}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Thomas Arildsen}$^{3\dagger}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{orcid}},
+\textbf{Lorena Barba}$^{4\dagger}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},
+\textbf{Fabien C. Y. Benureau}$^{5\ddagger}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},
+\textbf{C. Titus Brown}$^{6\dagger}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pierre de Buyl}$^{7\dagger}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Ozan Çağlayan}$^{8}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
+\textbf{Ozan Çağlayan}$^{8\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Andrew Davison}$^{9}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
+\textbf{Andrew Davison}$^{9\ddagger}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marc André Delsuc}$^{10}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marc André Delsuc}$^{10\ddagger}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Georgios Detorakis}$^{11}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},
+\textbf{Georgios Detorakis}$^{11\ddagger\S}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Damien Drix}$^{12}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
+\textbf{Damien Drix}$^{12\ddagger}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre Enel}$^{13}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pierre Enel}$^{13\ddagger}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Benoît Girard}$^{14}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
+\textbf{Benoît Girard}$^{14\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Emmanuelle Gouillart}$^{15}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},
+\textbf{Emmanuelle Gouillart}$^{15\dagger}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivier Grisel}$^{16}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},
+\textbf{Olivier Grisel}$^{16\ddagger}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivia Guest}$^{17}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
+\textbf{Olivia Guest}$^{17\dagger}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Matt Hall}$^{18}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
+\textbf{Matt Hall}$^{18\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Rafael Neto Henriques}$^{19}$,
+\textbf{Rafael Neto Henriques}$^{19\S}$,
 %%
-\textbf{Xavier Hinaut}$^{20}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Xavier Hinaut}$^{20\ddagger}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Mehdi Khamassi}$^{21}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
+\textbf{Mehdi Khamassi}$^{21\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Almar Klein}$^{22}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
+\textbf{Almar Klein}$^{22\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Andrei Maksimov}$^{23}$,
+\textbf{Andrei Maksimov}$^{23\S}$,
 %%
-\textbf{Pietro Marchesi}$^{24}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pietro Marchesi}$^{24\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Erwan Le Masson}$^{25}$,
+\textbf{Erwan Le Masson}$^{25\S}$,
 %%
-\textbf{Dan McGlinn}$^{26}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
+\textbf{Dan McGlinn}$^{26\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Owen Petchey}$^{27}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
+\textbf{Christoph Metzner}$^{27\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Hans Ekkehard Plesser}$^{28}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
+\textbf{Owen Petchey}$^{28\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Timothée Poisot}$^{29}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Hans Ekkehard Plesser}$^{29\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Karthik Ram}$^{30}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
+\textbf{Timothée Poisot}$^{30\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Yoav Ram}$^{31}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
+\textbf{Karthik Ram}$^{31\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Etienne Roesch}$^{32}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
+\textbf{Yoav Ram}$^{32\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Cyrille Rossant}$^{33}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
+\textbf{Etienne Roesch}$^{33\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Vahid Rostami}$^{34}$,
+\textbf{Cyrille Rossant}$^{34\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Aaron Shifman}$^{35}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
+\textbf{Vahid Rostami}$^{35\S}$,
 %%
-\textbf{Joseph Stachelek}$^{36}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
+\textbf{Aaron Shifman}$^{36\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marcel Stimberg}$^{37}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Joseph Stachelek}$^{37\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Adam Tomkins}$^{38}$,
+\textbf{Marcel Stimberg}$^{38\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Federico Vaggi}$^{39}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
+\textbf{Frank Stollmeier}$^{39\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Guillaume Viejo}$^{40}$,
+\textbf{Adam Tomkins}$^{40\ddagger}$,
 %%
-\textbf{Julien Vitay}$^{41}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
+\textbf{Federico Vaggi}$^{41\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Anya Vostinar}$^{42}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
+\textbf{Guillaume Viejo}$^{42\S}$,
 %%
-\textbf{Roman Yurchak}$^{43}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+\textbf{Julien Vitay}$^{43\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Tiziano Zito}$^{44}$\\
+\textbf{Anya Vostinar}$^{44\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Roman Yurchak}$^{45\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Tiziano Zito}$^{46\dagger}$\\

### 2017-06-09 draft.tex
Added author roles
Another revision of "The ReScience initiative"

@@
             linkbordercolor=white]{hyperref}
-\usepackage{hyperref}
 \hypersetup{colorlinks=true}
@@
   \input{affiliations.tex}
-  $^{*}$Corresponding author:
+  \vspace{2mm}
+  $^{\dagger}$ReScience editor
+  $^{\ddagger}$ReScience reviewer
+  $^{\S}$ReScience author\\
+  $^{\star}$Corresponding author:
             \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
@@
 
-Performing a replication is a daunting task that is traditionally hardly or not
-at all rewarded. Nevertheless, some people are actually willing to replicate
-computational research. The motivations for doing so are very diverse (see Box 1). Students may want familiarize themselves with
+Performing a replication is a daunting task that is traditionally not well
+rewarded. Nevertheless, some people are actually willing to replicate
+computational research. The motivations for doing so are very diverse (see Box 1). Students may want to familiarize themselves with
 a specific scientific domain, and acquire relevant practical experience by replicating important published work. Senior researchers may critically
@@
 open source implementation of already published research, chances are that this new
-implementation may be of great interest for other people as well, including
+implementation may be of interest for other people as well, including
 the original authors. The question is where to publish such a replication. To the
@@
 and encourages the explicit replication of already published research. In order
-to provide the largest benefit to the scientific community, replications are
+to provide the largest possible benefit to the scientific community, replications are
 required to be reproducible and open-source. In less than two years of existence, 12
@@
 editorial board covers a wide range of computational sciences (see
-\url{http://rescience.github.io/board/}) and more than 70 volunteers have registered to be reviewers. The computational domains of published work
-are in computational neuroscience, neuroimaging, computational ecology and
-computer graphics with a majority in computational neuroscience. There is a
+\url{http://rescience.github.io/board/}) and more than 70 volunteers have registered to be reviewers. The scientific domains of published work
+are computational neuroscience, neuroimaging, computational ecology and
+computer graphics, with a majority in computational neuroscience. There is a
 strong bias towards successful replication (100\%) and experience has
@@
 chain that is radically different from any other traditional
-scientific journals since ReScience lives on GitHub. One of the
-consequences is that the whole process, from submission via reviewing
+scientific journals since ReScience lives on GitHub, a platform
+originally designed for collaborative software development. A
+ReScience submission is treated very similarly to a contribution to an
+Open Source software project. One of the consequences is that the
+whole process, from submission via reviewing
 to publication, is open for anyone to see and even comment on.\\
@@
 \item an explanation of why the authors think they have replicated the paper
-      (same figures, same graphics,same behavior, etc.),
+      (same figures, same graphics, same behavior, etc.),
 \item a description of any difficulties encountered during the
@@
 article. Partial replications that cover only some of the results in the
-original work are acceptable, but need to be justified.\\
+original work are acceptable, but must be justified.\\
 
@@
 through discussion. Since ReScience targets replication of already
-published work, the criteria of relevance or novelty applied by most
+published work, the criteria of importance or novelty applied by most
 traditional journals are irrelevant.
@@
 reproducible and a valid replication of the original work. As we
-explained in section~\ref{sec:replication-reproduction}, this means
-that the reviewers
+explained earlier, this means that the reviewers
 \begin{itemize}
@@
 
-Since independent implementation is a major criterion in replication
+Since independent implementation is a major feature of replication
 work, ReScience does not allow authors to submit replications of their

### 2017-06-09 draft.tex
Revised and restructured the former "Discussions" section

@@
 
-\section*{Discussion}
+\section*{Lessons learned}
 
-% -> Short-term vs long-term reproducibility
+Although ReScience is still a young project, the submissions handled
+so far already provide valuable experience concerning the
+reproducibility and replicability of computational work in scientific
+research.
 
-There are several different reasons for non-reproducibility. For the most part,
-those reasons are specific to each scientifc domain but, from our publishing
-experience, there are also some common behaviors that can be identified.
-Missing code and/or data, unknown dependencies, inaccurate or imprecise
-description appears to be shared characteristic of a lot of non-reproducible
-work. If the code accompanying a ReScience replication can fix a lot of these
-issue, it can nonetheless only ensure short-term reproducibility. Even if a
-piece of code is written following best practices, and then reviewed and
-tested, it suffers from the same problem as any other piece of code, i.e. it
-depends on a software stack whose stability is not guaranteed in the long
-term. \citep{Mesnard:2016} illustrated this problem very clearly when they
-tried to reproduce their own work performed two years earlier. Even though
-Barba's group is committed to reproducible research practices, they did not
-escape the many problems one can face when trying to re-run a piece of code.
-This means the newly produced code for ReScience will likely be obsolete at
-some point in the future. It can be a matter of months or years, or even
-decades, but ultimately, obsolescence is inevitable. Therefore, the long-term
-value of a ReScience publication is not the actual code but the accompanying
-article. If you consider the original article with missing or incomplete
-information and the new article with missing and checked information, you have
-a complete and consistent description of the original work. 5, 10 or 20 years
-from now, anyone should be able to replicate the work thanks to these two
-articles. Of course, the new code can also help, but the true value of a
-replication is really the accompanying article.\\
+\subsection*{Short-term and long-term reproducibility}
 
-One immediate and legitimate question is to wonder to what extent such
-replication could be performed prior to the publication of the original
-article. This would strongly reinforce a claim because a successful and
-independent replication would have been performed prior to the publication. As
-illustrated on figure \ref{fig:coscience}, this would require for a group A to
-contact a group B and to send them their a draft of their original work (the
-one that would be normally submitted to a journal) such that group B could run
-a replication and confirm or infirm the work. In case of confirmation, a
-certified article could be later published with both group as authors (each
-group being identified according to their respective roles). However, if the
-replication failed and the original work cannot be fixed, this would prevent
-the publication. This model would improve the overall reproducibiloty and would
-slow down considerably the pace of publication we're observing
-today. Unfortunately, such scenario is highly improbable. The pressure to
-publish is so strong and the incentive for doing replication so low that it
-would most probably prevent such collaborative work. At this point, CoScience
-is mostly an utopia for tomorrow.
+While some of the reasons for non-reproducibility are specific to each
+scientifc domain, our experience has shown that there are also some
+common issued that can be identified.  Missing code and/or data,
+undocumented dependencies, and inaccurate or imprecise description
+appear to be characteristic of much non-reproducible work. Moreover,
+these problems are not always easy to detect even for attentive
+reviewers, as we discovered when some articles published in ReScience
+turned out to be difficult to reproduce for someone else for exactly
+the reasons listed above. ReScience reviewers are scientists working
+in the same domain as the submitting authors, because familiarity with
+the field is a condition for judging if a replication is
+succesful. But this also means that our reviewers share a significant
+common background with the authors, and that background includes the
+software packages and programming languages adopted by their
+community.  In particular, if both authors and reviewers have
+essential libraries of their community installed on their computers,
+they may not notice that these libraries are actually dependencies of
+the submitted code.  While solutions to this problem evidently exist
+(ReScience could, for example, request that authors make their
+software work on a standard computational environment supplied in the
+form of a virtual machine), they represent an additional effort to
+authors and therefore discourage from submitting replication work to
+ReScience.  Our goal is to develop a set of recommendations for
+authors that represent a workable compromise between reproducibility
+and implementation effort.\\
+
+Another issue with reproducibility is that with today's computing
+technology, long-term reproducibility can only be achieved by imposing
+drastic constraints on languages and libraries that are not compatible
+with the requirements of research computing. This problem is nicely
+illustrated by \citep{Mesnard:2016} whose authors report trying to
+reproduce their own work performed two years earlier. Even though
+Barba's group is committed to reproducible research practices, they
+did not escape the many problems one can face when trying to re-run a
+piece of code. As a consequence, the code newly produced for ReScience
+will likely cease to be functional at some point in the future.
+Therefore, the long-term value of a ReScience publication is not the
+actual code but the accompanying article. The combination of the
+original article and the replication article provide a complete and
+consistent description of the original work, as evidenced by the fact
+that replication was possible. Even 5, 10, or 20 years later, a
+competent scientist should be able to replicate the work again thanks
+to these two articles. Of course, the new code can also help, but the
+true long-term value of a replication is the accompanying article.\\
+
+\section*{Outlook}
+
+One immediate and legitimate question is to wonder to what extent a
+replication could be performed \textit{prior} to the publication of
+the original article. This would strongly reinforce a claim because a
+successful and independent replication would be available right from
+the start. As illustrated in figure \ref{fig:coscience}, this would
+require for a group A to contact a group B and send them a draft of
+their original work (the one that would be normally submitted to a
+journal) such that group B could perform a replication and confirm or
+infirm the results. In case of confirmation, a certified article could
+be later published with both groups as authors (each group being
+identified according to their respective roles). However, if the
+replication fails and the original work cannot be fixed, this would
+prevent publication. This model would improve the quality of
+computational research and also slow down considerably the rapid pace
+of publication we are observing today. Unfortunately, such a scenario
+seems highly improbable today. The pressure to publish is so strong
+and the incentive for doing replication so low that it would most
+probably prevent such collaborative work. At this point, CoScience is
+just a utopia for tomorrow.
 

### 2017-06-12 draft.tex
Discussion of open reviewing

@@
 
+\subsection*{Open reviewing}
+
+The well-known weaknesses of the traditional anonymous peer-reviewing
+system used by most scientific journals have motivated many
+experiments with various alternative reviewing processes. The variant
+adopted by ReScience is similar to the ones used by F1000Research or
+PeerJ, but is even more radically open: anyone can look at ReScience
+submissions and at the complete reviewing process, starting from the
+assignment of an editor and the invitation of reviewers. Moreover,
+anyone with a GitHub account can intervene by commenting. Such
+interventions could even be anonymous because a GitHub account is not
+required to advertise a real name or any other identifying
+element. ReScience does currently require all authors, editors, and
+reviewers to provide real names (which however are not verified in any
+way), but there are valid reasons to allow anonymity for authors and
+reviewers, in particular to allow junior scientists to criticize the
+work of senior colleagues without fear of retribution, and we envisage
+exploring such options in the future.
+
+Our experience with this open reviewing system is very positive so
+far. The exchanges between reviewers and authors are constructive and
+courteous, without exception. They are more similar in style to a
+coffee-table discussion than to the judgement/defence style that
+dominates traditional anonymous reviewing. Once reviewers have been
+invited and have accepted the task, the editors' main role is to
+ensure that the review moves forward, by gently reminding everyone to
+reply within reasonable delays. In addition, the editors occasionally
+answer questions by authors and reviewers about the ReScience
+publishing process.
+
+The possibility to imply participants beyond the traditional group of
+authors, editors, and reviewers is particularly interesting in the
+case of ReScience, because it can be helpful to solicit input from the
+authors of the original study that is being replicated. For example,
+in one recent case
+(\href{https://github.com/ReScience/ReScience-submission/pull/28}{\#28}),
+a reviewer suggested asking the author of the original work for a
+permission to re-use an image. The author intervened in the review and
+granted permission.
+
 \section*{Outlook}

### 2017-06-12 draft.tex
Start of discussion of GitHub

@@
 
+\subsection*{Publishing on the GitHub platform}
+
+\href{http://github.com/}{GitHub} is a commercial platform for
+collaborative software development based on the popular version
+control system \href{https://git-scm.com/}{git}. It offers unlimited
+free use to Open Source projects, defined as projects whose contents
+are accessible to everyone. All ReScience activities are organized
+around a few such Open Source projects hosted by GitHub. This is an
+unusual choice for a scientific journal, the only other journal hosted
+on GitHub being \href{http://joss.theoj.org/}{The Journal of Open
+Source Software}. In this section, we discuss the advantages and
+problems resulting from this choice, considering both technical and
+social issues.
+
+There are clear differences between platforms for software
+development, such as GitHub, and platforms for scientific publishing,
+such as \href{http://home.highwire.org/}{HighWire}. The latter tend to
+be expensive commercial products developed for the needs of large
+commercial publishers, although the market is beginning to diversify
+with products such as
+\href{https://www.episciences.org/}{Episciences}.  More importantly,
+to the best of our knowledge, no existing scientific publishing
+platform supports the submission and review of code, which is an
+essential part of every ReScience article. For this reason, the only
+option for ReScience was to adopt a software development platform and
+develop a set of procedures that make it usable for scientific
+publishing.
+
 \section*{Outlook}

### 2017-06-12 draft.tex
More discussion of GitHub

@@
 
+Our experience shows that the GitHub platform provides excellent
+support for reviewing process, which is not surprising given that the
+review of a scientific article containing code is not fundamentally
+different from the review of code with accompanying documentation.
+One potential issue for other journals envisaging to adopt this
+platform is the necessity for submitting authors to have a basic
+knowledge of the version control system git and of the techniques of
+collaborative software development. Given the code-centric nature of
+ReScience, this has not been a major problem for us, and the minor
+ones could be resolved by our editors providing technical assistance
+to authors. It is of course possible that potential authors are
+completely discouraged from submitting to ReScience by their lack
+of the required technical competence, but so far nobody has
+provided feedback suggesting that this is a problem.
+
+The main inconvenience of the GitHub platform is its almost complete
+lack of support for the publishing steps, once a submission has
+successfully passed the reviewing process. At this point, the
+submission consists of an article text in Markdown format plus a set
+of code and data files in a git repository. The desired archival form
+is an article in PDF format plus a permanent archive of the submitted
+code and data, with a Digital Object Identifier (DOI) providing a
+permanent reference. The \href{https://zenodo.org/}{Zenodo} platform
+allows straightforward archiving of snapshots of a repository hosted
+on GitHub, and issues a DOI for the archive. This leaves the task
+of producing a PDF version of the article, which is currently assumed
+by the editor handling the submission, in order to ease the technical
+burden on our authors.
+
+A minor inconvenience of the GitHub platform is its implementation of
+code reviews. It is designed for reviewing contributions to a
+collaborative project. The contributor submits new code and
+modifications to existing code in the form of a ``pull request'',
+which other project members can then comment on. In the course of the
+exchanges, the contributor can update the code and request further
+comments. Once everybody is satisfied, the contribution is ``merged''
+into the main project. In the case of ReScience, the collaborative
+project is the whole journal, and each article submission is a
+contribution proposed as a pull request. This is, however, not a very
+intuitive representation of how a journal works. It would be more
+natural to have a separate repository for each article, an arrangement
+that would also facilitate the final publishing steps. However, GitHub
+does not allow code review on a new repository, only on contributions
+to an already existing one.
+
+Relying on a free-use offer on a commercial platform poses some
+additional problems for scientific publishing. GitHub can change its
+conditions at any time, and could in principle delete or modify
+ReScience contents at any time without prior notice. Moreover, in the
+case of technical problems rendering ReScience contents temporarily or
+permanently inaccessible, the ReScience community has no legal claims
+for compensation because there is no contract that would imply any
+obligations for GitHub. It would clearly be imprudent to count on
+GitHub for long-term preservation of ReScience content, which is why
+we deposit accepted articles on Zenodo, a platform designed for
+archiving scientific information and funded by research organizations
+as an element of public research infrastructure.
+
+The use of free services provided by GitHub and Zenodo was clearly
+important to get ReScience started. The incentives for the publication
+of replication work being low, and its importance being recognized
+only slowly in the scientific community, funding ReScience through
+either author page charges or grants would have created further
+obstacles to its success. A less obvious advantage of not having to
+organize funding is that ReScience can exist without being backed by
+any legal entity that would manage its budget. This makes it possible
+to maintain a community spirit focused on shared scientific
+objectives, with nobody in a position to influence ReScience by
+explicit or implicit threats of reducing future funding.
+
 \section*{Outlook}

### 2017-06-12 draft.tex
Discussion of Software Heritage

@@
 
+Based on our experience with the ReScience initiative, we can engage
+in informed speculation about possible future evolutions in scientific
+publishing, in particular concerning replication work. We won't
+discuss minor technical advances such as a better toolchain for
+producing PDF articles, but concentrate on long-term improvements in
+the technology of electronic publishing and, most of all, in the
+attitude of the scientific community towards the publication,
+preservation, and verification of computer-aided research.
+
+% -> Long term storage: Software Heritage
+
+Today's electronic publishing platforms for scientific research still
+show their origins in paper-based publishing. Except for the
+replacement of printed paper by a printable PDF file, not much has
+changed. Although it is increasingly realized that software and data
+should be integral parts of most scientific publications today, they
+are at best relegated to the status of ``supplementary material'', and
+systematically excluded from the peer review process. In fact, to the
+best of our knowledge, ReScience is the only scientific journal that
+aims to verify the correctness of scientific software. As our
+experience has shown, it is far easier to graft publication onto a
+software development platform than to integrate software reviewing
+into a publishing platform.
+
+A logical next step is to fully embrace the technology designed for
+software development, which far better takes into account the
+specificity of electronic information processing than today's
+scientific publishing systems. In addition to the proper handling of
+code, such an approach offers further advantages. Perhaps the most
+important one is a shift of focus from the paper as a mostly isolated
+and finished piece of work to scientific progress as a collection of
+incremental and highly interdependent steps. The
+\href{https://www.softwareheritage.org/}{Software Heritage} project,
+whose aim is to create a permanent public archive of all publicly
+available software source code, adopts exactly this point of view for
+the preservation of software. As our experience with ReScience has
+shown, integrating the narrative of a scientific article into a
+framework designed for software development is not difficult at all.
+Publishing and archiving scientific research in Software Heritage
+would offer several advantages. The intrinsic identifiers that provide
+access to the contents of the archive permit unambiguous and permanent
+references to ongoing projects as well as to snapshots at a specific
+time, and to whole projects as well as to the individual files that
+are part of them. Such references hold the promise for better reuse of
+scientific information, for better reproducibility of
+computations, and for fairer attribution of credit to scientists
+who contribute to research infrastructure.
+
+% -> Post vs Pre replication: CoScience, an utopia for tomorrow
+
 One immediate and legitimate question is to wonder to what extent a
@@
 
-% -> Long term storage: Software Heritage
-
 % -> Computational vs Experimental: ReScience X (Etienne Roesch)
-
-% -> Post vs Pre replication: CoScience, an utopia for tomorrow
 

### 2017-06-13 draft.tex
two typos

@@
 While some of the reasons for non-reproducibility are specific to each
-scientifc domain, our experience has shown that there are also some
-common issued that can be identified.  Missing code and/or data,
+scientific domain, our experience has shown that there are also some
+common issues that can be identified.  Missing code and/or data,
 undocumented dependencies, and inaccurate or imprecise description

### 2017-06-15 authors.tex

--- 2017-06-09 authors.tex
@@
-\textbf{Nicolas P. Rougier}$^{1}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=8pt]{orcid}},
+\textbf{Nicolas P. Rougier}$^{1\dagger\S\star}$\href{http://orcid.org/0000-0002-6972-589X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Konrad Hinsen}$^{2}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{orcid}},
+\textbf{Konrad Hinsen}$^{2\dagger}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Thomas Arildsen}$^{3}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Frédéric Alexandre}$^{3\S}$\href{http://orcid.org/0000-0002-6113-1878}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Lorena Barba}$^{4}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{orcid}},
+\textbf{Thomas Arildsen}$^{4\dagger}$\href{http://orcid.org/0000-0003-3254-3790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Fabien C. Y. Benureau}$^{5}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},
+\textbf{Lorena Barba}$^{5\dagger}$\href{http://orcid.org/0000-0001-5812-2711}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{C. Titus Brown}$^{6}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},
+\textbf{Fabien C. Y. Benureau}$^{6\ddagger}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre de Buyl}$^{7}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},
+\textbf{C. Titus Brown}$^{7\dagger}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Ozan Çağlayan}$^{8}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pierre de Buyl}$^{8\dagger}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Andrew Davison}$^{9}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
+\textbf{Ozan Çağlayan}$^{9\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marc André Delsuc}$^{10}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},
+\textbf{Andrew Davison}$^{10\ddagger}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Georgios Detorakis}$^{11}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marc André Delsuc}$^{11\ddagger}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Damien Drix}$^{12}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
+\textbf{Georgios Detorakis}$^{12\ddagger\S}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre Enel}$^{13}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
+\textbf{Damien Drix}$^{13\ddagger}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Benoît Girard}$^{14}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pierre Enel}$^{14\ddagger}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Emmanuelle Gouillart}$^{15}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},
+\textbf{Benoît Girard}$^{15\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivier Grisel}$^{16}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},
+\textbf{Emmanuelle Gouillart}$^{16\dagger}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivia Guest}$^{17}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
+\textbf{Olivier Grisel}$^{17\ddagger}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Matt Hall}$^{18}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
+\textbf{Olivia Guest}$^{18\dagger}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Rafael Neto Henriques}$^{19}$,
+\textbf{Matt Hall}$^{19\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Xavier Hinaut}$^{20}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Rafael Neto Henriques}$^{20\S}$,
 %%
-\textbf{Mehdi Khamassi}$^{21}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
+\textbf{Xavier Hinaut}$^{21\ddagger}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Almar Klein}$^{22}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
+\textbf{Mehdi Khamassi}$^{22\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Andrei Maksimov}$^{23}$,
+\textbf{Almar Klein}$^{23\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pietro Marchesi}$^{24}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
+\textbf{Andrei Maksimov}$^{24\S}$,
 %%
-\textbf{Erwan Le Masson}$^{25}$,
+\textbf{Pietro Marchesi}$^{25\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Dan McGlinn}$^{26}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
+\textbf{Erwan Le Masson}$^{26}$,
 %%
-\textbf{Owen Petchey}$^{27}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
+\textbf{Dan McGlinn}$^{27\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Hans Ekkehard Plesser}$^{28}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
+\textbf{Christoph Metzner}$^{28\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Timothée Poisot}$^{29}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Owen Petchey}$^{29\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Karthik Ram}$^{30}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
+\textbf{Hans Ekkehard Plesser}$^{30\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Yoav Ram}$^{31}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
+\textbf{Timothée Poisot}$^{31\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Etienne Roesch}$^{32}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
+\textbf{Karthik Ram}$^{32\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Cyrille Rossant}$^{33}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
+\textbf{Yoav Ram}$^{33\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Vahid Rostami}$^{34}$,
+\textbf{Etienne Roesch}$^{34\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Aaron Shifman}$^{35}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
+\textbf{Cyrille Rossant}$^{35\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Joseph Stachelek}$^{36}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
+\textbf{Vahid Rostami}$^{36\S}$,
 %%
-\textbf{Marcel Stimberg}$^{37}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Aaron Shifman}$^{37\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Adam Tomkins}$^{38}$,
+\textbf{Joseph Stachelek}$^{38\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Federico Vaggi}$^{39}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marcel Stimberg}$^{39\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Guillaume Viejo}$^{40}$,
+\textbf{Frank Stollmeier}$^{40\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Julien Vitay}$^{41}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
+\textbf{Adam Tomkins}$^{41\ddagger}$,
 %%
-\textbf{Anya Vostinar}$^{42}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
+\textbf{Federico Vaggi}$^{42\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Roman Yurchak}$^{43}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+\textbf{Guillaume Viejo}$^{43\S}$,
 %%
-\textbf{Tiziano Zito}$^{44}$\\
+\textbf{Julien Vitay}$^{44\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Anya Vostinar}$^{45\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Roman Yurchak}$^{46\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Tiziano Zito}$^{47\dagger}$\\

### 2017-06-16 authors.tex
Updated authors list

@@
 %%
-\textbf{Erwan Le Masson}$^{26}$,
+\textbf{Dan McGlinn}$^{26\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Dan McGlinn}$^{27\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
+\textbf{Christoph Metzner}$^{27\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Christoph Metzner}$^{28\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
+\textbf{Owen Petchey}$^{28\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Owen Petchey}$^{29\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
+\textbf{Hans Ekkehard Plesser}$^{29\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Hans Ekkehard Plesser}$^{30\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
+\textbf{Timothée Poisot}$^{30\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Timothée Poisot}$^{31\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Karthik Ram}$^{31\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Karthik Ram}$^{32\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
+\textbf{Yoav Ram}$^{32\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Yoav Ram}$^{33\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
+\textbf{Etienne Roesch}$^{33\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Etienne Roesch}$^{34\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
+\textbf{Cyrille Rossant}$^{34\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Cyrille Rossant}$^{35\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
+\textbf{Vahid Rostami}$^{35\S}$,
 %%
-\textbf{Vahid Rostami}$^{36\S}$,
+\textbf{Aaron Shifman}$^{36\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Aaron Shifman}$^{37\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
+\textbf{Joseph Stachelek}$^{37\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Joseph Stachelek}$^{38\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marcel Stimberg}$^{38\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marcel Stimberg}$^{39\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Frank Stollmeier}$^{39\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Frank Stollmeier}$^{40\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
+\textbf{Federico Vaggi}$^{40\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Adam Tomkins}$^{41\ddagger}$,
+\textbf{Guillaume Viejo}$^{41\S}$,
 %%
-\textbf{Federico Vaggi}$^{42\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
+\textbf{Julien Vitay}$^{42\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Guillaume Viejo}$^{43\S}$,
+\textbf{Anya Vostinar}$^{43\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Julien Vitay}$^{44\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
+\textbf{Roman Yurchak}$^{44\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Anya Vostinar}$^{45\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
-%%
-\textbf{Roman Yurchak}$^{46\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
-%%
-\textbf{Tiziano Zito}$^{47\dagger}$\\
+\textbf{Tiziano Zito}$^{45\dagger}$\\

### 2017-06-16 parse-board.py

@@ -4,7 +4,7 @@ chiefs = ["rougier", "khinsen"]
 editors = ["otizonaizit", "pdebuyl", "emmanuelle", "ctb", "ThomasA", "tpoisot",
            "karthik", "oliviaguest", "labarba"]
 reviewers = ["MehdiKhamassi", "benoit-girard", "vitay", "gdetor", "dmcglinn",
-             "yoavram", "FedericoV", "AdamRTomkins", "heplesser", "apdavison",
+             "yoavram", "FedericoV",  "heplesser", "apdavison",
              "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
              "damiendr", "delsuc", "ogrisel", "soolijoo", "benureau", "rth",
              "almarklein", "pietromarchesi", "anyaevostinar","ozancaglayan",
@@ -17,7 +17,6 @@ replicators = ["gviejo", "gdetor", "MehdiKhamassi", "benoit-girard", "opetchey",
 board = {}
 board["Guillaume Viejo"] = ["gviejo", "---"]
 board["Andrei Maksimov"] = ["andruhamax", "---"]
-board["Erwan Le Masson"] = ["maekclena", "---"]
 board["Frédéric Alexandre"] = ["falex33", "0000-0002-6113-1878"]
 board["Rafael Neto Henriques"] = ["RafaelNH", "---"]
 board["Vahid Rostami"] = ["Vahidrostami", "---"]

### 2017-06-20 affiliations.tex
Added author affiliations

@@
-$^{1}$INRIA Bordeaux Sud-Ouest
-      Talence, France --
-      Institut des Maladies Neurodégénératives, Université de Bordeaux,
-      CNRS UMR 5293, Bordeaux, France -- 
-      LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
-      CNRS UMR 5800, Talence, France
+$^{1}$INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France
 %%
-      •
+$^{2}$Centre de Biophysique Moléculaire, CNRS UPR4301, Orléans -- Synchrotron SOLEIL, Division Expériences, Gif sur Yvette, France
 %%
-$^{2}$Centre de Biophysique Moléculaire,
-      CNRS UPR4301, Orléans --
-      Synchrotron SOLEIL, Division Expériences,
-      Gif sur Yvette, France
+$^{3}$Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark
+%%
+$^{4}$Department of Mechanical and Aerospace Engineering, the George Washington University, Washington DC, USA
+%%
+$^{5}$Department of Population Health and Reproduction, University of California Davis, Davis, CA, USA
+%%
+$^{6}$Instituut voor Theoretische Fysica, KU Leuven, Belgium -- PdB is a postdoctoral fellow of the Research Foundation -- Flanders (FWO)
+%%
+$^{7}$Laboratoire d'Informatique de l'Université du Maine (LIUM), Le Mans, France
+%%
+$^{8}$Unité de Neurosciences, Information et Complexité, Centre National de la Recherche Scientifique, Gif-sur-Yvette, France
+%%
+$^{9}$IGBMC, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France
+%%
+$^{10}$Department of Cognitive Sciences, University of California Irvine, USA
+%%
+$^{11}$Department of Computer Science, Humboldt-Universität zu Berlin
+%%
+$^{12}$Friedman Brain Institute, Icahn School of Medicine at Mount Sinai, NY, USA
+%%
+$^{13}$Institute of Intelligent Systems and Robotics, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France
+%%
+$^{14}$Experimental Psychology, University College London, UK
+%%
+$^{15}$UCL Great Ormond St Institute of Child Health. University College London, London, UK
+%%
+$^{16}$MRC Cognition and Brain Sciences Unit, Cambridge, UK
+%%
+$^{17}$Independent scholar, Enschede, The Netherlands
+%%
+$^{18}$Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands
+%%
+$^{19}$Department of Biology, College of Charleston, Charleston, SC, USA
+%%
+$^{20}$Centre for Computer Science and Informatics Research, University of Hertfordshire, UK
+%%
+$^{21}$Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland
+%%
+$^{22}$Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany
+%%
+$^{23}$Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
+%%
+$^{24}$Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA
+%%
+$^{25}$Department of Biology, Stanford University, Stanford, CA, USA
+%%
+$^{26}$Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK
+%%
+$^{27}$Institute of Neurology, University College London, UK
+%%
+$^{28}$Institute of Neuroscience \& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany
+%%
+$^{29}$Department of Biology, University of Ottawa, Ottawa, Ontario, Canada
+%%
+$^{30}$Department of Fisheries and Wildlife, Michigan State University, MI, USA
+%%
+$^{31}$Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France
+%%
+$^{32}$Network Dynamics, Max Planck Institute for Dynamics and Self-Organization, Germany
+%%
+$^{33}$Montreal Neurological Institute, McGill University, Montreal, Canada
+%%
+$^{34}$Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany
+%%
+$^{35}$Department of Computer Science, Grinnell College, IA, USA
+%%
+$^{36}$Symerio, Palaiseau, France
+%%
+$^{37}$Neural Information Processing Group, University of Tübingen, Germany
 %%

### 2017-06-20 authors.tex
Added author affiliations

--- 2017-06-09 authors.tex
@@
 %%
-\textbf{Konrad Hinsen}$^{2\dagger}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{orcid}},
+\textbf{Konrad Hinsen}$^{2\dagger\star}$\href{http://orcid.org/0000-0003-0330-9428}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Frédéric Alexandre}$^{1\S}$\href{http://orcid.org/0000-0002-6113-1878}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Fabien C. Y. Benureau}$^{5\ddagger}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},
+\textbf{Fabien C. Y. Benureau}$^{1\ddagger}$\href{http://orcid.org/0000-0003-4083-4512}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{C. Titus Brown}$^{6\dagger}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},
+\textbf{C. Titus Brown}$^{5\dagger}$\href{http://orcid.org/0000-0001-6001-2677}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre de Buyl}$^{7\dagger}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pierre de Buyl}$^{6\dagger}$\href{http://orcid.org/0000-0002-6640-6463}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Ozan Çağlayan}$^{8\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
+\textbf{Ozan Çağlayan}$^{7\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Andrew Davison}$^{9\ddagger}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
+\textbf{Andrew Davison}$^{8\ddagger}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marc André Delsuc}$^{10\ddagger}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marc André Delsuc}$^{9\ddagger}$\href{http://orcid.org/0000-0002-1400-5326}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Georgios Detorakis}$^{11\ddagger\S}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},
+\textbf{Georgios Detorakis}$^{10\ddagger\S}$\href{http://orcid.org/0000-0001-5891-1702}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Damien Drix}$^{12\ddagger}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
+\textbf{Damien Drix}$^{11\ddagger}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre Enel}$^{13\ddagger}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pierre Enel}$^{12\ddagger}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Benoît Girard}$^{14\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
+\textbf{Benoît Girard}$^{13\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Emmanuelle Gouillart}$^{15\dagger}$\href{http://orcid.org/0000-0002-3869-9967}{\includegraphics[width=8pt]{orcid}},
+\textbf{Olivia Guest}$^{14\dagger}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivier Grisel}$^{16\ddagger}$\href{http://orcid.org/0000-0002-8226-4012}{\includegraphics[width=8pt]{orcid}},
+\textbf{Matt Hall}$^{15\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivia Guest}$^{17\dagger}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
+\textbf{Rafael Neto Henriques}$^{16\S}$,
 %%
-\textbf{Matt Hall}$^{18\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
+\textbf{Xavier Hinaut}$^{1\ddagger}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Rafael Neto Henriques}$^{19\S}$,
+\textbf{Mehdi Khamassi}$^{13\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Xavier Hinaut}$^{20\ddagger}$\href{http://orcid.org/0000-0002-1924-1184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Almar Klein}$^{17\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Mehdi Khamassi}$^{21\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pietro Marchesi}$^{18\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Almar Klein}$^{22\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
+\textbf{Dan McGlinn}$^{19\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Andrei Maksimov}$^{23\S}$,
+\textbf{Christoph Metzner}$^{20\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pietro Marchesi}$^{24\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
+\textbf{Owen L. Petchey}$^{21\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Erwan Le Masson}$^{25\S}$,
+\textbf{Hans Ekkehard Plesser}$^{22\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Dan McGlinn}$^{26\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
+\textbf{Timothée Poisot}$^{23\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Christoph Metzner}$^{27\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
+\textbf{Karthik Ram}$^{24\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Owen Petchey}$^{28\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
+\textbf{Yoav Ram}$^{25\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Hans Ekkehard Plesser}$^{29\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
+\textbf{Etienne Roesch}$^{26\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Timothée Poisot}$^{30\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Cyrille Rossant}$^{27\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Karthik Ram}$^{31\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
+\textbf{Vahid Rostami}$^{28\S}$,
 %%
-\textbf{Yoav Ram}$^{32\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
+\textbf{Aaron Shifman}$^{29\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Etienne Roesch}$^{33\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
+\textbf{Joseph Stachelek}$^{30\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Cyrille Rossant}$^{34\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marcel Stimberg}$^{31\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Vahid Rostami}$^{35\S}$,
+\textbf{Frank Stollmeier}$^{32\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Aaron Shifman}$^{36\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
+\textbf{Guillaume Viejo}$^{33\S}$,
 %%
-\textbf{Joseph Stachelek}$^{37\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
+\textbf{Julien Vitay}$^{34\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marcel Stimberg}$^{38\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Anya Vostinar}$^{35\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Frank Stollmeier}$^{39\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
+\textbf{Roman Yurchak}$^{36\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Adam Tomkins}$^{40\ddagger}$,
-%%
-\textbf{Federico Vaggi}$^{41\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
-%%
-\textbf{Guillaume Viejo}$^{42\S}$,
-%%
-\textbf{Julien Vitay}$^{43\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
-%%
-\textbf{Anya Vostinar}$^{44\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
-%%
-\textbf{Roman Yurchak}$^{45\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
-%%
-\textbf{Tiziano Zito}$^{46\dagger}$\\
+\textbf{Tiziano Zito}$^{37\dagger}$\\

### 2017-06-20 parse-board.py

@@ -1,42 +1,83 @@
 import re
+import collections
 
+affiliations = {
+    "eroesch" : "Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK",
+    "ThomasA" : "Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark",
+    "ChristophMetzner" : "Centre for Computer Science and Informatics Research, University of Hertfordshire, UK",
+    "apdavison" : "Unité de Neurosciences, Information et Complexité, Centre National de la Recherche Scientifique, Gif-sur-Yvette, France",
+    "MehdiKhamassi":  "Institute of Intelligent Systems and Robotics, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",
+    "benoit-girard" : "Institute of Intelligent Systems and Robotics, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",
+    
+    "Vahidrostami": "Institute of Neuroscience \\& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany",
+    "neuronalX" : "INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France",
+    "pietromarchesi" : "Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands",
+    "vitay" :"Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany",
+    "rossant" : "Institute of Neurology, University College London, UK",
+    "soolijoo" : "UCL Great Ormond St Institute of Child Health. University College London, London, UK",
+    "oliviaguest" : "Experimental Psychology, University College London, UK",
+    "mstimberg" : "Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France",
[…]

### 2017-06-20 parse-board.py
Correction for Konrad Hinsen affiliation

@@ -33,7 +33,7 @@ affiliations = {
     "piero-le-fou" : "Friedman Brain Institute, Icahn School of Medicine at Mount Sinai, NY, USA",
     "almarklein" : "Independent scholar, Enschede, The Netherlands",
     "benureau" : "INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France",
-    "khinsen" : "Centre de Biophysique Moléculaire, CNRS UPR4301, Orléans -- Synchrotron SOLEIL, Division Expériences, Gif sur Yvette, France",
+    "khinsen" : "Centre de Biophysique Moléculaire, CNRS UPR4301, Orléans, France -- Synchrotron SOLEIL, Division Expériences, Gif sur Yvette, France",
     "rougier" : "INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France",
     "karthik" : "Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA",
     "ozancaglayan" : "Laboratoire d'Informatique de l'Université du Maine (LIUM), Le Mans, France",

### 2017-06-20 draft.tex
Added author affiliations

@@
 % Bibliography file
-\bibliography{article.bib}
+\bibliography{draft.bib}
 
@@
   \vspace{2mm}
+  $^{\star}$ReScience co-founder
   $^{\dagger}$ReScience editor
@@
   $^{\S}$ReScience author\\
-  $^{\star}$Corresponding author:
+  Corresponding author:
             \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
@@
   \textbf{Keywords:} Open Science, Computational Science,
-                     Reproducibility, Replicability
+                     Reproducibility, Replicability, Journal, Publication
 \end{small}

### 2017-06-20 draft.tex
grammar fixes for first paragraph

@@
 \section*{Introduction}
-There is a replication crisis in Science. It has recently been highlighted in
-medicine \citep{ioannidis:2005}, psychology \citep{nosek:2015}, the
-political sciences \citep{janz:2015}, and even more recently in the biomedical
-sciences \citep{iqbal:2016}. The reasons for such non-reproducibility are as
-diverse as these domains are. In medicine, the {\em study power and bias, the
-number of other studies on the same question, and, importantly, the ratio of
-true to no relationships among the relationships probed in each scientific
-field} are important causes, as reported by \citep{ioannidis:2005}. In psychology,
-the infamous p-value seems to be the root of all evil, while in the biomedical
-sciences, \citep{iqbal:2016} identified a {\em lack of access to full datasets and
-detailed protocols for both clinical and non-clinical biomedical
-investigation}. Surprisingly enough, the computational sciences (in the broad
-sense) and computer sciences are no exception, even though they rely mostly on
-code and data that are believed to be not prone to the aforementioned
-problems.\\
+There is a replication crisis in Science. This crisis has been
+highlighted in fields as diverse as medicine \citep{ioannidis:2005},
+psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
+and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
+behind such non-reproducibility are as diverse as the domains 
+themselves. In medicine, factors such as {\em study power and bias, the
+number of other studies on the same question, and importantly, the
+ratio of true to no relationships among the all relationships probed}
+have been highlighted as important causes \citep{ioannidis:2005}. 
+In psychology, non-reproducibility has been blamed on spurious p-value
+claims (p-hacking), while in the biomedical sciences, \citep{iqbal:2016}
+a {\em lack of access to full datasets and detailed protocols for both
+clinical and non-clinical biomedical investigation} is seen as a
+critical factor. Surprisingly, the computational sciences (in the broad
+sense) and computer sciences (in the strict sense) are no exception
+despite the fact that they rely heavily on code and data that should
+make them immune to the aforementioned problems.\\
 
-When \citep{collberg:2014, collberg:2015} decided to measure the
-extent of the problem precisely, they investigated the availability of code and data,
-and {\em the extent to which this code would actually build with reasonable
-  effort}. The results were dramatic: of the 515 potentially reproducible
-papers (out of 613) targeted by the study, the authors managed to ultimately run
-only 102, i.e. less than 20\%. It is to be underlined that the authors only
-investigated the possibility to run the code. They did not check for the
-correctness of the code (does the code actually implement what is advertised
-in the paper), nor the replicability of the results (does the run lead to the
-same results as in the paper).  \citep{topalidou:2015a} encountered the same
-problem when they tried to replicate a model from the computational
-neuroscience literature: source code was not part of the supplementary section
+When \citep{collberg:2014, collberg:2015} decided to measure the extent of the problem
+precisely, they investigated the availability of code and data as well as {\em the extent to which this code would actually build with reasonable
+  effort}. The results were dramatic: of the 515 (out of 613) potentially reproducible
+papers targeted by the study, the authors managed to ultimately run
+only 102 (i.e.
+less than 20\%).
+These low numbers figures reflect only the authors success at running the code.
+They did not check for correctness of the code (does the code actually implement what is advertised in the paper), nor the replicability of the results (does the run lead to the same results as in the paper).
+\citep{topalidou:2015a} encountered the same
+problem when they tried to replicate a model from the computational neuroscience literature: source code was not part of the supplementary section
 of the paper and no link or repository was provided in the main text. When they

### 2017-06-20 draft.tex
typo and cite type change

@@
 less than 20\%).
-These low numbers figures reflect only the authors success at running the code.
+These low numbers reflect only the authors success at running the code.
 They did not check for correctness of the code (does the code actually implement what is advertised in the paper), nor the replicability of the results (does the run lead to the same results as in the paper).
-\citep{topalidou:2015a} encountered the same
+\citet{topalidou:2015a} encountered the same
 problem when they tried to replicate a model from the computational neuroscience literature: source code was not part of the supplementary section

### 2017-06-20 draft.tex
grammar fixes for second paragraph

@@
 They did not check for correctness of the code (does the code actually implement what is advertised in the paper), nor the replicability of the results (does the run lead to the same results as in the paper).
-\citet{topalidou:2015a} encountered the same
-problem when they tried to replicate a model from the computational neuroscience literature: source code was not part of the supplementary section
-of the paper and no link or repository was provided in the main text. When they
-finally got their hands on the code, after contacting the corresponding
-author, it was only to realize that it could not be compiled and was mostly
-unusable.\\
+One example of this problem can be found in \citet{topalidou:2015a} where they tried to replicate a model from the computational neuroscience literature.
+Source code was not included in the supplementary section of the paper and no link to a repository was provided in the main text.
+When they obtained the code from the corresponding author, they found that it could not be compiled and would be difficult to repurpose.\\
 

### 2017-06-20 draft.tex
finish out introduction grammar fixes

@@
   annoucement} by eLife on forking software used in eLife papers to GitHub.
-Such policies will ensure access to code and data in a well-defined format
+Such policies help to ensure access to code and data in a well-defined format
 \citep{perkel:2016} but this will not guarantee reproducilbility, nor
@@
 \citep{sandve:2013, crook:2013, wilson:2014, halchenko:2015, janz:2015,
-  hinsen:2015}. Original initiatives such as Software and Data Carpentry
+  hinsen:2015}. Related initiatives such as Software and Data Carpentry
 \citep{wilson:2016} are worth mentioning since their goal is {\em to make
   scientists more productive, and their work more reliable, by teaching them
-  basic computing skills}. Obviously, such best practices could be applied as well to already published research software or code, provided the original
-authors are willing to take on the challenge of re-implementing their own
-software for the sake of better science. This is unlikely since, unfortunately, the
+  basic computing skills}. Such best practices could be applied to already published research software or code as well, provided the original authors are willing to take on the challenge of 
+  re-implementing their own software for the sake of better science. Unfortunately, this is unlikely since the
 incentives for doing such time-consuming work are low or nonexistent.
@@
 \label{sec:replication-reproduction}
-With the increasing recognition of the replication crisis as a problem
-for scientific research, it has become a major subject of debate, but
-unfortunately no common terminology has emerged so far. One reason for
+While recognition of the replication crisis as a problem
+for scientific research has increased over time, unfortunately no 
+common terminology has emerged so far. One reason for
 the diverse use of terms is that each field of research has its own
-specific technical and social obstacles on the road to published
+specific technical and social obstacles on the road to publishing
 results and findings that can be verified by other scientists. Here we
@@
 and software in scientific research, and introduce the terminology we
-will use in the rest of this article.\\
+will use in the rest of this article:\\
 

### 2017-06-21 draft.tex
fix misspelling

@@
 solves the problem, but not so often (because of the {\em dog ate my hard
-  drive} syndrom). We thus accumulate knowledge, internal to the lab, about
+  drive} syndrome). We thus accumulate knowledge, internal to the lab, about
 which model works and which doesn't, and how a given model has to be parameterized
@@
 
-The possibility to imply participants beyond the traditional group of
+The possibility to imploy participants beyond the traditional group of
 authors, editors, and reviewers is particularly interesting in the
@@
 on GitHub, and issues a DOI for the archive. This leaves the task
-of producing a PDF version of the article, which is currently assumed
-by the editor handling the submission, in order to ease the technical
+of producing a PDF version of the article, which is currently handled
+by the managing editor of the submission, in order to ease the technical
 burden on our authors.
@@
 the start. As illustrated in figure \ref{fig:coscience}, this would
-require for a group A to contact a group B and send them a draft of
+require group A to contact group B and send them a draft of
 their original work (the one that would be normally submitted to a
 journal) such that group B could perform a replication and confirm or
-infirm the results. In case of confirmation, a certified article could
+refute the results. In case of confirmation, a certified article could
 be later published with both groups as authors (each group being
@@
 prevent publication. This model would improve the quality of
-computational research and also slow down considerably the rapid pace
+computational research and also considerably slow down the rapid pace
 of publication we are observing today. Unfortunately, such a scenario

### 2017-06-21 draft.tex
minor edits to first para

@@
 and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
-behind such non-reproducibility are as diverse as the domains 
-themselves. In medicine, factors such as {\em study power and bias, the
+behind such non-reproducibility are as diverse as the domains in which it occurs.
+In medicine, factors such as {\em study power and bias, the
 number of other studies on the same question, and importantly, the
@@
 have been highlighted as important causes \citep{ioannidis:2005}. 
-In psychology, non-reproducibility has been blamed on spurious p-value
-claims (p-hacking), while in the biomedical sciences, \citep{iqbal:2016}
+In psychology, non-reproducibility has been blamed on spurious p-values (p-hacking),
+while in the biomedical sciences, \citep{iqbal:2016}
 a {\em lack of access to full datasets and detailed protocols for both
@@
 sense) and computer sciences (in the strict sense) are no exception
-despite the fact that they rely heavily on code and data that should
+despite the fact they rely heavily on code and data, which should
 make them immune to the aforementioned problems.\\

### 2017-06-21 draft.tex

@@
 papers targeted by the study, the authors managed to ultimately run
-only 102 (i.e.
-less than 20\%).
-These low numbers reflect only the authors success at running the code.
-They did not check for correctness of the code (does the code actually implement what is advertised in the paper), nor the replicability of the results (does the run lead to the same results as in the paper).
-One example of this problem can be found in \citet{topalidou:2015a} where they tried to replicate a model from the computational neuroscience literature.
-Source code was not included in the supplementary section of the paper and no link to a repository was provided in the main text.
-When they obtained the code from the corresponding author, they found that it could not be compiled and would be difficult to repurpose.\\
+only 102 (less than 20\%).
+These low numbers only reflect the authors' success at running the code.
+They did not check for correctness of the code (i.e., does the code actually implement what is advertised in the paper), nor the replicability of the results (does each run lead to the same results as in the paper).
+One example of this problem can be found in \citet{topalidou:2015a} where they tried to replicate a computational neuroscience model.
+Source code was not included in the supplementary section of the paper nor a link to a repository in the main text.
+When the replicators obtained code from the corresponding author, they found that it could not be compiled and would be difficult to repurpose.\\
 
 Confronted with this problem, a small but growing number of journals and
-publishers have decided to react and have adopted explicit data and software
-policies. See for example the PLOS instructions on
+publishers have reacted by adopting explicit policies for data and software, for example the PLOS instructions on
 \href{http://journals.plos.org/plosone/s/materials-and-software-sharing}{Materials
@@
 on \href{http://journals.plos.org/plosone/s/data-availability}{Data Availability},
-or the
+and the
 \href{https://elifesciences.org/elife-news/inside-elife-forking-software-used-elife-papers-github}{recent
-  annoucement} by eLife on forking software used in eLife papers to GitHub.
+  annoucement} by eLife on forking (creating a linked copy of) software used in eLife papers to GitHub.
 Such policies help to ensure access to code and data in a well-defined format
-\citep{perkel:2016} but this will not guarantee reproducilbility, nor
-correctness. At the educational level, things have started to change with a
+\citep{perkel:2016} but this will not guarantee reproducilbility nor
+correctness.
+At the educational and methodological levels, things have started to change with a
 growing literature on best practices for making code reproducible
 \citep{sandve:2013, crook:2013, wilson:2014, halchenko:2015, janz:2015,
-  hinsen:2015}. Related initiatives such as Software and Data Carpentry
-\citep{wilson:2016} are worth mentioning since their goal is {\em to make
-  scientists more productive, and their work more reliable, by teaching them
-  basic computing skills}. Such best practices could be applied to already published research software or code as well, provided the original authors are willing to take on the challenge of 
-  re-implementing their own software for the sake of better science. Unfortunately, this is unlikely since the
+  hinsen:2015}.
+  Related initiatives such as Software and Data Carpentry
+\citep{wilson:2016} are of note since their goal is {\em to make
+scientists more productive, and their work more reliable, by teaching them basic computing skills}.
+Such best practices could be applied to already published research codebases as well, provided the original authors are willing to take on the challenge of 
+re-implementing their software for the sake of better science.
+Unfortunately, this is unlikely since the
 incentives for doing such time-consuming work are low or nonexistent.
 Furthermore, if the original authors made mistakes in their original
-implementation, chances are that they will reproduce the same mistakes again (just an educated guess, we have no data supporting this
-assertion).\\
-
+implementation, chances are that they will reproduce their mistakes.\\
+% (just an educated guess, we have no data supporting this assertion)
 %% At this point, the question is what do we do? Do we have to declare

### 2017-06-21 parse-board.py
Update parse-board.py

@@ -71,7 +71,7 @@ board["Guillaume Viejo"] = ["gviejo", "---"]
 # board["Andrei Maksimov"] = ["andruhamax", "---"]
 board["Frédéric Alexandre"] = ["falex33", "0000-0002-6113-1878"]
 board["Rafael Neto Henriques"] = ["RafaelNH", "---"]
-board["Vahid Rostami"] = ["Vahidrostami", "---"]
+board["Vahid Rostami"] = ["Vahidrostami", "0000-0002-3851-0220"]
 board["Frank Stollmeier"] = ["Fjanks", "0000-0003-4858-0895"]
 
 

### 2017-06-21 parse-board.py
deleted my name from those which are not part of the board

@@ -71,7 +71,6 @@ board["Guillaume Viejo"] = ["gviejo", "---"]
 # board["Andrei Maksimov"] = ["andruhamax", "---"]
 board["Frédéric Alexandre"] = ["falex33", "0000-0002-6113-1878"]
 board["Rafael Neto Henriques"] = ["RafaelNH", "---"]
-board["Vahid Rostami"] = ["Vahidrostami", "0000-0002-3851-0220"]
 board["Frank Stollmeier"] = ["Fjanks", "0000-0003-4858-0895"]
 
 

### 2017-06-21 authors.tex
authors: Modify my name to remove Turkish chars
I'm generally using a non-Turkish version of my last name.

@@
 %%
-\textbf{Ozan Çağlayan}$^{7\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
+\textbf{Ozan Caglayan}$^{7\ddagger}$\href{http://orcid.org/0000-0002-5992-3470}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Matt Hall}$^{15\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
+\textbf{Matt G. Hall}$^{15\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
 %%

### 2017-06-26 affiliations.tex
Correction for Konrad Hinsen affiliation
Updated draft PDF

@@
 %%
-$^{2}$Centre de Biophysique Moléculaire, CNRS UPR4301, Orléans -- Synchrotron SOLEIL, Division Expériences, Gif sur Yvette, France
+$^{2}$Centre de Biophysique Moléculaire, CNRS UPR4301, Orléans, France -- Synchrotron SOLEIL, Division Expériences, Gif sur Yvette, France
 %%
@@
 %%
-$^{33}$Montreal Neurological Institute, McGill University, Montreal, Canada
+$^{33}$Amazon, Seattle, USA
 %%
-$^{34}$Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany
+$^{34}$Montreal Neurological Institute, McGill University, Montreal, Canada
 %%
-$^{35}$Department of Computer Science, Grinnell College, IA, USA
+$^{35}$Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany
 %%
-$^{36}$Symerio, Palaiseau, France
+$^{36}$Department of Computer Science, Grinnell College, IA, USA
 %%
-$^{37}$Neural Information Processing Group, University of Tübingen, Germany
+$^{37}$Symerio, Palaiseau, France
+%%
+$^{38}$Neural Information Processing Group, University of Tübingen, Germany
 %%

### 2017-06-26 parse-board.py

@@ -44,6 +44,7 @@ affiliations = {
     "tpoisot" : "Département de Sciences Biologiques, Université de Montréal, Montréal, Canada",
     "ctb":  "Department of Population Health and Reproduction, University of California Davis, Davis, CA, USA",
     "opetchey" : "Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland",
+    "FedericoV" : "Amazon, Seattle, USA"
 }
 
 # Commented names have declined or not answered yet
@@ -51,9 +52,8 @@ chiefs = ["rougier", "khinsen"]
 editors = ["otizonaizit", "pdebuyl", "ctb", "ThomasA", "tpoisot",
 #          "emmanuelle"
            "karthik", "oliviaguest", "labarba"]
-reviewers = ["MehdiKhamassi", "benoit-girard", "vitay", "gdetor", "dmcglinn", "yoavram",
-#             "FedericoV",
-             "heplesser", "apdavison",
+reviewers = ["MehdiKhamassi", "benoit-girard", "vitay", "gdetor", "dmcglinn",
+             "yoavram",  "FedericoV", "heplesser", "apdavison",
              "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
              "damiendr", "delsuc", "soolijoo", "benureau", "rth",
 #             "ogrisel",

### 2017-06-26 authors.tex

@@
 %%
-\textbf{Vahid Rostami}$^{28\S}$,
+\textbf{Vahid Rostami}$^{28\S}$\href{http://orcid.org/0000-0002-3851-0220}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Guillaume Viejo}$^{33\S}$,
+\textbf{Federico Vaggi}$^{33\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Julien Vitay}$^{34\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
+\textbf{Guillaume Viejo}$^{34\S}$,
 %%
-\textbf{Anya Vostinar}$^{35\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
+\textbf{Julien Vitay}$^{35\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Roman Yurchak}$^{36\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+\textbf{Anya Vostinar}$^{36\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Tiziano Zito}$^{37\dagger}$\\
+\textbf{Roman Yurchak}$^{37\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Tiziano Zito}$^{38\dagger}$\\

### 2017-06-26 draft.tex

@@
 clinical and non-clinical biomedical investigation} is seen as a
-critical factor. Surprisingly, the computational sciences (in the broad
-sense) and computer sciences (in the strict sense) are no exception
+critical factor.
+The same remarks were recently issued for chemistry \citep{coudert:2017}.
+Surprisingly, the computational sciences (in the broad
+sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009}
 despite the fact they rely heavily on code and data, which should

### 2017-06-27 draft.tex
Fixed rep*bility terminology
A few uses in the introduction were in contradiction to the definitions given in the article.

@@
 and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
-behind such non-reproducibility are as diverse as the domains in which it occurs.
+behind such non-replicability are as diverse as the domains in which it occurs.
 In medicine, factors such as {\em study power and bias, the
@@
 have been highlighted as important causes \citep{ioannidis:2005}. 
-In psychology, non-reproducibility has been blamed on spurious p-values (p-hacking),
+In psychology, non-replicability has been blamed on spurious p-values (p-hacking),
 while in the biomedical sciences, \citep{iqbal:2016}
@@
 These low numbers only reflect the authors' success at running the code.
-They did not check for correctness of the code (i.e., does the code actually implement what is advertised in the paper), nor the replicability of the results (does each run lead to the same results as in the paper).
+They did not check for correctness of the code (i.e., does the code actually implement what is advertised in the paper), nor the reproducibility of the results (does each run lead to the same results as in the paper).
 One example of this problem can be found in \citet{topalidou:2015a} where they tried to replicate a computational neuroscience model.
@@
 At the educational and methodological levels, things have started to change with a
-growing literature on best practices for making code reproducible
+growing literature on best practices for making computations reproducible
 \citep{sandve:2013, crook:2013, wilson:2014, halchenko:2015, janz:2015,

### 2017-06-28 draft.tex

@@
 task every time we want to build a new model: either because we want to build
-on it, or because we want to compare to it. We also give replication tasks to
+on this previous work, or because we want to compare our new model to it. We also give replication tasks to
 M.Sc. students every year, as projects. In all these cases, we are confronted

### 2017-06-29 draft.tex
Inlcuded automated validation/verification into Outlook

@@
 software development platform than to integrate software reviewing
-into a publishing platform.
+into a publishing platform. Furthermore, tools that will allow for the automated
+validation of computational models and the automated verification of correctness are being actively 
+developed in the community (see e.g. 
+\href{https://github.com/scidash/sciunit}{SciUnit} or 
+\href{https://github.com/OpneSourceBrain/osb-model-validation}{OSB-model-validation}). 
+An integration of such frameworks, which would greatly enhance the 
+verification and validation process, seems feasible for the existing software 
+development platform,
 

### 2017-06-29 draft.tex
fix typos

--- 2017-06-28 draft.tex
@@
 Such policies help to ensure access to code and data in a well-defined format
-\citep{perkel:2016} but this will not guarantee reproducilbility nor
+\citep{perkel:2016} but this will not guarantee reproducibility nor
 correctness.
@@
 
-The possibility to imploy participants beyond the traditional group of
+The possibility to imply participants beyond the traditional group of
 authors, editors, and reviewers is particularly interesting in the

### 2017-06-30 draft.tex

--- 2017-06-28 draft.tex
@@
 
-Each submission takes the form of a pull request that is first
-considered by a member of the editorial board, who may decide to
-reject the submission if it does not respect the formal publication
-criteria of ReScience. A submission must contain
+Each submission is considered by a member of the editorial board, who
+may decide to reject the submission if it does not respect the formal
+publication criteria of ReScience. A submission must contain
 \begin{itemize}
@@
 \end{itemize}
-A complete submission therefore consists of both code and an accompanying
-article. Partial replications that cover only some of the results in the
+A complete submission therefore consists of both computer code and an
+accompanying article that are sent to ReScience in the form of a pull
+request, that is the process used on GitHub to submit a modification
+to a software project.
+%
+Partial replications that cover only some of the results in the
 original work are acceptable, but must be justified.\\

### 2017-06-30 draft.tex
fixed typos

--- 2017-06-29 draft.tex
@@
 Such policies help to ensure access to code and data in a well-defined format
-\citep{perkel:2016} but this will not guarantee reproducibility nor
+\citep{perkel:2016} but this will not guarantee reproducilbility nor
 correctness.
@@
 software development platform than to integrate software reviewing
-into a publishing platform.
+into a publishing platform. Furthermore, tools that will allow for the automated
+validation of computational models and the automated verification of correctness are being actively 
+developed in the community (see e.g. 
+\href{https://github.com/scidash/sciunit}{SciUnit} or 
+\href{https://github.com/OpenSourceBrain/osb-model-validation}{OSB-model-validation}). 
+An integration of such frameworks, which would greatly enhance the 
+verification and validation process, seems feasible for the existing software 
+development platform.
 

### 2017-07-07 draft.tex
Comment on divergent terminology.

@@
 and software in scientific research, and introduce the terminology we
-will use in the rest of this article:\\
+will use in the rest of this article. We note, however, that even the
+authors of this article are not all happy with this particular choice
+of terminology. \\
 

### 2017-07-07 draft.tex
Reformulation
Overall revision, with a more optimistic ending.

@@
 sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009}
-despite the fact they rely heavily on code and data, which should
-make them immune to the aforementioned problems.\\
+despite the fact they rely on code and data rather than on experimental observations,
+ which should make them immune to the aforementioned problems.\\
 
@@
 They did not check for correctness of the code (i.e., does the code actually implement what is advertised in the paper), nor the reproducibility of the results (does each run lead to the same results as in the paper).
-One example of this problem can be found in \citet{topalidou:2015a} where they tried to replicate a computational neuroscience model.
-Source code was not included in the supplementary section of the paper nor a link to a repository in the main text.
-When the replicators obtained code from the corresponding author, they found that it could not be compiled and would be difficult to repurpose.\\
+One example of this problem can be found in \citet{topalidou:2015a} where the authors tried to replicate results obtained from a computational neuroscience model.
+Source code was not available, neither as supplementary material to the paper nor in a public repository.
+When the replicators obtained the source code after contacting the corresponding author, they found that it could not be compiled and would be difficult to reuse for other purposes.\\
 
 Confronted with this problem, a small but growing number of journals and
-publishers have reacted by adopting explicit policies for data and software, for example the PLOS instructions on
+publishers have reacted by adopting explicit policies for data and software. Examples can be seen in the PLOS instructions on
 \href{http://journals.plos.org/plosone/s/materials-and-software-sharing}{Materials
@@
 on \href{http://journals.plos.org/plosone/s/data-availability}{Data Availability},
-and the
+and in the
 \href{https://elifesciences.org/elife-news/inside-elife-forking-software-used-elife-papers-github}{recent
@@
 and software in scientific research, and introduce the terminology we
-will use in the rest of this article. We note, however, that even the
-authors of this article are not all happy with this particular choice
-of terminology. \\
+will use in the rest of this article. We note, however, that there is
+some disagreement about this particular choice of terminology even
+among the authors of this article. \\
 
@@
 succesful. But this also means that our reviewers share a significant
-common background with the authors, and that background includes the
+common background with the authors, and that background often includes the
 software packages and programming languages adopted by their
@@
 verification and validation process, seems feasible for the existing software 
-development platform.
+development platforms.
 
@@
 successful and independent replication would be available right from
-the start. As illustrated in figure \ref{fig:coscience}, this would
+the start. As illustrated in Figure~\ref{fig:coscience}, this would
 require group A to contact group B and send them a draft of
@@
 and the incentive for doing replication so low that it would most
-probably prevent such collaborative work. At this point, CoScience is
-just a utopia for tomorrow.
+probably prevent such collaborative work. However, we hope that the
+current replication crisis will lead to a change in attitude, with
+an emphasis on the quality rather than the quantity of scientific ouput,
+with CoScience becoming the gold-standard approach to quality assurance.
 

### 2017-07-10 affiliations.tex
Updated authors (because of new submission)

@@
 %%
-$^{11}$Department of Computer Science, Humboldt-Universität zu Berlin
+$^{11}$Computational Engineering and Design, Faculty of Engineering and the Environment, University of Southampton, UK
 %%
-$^{12}$Friedman Brain Institute, Icahn School of Medicine at Mount Sinai, NY, USA
+$^{12}$Department of Computer Science, Humboldt-Universität zu Berlin
 %%
-$^{13}$Institute of Intelligent Systems and Robotics, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France
+$^{13}$Friedman Brain Institute, Icahn School of Medicine at Mount Sinai, NY, USA
 %%
-$^{14}$Experimental Psychology, University College London, UK
+$^{14}$Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France
 %%
-$^{15}$UCL Great Ormond St Institute of Child Health. University College London, London, UK
+$^{15}$Experimental Psychology, University College London, UK
 %%
-$^{16}$MRC Cognition and Brain Sciences Unit, Cambridge, UK
+$^{16}$UCL Great Ormond St Institute of Child Health. University College London, London, UK
 %%
-$^{17}$Independent scholar, Enschede, The Netherlands
+$^{17}$MRC Cognition and Brain Sciences Unit, Cambridge, UK
 %%
-$^{18}$Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands
+$^{18}$Independent scholar, Enschede, The Netherlands
 %%
-$^{19}$Department of Biology, College of Charleston, Charleston, SC, USA
+$^{19}$Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands
 %%
-$^{20}$Centre for Computer Science and Informatics Research, University of Hertfordshire, UK
+$^{20}$Department of Biology, College of Charleston, Charleston, SC, USA
 %%

### 2017-07-10 authors.tex
Reformulation for clarity and minor authorship corrections
* reformulated the Viejo et al. feedback, that was not clear (did it
refer to previous work, or new model?),
* changed my status from reviewer to editor
* corrected my affiliation (the name of the ISIR lab is officially in
French)
Updated authors (because of new submission)

@@
 %%
-\textbf{Damien Drix}$^{11\ddagger}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
+\textbf{Alexandra K. Diem}$^{11\S}$\href{http://orcid.org/0000-0003-1719-1942}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pierre Enel}$^{12\ddagger}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
+\textbf{Alexandra K. Diem}$^{11\S}$\href{http://orcid.org/0000-0003-1719-1942}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Benoît Girard}$^{13\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
+\textbf{Damien Drix}$^{12\ddagger}$\href{http://orcid.org/0000-0003-4107-5693}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Olivia Guest}$^{14\dagger}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pierre Enel}$^{13\ddagger}$\href{http://orcid.org/0000-0001-8983-6223}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Matt G. Hall}$^{15\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
+\textbf{Benoît Girard}$^{14\dagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Rafael Neto Henriques}$^{16\S}$,
+\textbf{Olivia Guest}$^{15\dagger}$\href{http://orcid.org/0000-0002-1891-0972}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Matt G. Hall}$^{16\ddagger}$\href{http://orcid.org/0000-0002-9530-5477}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Rafael Neto Henriques}$^{17\S}$,
 %%
@@
 %%
-\textbf{Mehdi Khamassi}$^{13\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
+\textbf{Mehdi Khamassi}$^{14\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Almar Klein}$^{17\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
+\textbf{Almar Klein}$^{18\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pietro Marchesi}$^{18\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pietro Marchesi}$^{19\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Dan McGlinn}$^{19\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
-%%
-\textbf{Christoph Metzner}$^{20\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
+\textbf{Dan McGlinn}$^{20\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%

### 2017-07-10 parse-board.py

@@ -6,9 +6,8 @@ affiliations = {
     "ThomasA" : "Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark",
     "ChristophMetzner" : "Centre for Computer Science and Informatics Research, University of Hertfordshire, UK",
     "apdavison" : "Unité de Neurosciences, Information et Complexité, Centre National de la Recherche Scientifique, Gif-sur-Yvette, France",
-    "MehdiKhamassi":  "Institute of Intelligent Systems and Robotics, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",
-    "benoit-girard" : "Institute of Intelligent Systems and Robotics, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",
-    
+    "MehdiKhamassi":  "Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",
+    "benoit-girard" : "Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",    
     "Vahidrostami": "Institute of Neuroscience \\& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany",
     "neuronalX" : "INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France",
     "pietromarchesi" : "Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands",
@@ -44,15 +43,16 @@ affiliations = {
     "tpoisot" : "Département de Sciences Biologiques, Université de Montréal, Montréal, Canada",
     "ctb":  "Department of Population Health and Reproduction, University of California Davis, Davis, CA, USA",
     "opetchey" : "Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland",
-    "FedericoV" : "Amazon, Seattle, USA"
+    "FedericoV" : "Amazon, Seattle, USA",
[…]

### 2017-07-10 affiliations.tex
Updated authors (because of new submission)

@@
 %%
-$^{18}$Independent scholar, Enschede, The Netherlands
+$^{18}$Department of Ecology and Evolution, University of Lausanne, Lausanne, Switzerland
 %%
-$^{19}$Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands
+$^{19}$Independent scholar, Enschede, The Netherlands
 %%
-$^{20}$Department of Biology, College of Charleston, Charleston, SC, USA
+$^{20}$Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands
 %%
-$^{21}$Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland
+$^{21}$Department of Biology, College of Charleston, Charleston, SC, USA
 %%
-$^{22}$Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany
+$^{22}$Centre for Computer Science and Informatics Research, University of Hertfordshire, UK
 %%
-$^{23}$Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
+$^{23}$Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland
 %%
-$^{24}$Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA
+$^{24}$Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany
 %%
-$^{25}$Department of Biology, Stanford University, Stanford, CA, USA
+$^{25}$Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
 %%
-$^{26}$Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK
+$^{26}$Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA
 %%
-$^{27}$Institute of Neurology, University College London, UK
+$^{27}$Department of Biology, Stanford University, Stanford, CA, USA
 %%
-$^{28}$Institute of Neuroscience \& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany
+$^{28}$Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK
 %%
-$^{29}$Department of Biology, University of Ottawa, Ottawa, Ontario, Canada
+$^{29}$Institute of Neurology, University College London, UK
 %%
-$^{30}$Department of Fisheries and Wildlife, Michigan State University, MI, USA
+$^{30}$Institute of Neuroscience \& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany
 %%
-$^{31}$Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France
+$^{31}$Department of Biology, University of Ottawa, Ottawa, Ontario, Canada
 %%
-$^{32}$Network Dynamics, Max Planck Institute for Dynamics and Self-Organization, Germany
+$^{32}$Department of Fisheries and Wildlife, Michigan State University, MI, USA
 %%
-$^{33}$Amazon, Seattle, USA
+$^{33}$Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France
 %%
-$^{34}$Montreal Neurological Institute, McGill University, Montreal, Canada
+$^{34}$Network Dynamics, Max Planck Institute for Dynamics and Self-Organization, Germany
 %%
-$^{35}$Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany
+$^{35}$Amazon, Seattle, USA
 %%
-$^{36}$Department of Computer Science, Grinnell College, IA, USA
+$^{36}$Montreal Neurological Institute, McGill University, Montreal, Canada
 %%
-$^{37}$Symerio, Palaiseau, France
+$^{37}$Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany
 %%
-$^{38}$Neural Information Processing Group, University of Tübingen, Germany
+$^{38}$Department of Computer Science, Grinnell College, IA, USA
+%%
+$^{39}$Symerio, Palaiseau, France
+%%
+$^{40}$Neural Information Processing Group, University of Tübingen, Germany
 %%

### 2017-07-10 authors.tex
Updated authors (because of new submission)

@@
 %%
-\textbf{Benoît Girard}$^{14\dagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
+\textbf{Benoît Girard}$^{14\dagger\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
+\textbf{Kamil S Jaron}$^{18\ddagger}$\href{http://orcid.org/0000-0003-1470-5450}{\includegraphics[width=8pt]{orcid}},
+%%
 \textbf{Mehdi Khamassi}$^{14\ddagger\S}$\href{http://orcid.org/0000-0002-2515-1046}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Almar Klein}$^{18\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
+\textbf{Almar Klein}$^{19\ddagger}$\href{http://orcid.org/0000-0002-9978-2780}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Pietro Marchesi}$^{19\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pietro Marchesi}$^{20\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Dan McGlinn}$^{20\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
+\textbf{Dan McGlinn}$^{21\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Owen L. Petchey}$^{21\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
+\textbf{Christoph Metzner}$^{22\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Hans Ekkehard Plesser}$^{22\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
+\textbf{Owen L. Petchey}$^{23\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Timothée Poisot}$^{23\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Hans Ekkehard Plesser}$^{24\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Karthik Ram}$^{24\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
+\textbf{Timothée Poisot}$^{25\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Yoav Ram}$^{25\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
+\textbf{Karthik Ram}$^{26\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Etienne Roesch}$^{26\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
+\textbf{Yoav Ram}$^{27\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Cyrille Rossant}$^{27\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
+\textbf{Etienne Roesch}$^{28\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Vahid Rostami}$^{28\S}$\href{http://orcid.org/0000-0002-3851-0220}{\includegraphics[width=8pt]{orcid}},
+\textbf{Cyrille Rossant}$^{29\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Aaron Shifman}$^{29\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
+\textbf{Vahid Rostami}$^{30\S}$\href{http://orcid.org/0000-0002-3851-0220}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Joseph Stachelek}$^{30\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
+\textbf{Aaron Shifman}$^{31\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marcel Stimberg}$^{31\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Joseph Stachelek}$^{32\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Frank Stollmeier}$^{32\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marcel Stimberg}$^{33\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Federico Vaggi}$^{33\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
+\textbf{Frank Stollmeier}$^{34\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Guillaume Viejo}$^{34\S}$,
+\textbf{Federico Vaggi}$^{35\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Julien Vitay}$^{35\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
+\textbf{Guillaume Viejo}$^{36\S}$,
 %%
-\textbf{Anya Vostinar}$^{36\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
+\textbf{Julien Vitay}$^{37\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Roman Yurchak}$^{37\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+\textbf{Anya Vostinar}$^{38\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Tiziano Zito}$^{38\dagger}$\\
+\textbf{Roman Yurchak}$^{39\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Tiziano Zito}$^{40\dagger}$\\

### 2017-07-10 parse-board.py

@@ -45,6 +45,7 @@ affiliations = {
     "opetchey" : "Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland",
     "FedericoV" : "Amazon, Seattle, USA",
     "akdiem" : "Computational Engineering and Design, Faculty of Engineering and the Environment, University of Southampton, UK",
+    "KamilSJaron" : "Department of Ecology and Evolution, University of Lausanne, Lausanne, Switzerland"
 }
 
 # Commented names have declined or not answered yet
@@ -52,10 +53,10 @@ chiefs = ["rougier", "khinsen"]
 editors = ["otizonaizit", "pdebuyl", "ctb", "ThomasA", "tpoisot",
 #          "emmanuelle"
            "benoit-girard", "karthik", "oliviaguest", "labarba"]
-reviewers = ["MehdiKhamassi", "vitay", "gdetor", "dmcglinn",
+reviewers = ["benoit-girard", "MehdiKhamassi", "vitay", "gdetor", "dmcglinn",
              "yoavram",  "FedericoV", "heplesser", "apdavison",
              "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
-             "damiendr", "delsuc", "soolijoo", "benureau", "rth",
+             "damiendr", "delsuc", "soolijoo", "benureau", "rth", "KamilSJaron",
 #             "ogrisel",
              "almarklein", "pietromarchesi", "anyaevostinar","ozancaglayan",
              "aaronshifman"]
@@ -89,6 +90,7 @@ with open("/Users/rougier/Development/Public/ReScience/ReScience.github.io/04-bo
         if match:
             name  = match.group("name")
             handle = match.group("handle")
+            print(name, handle)
         match = orcid_re.match(line)
         if match:
             orcid = match.group("orcid")

### 2017-07-10 draft.tex
Changed title (see #21)

@@
 
-\title{Long-Term Reproducibility through Replication:\\
-       the ReScience Initiative}
+\title{Sustainable computational science:\\
+       the ReScience initiative}
 \author{%
@@
 Surprisingly, the computational sciences (in the broad
-sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009}
-despite the fact they rely on code and data rather than on experimental observations,
- which should make them immune to the aforementioned problems.\\
+sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009,Manninen:2017} despite the fact they rely on code and data rather than on experimental observations, which should make them immune to the aforementioned problems.\\
 

### 2017-07-10 draft.tex
Minor edits for grammar, style, and colloquial language

@@
 Furthermore, if the original authors made mistakes in their original
-implementation, chances are that they will reproduce their mistakes.\\
+implementation, it seems likely that they will reproduce their mistakes
+in any re-implementation.\\
 % (just an educated guess, we have no data supporting this assertion)
@@
 perform computations based on these models and methods. If results
-depend on hard to control implementation details of the software,
+depend on hard-to-control implementation details of the software,
 their relation to the underlying models and methods becomes unclear
@@
 implementations that generate equivalent results, which makes serious
-mistakes in either software unlikely. Moreover, it shows that the
+mistakes in either implementation unlikely. Moreover, it shows that the
 second team was able to understand the description provided by the
@@
 
-Replication can be attempted both for reproducible and for
+Replication can be attempted for both reproducible and
 non-reproducible results. However, when an attempt to replicate
@@
 Performing a replication is a daunting task that is traditionally not well
-rewarded. Nevertheless, some people are actually willing to replicate
+rewarded. Nevertheless, some people are willing to replicate
 computational research. The motivations for doing so are very diverse (see Box 1). Students may want to familiarize themselves with
@@
 need a specific piece of code for a research project and therefore re-implement a published computational method. If these people write a brand new
-open source implementation of already published research, chances are that this new
-implementation may be of interest for other people as well, including
+open source implementation of already published research, it is likely that this new
+implementation will be of interest for other people as well, including
 the original authors. The question is where to publish such a replication. To the
-best of our knowledge, no major journal accepts publishing replications in computational science. This has been the main motivation for the
+best of our knowledge, no major journal accepts replications in computational science for publication. This was the main motivation for the
 creation of the ReScience journal (\href{https://rescience.github.io}{rescience.github.io}) by Konrad Hinsen and Nicolas P. Rougier in September 2015.\\
@@
 
-ReScience is an openly peer-reviewed journal that targets computational research
+ReScience is an openly-peer-reviewed journal that targets computational research
 and encourages the explicit replication of already published research. In order
@@
 computer graphics, with a majority in computational neuroscience. There is a
-strong bias towards successful replication (100\%) and experience has
+strong bias towards successful replication (100\%); experience has
 taught us that researchers are reluctant to publish failed replications, even when they can prove that the original work is wrong. For young researchers,
@@
 
-One of the specificities of the ReScience journal is its publishing
+One of the specificities of the ReScience journal is a publishing
 chain that is radically different from any other traditional
-scientific journals since ReScience lives on GitHub, a platform
+scientific journal, since ReScience lives on GitHub, a platform
 originally designed for collaborative software development. A
@@
 A complete submission therefore consists of both computer code and an
-accompanying article that are sent to ReScience in the form of a pull
-request, that is the process used on GitHub to submit a modification
-to a software project.
+accompanying article, which are sent to ReScience in the form of a pull
+request (the process used on GitHub to submit a proposed modification
+to a software project).
 %
@@
   \caption{\textbf{A} The ReScience publication chain starts from an
-    original research by authors A, published in a journal, in
+    original research article by authors A, published in a journal, in
     conference proceedings, or as a preprint. This article constitutes
-    the base material for authors B who attempt to replicate the work
+    the base material for authors B, who attempt to replicate the work
     based on its description. Success or failure to replicate is not a
@@
 form of a virtual machine), they represent an additional effort to
-authors and therefore discourage from submitting replication work to
+authors and therefore discourage them from submitting replication work to
 ReScience.  Our goal is to develop a set of recommendations for
@@
 system used by most scientific journals have motivated many
-experiments with various alternative reviewing processes. The variant
+experiments with alternative reviewing processes. The variant
 adopted by ReScience is similar to the ones used by F1000Research or
@@
 
-The possibility to imply participants beyond the traditional group of
+The possibility to involve participants beyond the traditional group of
 authors, editors, and reviewers is particularly interesting in the
@@
 (\href{https://github.com/ReScience/ReScience-submission/pull/28}{\#28}),
-a reviewer suggested asking the author of the original work for a
+a reviewer suggested asking the author of the original work for
 permission to re-use an image. The author intervened in the review and
@@
 Our experience shows that the GitHub platform provides excellent
-support for reviewing process, which is not surprising given that the
+support for the reviewing process, which is not surprising given that the
 review of a scientific article containing code is not fundamentally
 different from the review of code with accompanying documentation.
-One potential issue for other journals envisaging to adopt this
-platform is the necessity for submitting authors to have a basic
-knowledge of the version control system git and of the techniques of
+One potential issue for other journals envisaging adoption of this
+platform is the necessity that submitting authors have a basic
+knowledge of the version control system Git and of the techniques of
 collaborative software development. Given the code-centric nature of
 ReScience, this has not been a major problem for us, and the minor
-ones could be resolved by our editors providing technical assistance
+issues have been resolved by our editors providing technical assistance
 to authors. It is of course possible that potential authors are
@@
 in informed speculation about possible future evolutions in scientific
-publishing, in particular concerning replication work. We won't
+publishing, in particular concerning replication work. We will not
 discuss minor technical advances such as a better toolchain for
@@
 validation of computational models and the automated verification of correctness are being actively 
-developed in the community (see e.g. 
+developed in the community (see, for example, 
 \href{https://github.com/scidash/sciunit}{SciUnit} or 

### 2017-07-10 draft.tex
Added references to automation tools in the context of reducing the tediousness of recording scientist-computer interactions

@@
 In psychology, non-replicability has been blamed on spurious p-values (p-hacking),
-while in the biomedical sciences, \citep{iqbal:2016}
+while in the biomedical sciences \citep{iqbal:2016},
 a {\em lack of access to full datasets and detailed protocols for both
@@
 
-When \citep{collberg:2014, collberg:2015} decided to measure the extent of the problem
+When Collberg and colleagues \citep{collberg:2014, collberg:2015} decided to measure the extent of the problem
 precisely, they investigated the availability of code and data as well as {\em the extent to which this code would actually build with reasonable
@@
 They did not check for correctness of the code (i.e., does the code actually implement what is advertised in the paper), nor the reproducibility of the results (does each run lead to the same results as in the paper).
-One example of this problem can be found in \citet{topalidou:2015a} where the authors tried to replicate results obtained from a computational neuroscience model.
+One example of this problem can be found in \citet{topalidou:2015a}, in which the authors tried to replicate results obtained from a computational neuroscience model.
 Source code was not available, neither as supplementary material to the paper nor in a public repository.
@@
 stacks and the tediousness of recording all interactions between a
-scientist and a computer.  \citeauthor{Mesnard:2016} explain in
+scientist and a computer 
+\citep[although a number of recent tools have attempted to automate such recording, e.g.][]{guo:2011, davison:2012, murta:2015}.
+\citeauthor{Mesnard:2016} explain
 \citep{Mesnard:2016} how difficult it can be to reproduce a two-year
@@
 collection of recipes that have proven useful, see
-\citep{kitzes:2017}.
+\citet{kitzes:2017}.
 
@@
 with the requirements of research computing. This problem is nicely
-illustrated by \citep{Mesnard:2016} whose authors report trying to
+illustrated by \citet{Mesnard:2016} whose authors report trying to
 reproduce their own work performed two years earlier. Even though

### 2017-07-10 parse-board.py
Small fix in affiliation

@@ -5,7 +5,7 @@ affiliations = {
     "eroesch" : "Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK",
     "ThomasA" : "Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark",
     "ChristophMetzner" : "Centre for Computer Science and Informatics Research, University of Hertfordshire, UK",
-    "apdavison" : "Unité de Neurosciences, Information et Complexité, Centre National de la Recherche Scientifique, Gif-sur-Yvette, France",
+    "apdavison" : "Unité de Neurosciences, Information et Complexité, CNRS FRE 3693, Gif sur Yvette, France",
     "MehdiKhamassi":  "Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",
     "benoit-girard" : "Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",    
     "Vahidrostami": "Institute of Neuroscience \\& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany",
@@ -90,7 +90,7 @@ with open("/Users/rougier/Development/Public/ReScience/ReScience.github.io/04-bo
         if match:
             name  = match.group("name")
             handle = match.group("handle")
-            print(name, handle)
+#            print(name, handle)
         match = orcid_re.match(line)
         if match:
             orcid = match.group("orcid")

### 2017-07-10 draft.tex

@@
 stacks and the tediousness of recording all interactions between a
-scientist and a computer 
-\citep[although a number of recent tools have attempted to automate such recording, e.g.][]{guo:2011, davison:2012, murta:2015}.
-\citeauthor{Mesnard:2016} explain
+scientist and a computer.  \citeauthor{Mesnard:2016} explain 
 \citep{Mesnard:2016} how difficult it can be to reproduce a two-year

### 2017-07-10 affiliations.tex
Small fix in affiliation
Final author list + new ref for JOSS

@@
 %%
-$^{8}$Unité de Neurosciences, Information et Complexité, Centre National de la Recherche Scientifique, Gif-sur-Yvette, France
+$^{8}$Unité de Neurosciences, Information et Complexité, CNRS FRE 3693, Gif sur Yvette, France
 %%
@@
 %%
-$^{20}$Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands
+$^{20}$BioMediTech Institute and Faculty of Biomedical Sciences and Engineering, Tampere University of Technology, Tampere, Finland
 %%
-$^{21}$Department of Biology, College of Charleston, Charleston, SC, USA
+$^{21}$Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands
 %%
-$^{22}$Centre for Computer Science and Informatics Research, University of Hertfordshire, UK
+$^{22}$Department of Biology, College of Charleston, Charleston, SC, USA
 %%
-$^{23}$Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland
+$^{23}$Centre for Computer Science and Informatics Research, University of Hertfordshire, UK
 %%
-$^{24}$Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany
+$^{24}$Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland
 %%
-$^{25}$Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
+$^{25}$Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany
 %%
-$^{26}$Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA
+$^{26}$Département de Sciences Biologiques, Université de Montréal, Montréal, Canada
 %%
-$^{27}$Department of Biology, Stanford University, Stanford, CA, USA
+$^{27}$Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA
 %%
-$^{28}$Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK
+$^{28}$Department of Biology, Stanford University, Stanford, CA, USA
 %%
-$^{29}$Institute of Neurology, University College London, UK
+$^{29}$Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK
 %%
-$^{30}$Institute of Neuroscience \& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany
+$^{30}$Institute of Neurology, University College London, UK
 %%
-$^{31}$Department of Biology, University of Ottawa, Ottawa, Ontario, Canada
+$^{31}$Institute of Neuroscience \& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany
 %%
-$^{32}$Department of Fisheries and Wildlife, Michigan State University, MI, USA
+$^{32}$Department of Biology, University of Ottawa, Ottawa, Ontario, Canada
 %%
-$^{33}$Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France
+$^{33}$Department of Fisheries and Wildlife, Michigan State University, MI, USA
 %%
-$^{34}$Network Dynamics, Max Planck Institute for Dynamics and Self-Organization, Germany
+$^{34}$Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France
 %%
-$^{35}$Amazon, Seattle, USA
+$^{35}$Network Dynamics, Max Planck Institute for Dynamics and Self-Organization, Germany
 %%
-$^{36}$Montreal Neurological Institute, McGill University, Montreal, Canada
+$^{36}$Amazon, Seattle, USA
 %%
-$^{37}$Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany
+$^{37}$Montreal Neurological Institute, McGill University, Montreal, Canada
 %%
-$^{38}$Department of Computer Science, Grinnell College, IA, USA
+$^{38}$Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany
 %%
-$^{39}$Symerio, Palaiseau, France
+$^{39}$Department of Computer Science, Grinnell College, IA, USA
 %%
-$^{40}$Neural Information Processing Group, University of Tübingen, Germany
+$^{40}$Symerio, Palaiseau, France
+%%
+$^{41}$Neural Information Processing Group, University of Tübingen, Germany
 %%

### 2017-07-10 parse-board.py

@@ -45,7 +45,8 @@ affiliations = {
     "opetchey" : "Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland",
     "FedericoV" : "Amazon, Seattle, USA",
     "akdiem" : "Computational Engineering and Design, Faculty of Engineering and the Environment, University of Southampton, UK",
-    "KamilSJaron" : "Department of Ecology and Evolution, University of Lausanne, Lausanne, Switzerland"
+    "KamilSJaron" : "Department of Ecology and Evolution, University of Lausanne, Lausanne, Switzerland",
+    "TiinaManninen" : "BioMediTech Institute and Faculty of Biomedical Sciences and Engineering, Tampere University of Technology, Tampere, Finland"
 }
 
 # Commented names have declined or not answered yet
@@ -57,6 +58,7 @@ reviewers = ["benoit-girard", "MehdiKhamassi", "vitay", "gdetor", "dmcglinn",
              "yoavram",  "FedericoV", "heplesser", "apdavison",
              "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
              "damiendr", "delsuc", "soolijoo", "benureau", "rth", "KamilSJaron",
+             "TiinaManninen",
 #             "ogrisel",
              "almarklein", "pietromarchesi", "anyaevostinar","ozancaglayan",
              "aaronshifman"]

### 2017-07-10 authors.tex
Small fix in affiliation
updated author information

--- 2017-06-26 authors.tex
@@
 %%
-\textbf{Benoît Girard}$^{13\ddagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
+\textbf{Benoît Girard}$^{13\dagger\S}$\href{http://orcid.org/0000-0002-8117-7064}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Christoph Metzner}$^{20\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
+\textbf{Christoph Metzner}$^{20\ddagger\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
 %%

### 2017-07-10 parse-board.py
update to reviewer list

@@ -55,7 +55,7 @@ editors = ["otizonaizit", "pdebuyl", "ctb", "ThomasA", "tpoisot",
 reviewers = ["MehdiKhamassi", "benoit-girard", "vitay", "gdetor", "dmcglinn",
              "yoavram",  "FedericoV", "heplesser", "apdavison",
              "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
-             "damiendr", "delsuc", "soolijoo", "benureau", "rth",
+             "damiendr", "delsuc", "soolijoo", "benureau", "rth","ChristophMetzner"
 #             "ogrisel",
              "almarklein", "pietromarchesi", "anyaevostinar","ozancaglayan",
              "aaronshifman"]

### 2017-07-10 authors.tex

--- 2017-07-10 authors.tex
@@
 %%
-\textbf{Andrew Davison}$^{8\ddagger}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
+\textbf{Andrew P. Davison}$^{8\ddagger}$\href{http://orcid.org/0000-0002-4793-7541}{\includegraphics[width=8pt]{orcid}},
 %%
@@
 %%
-\textbf{Pietro Marchesi}$^{20\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
+\textbf{Tiina Manninen}$^{20\ddagger}$\href{http://orcid.org/0000-0002-0456-1185}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Dan McGlinn}$^{21\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
+\textbf{Pietro Marchesi}$^{21\ddagger}$\href{http://orcid.org/0000-0001-5955-6909}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Christoph Metzner}$^{22\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
+\textbf{Dan McGlinn}$^{22\ddagger}$\href{http://orcid.org/0000-0003-2359-3526}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Owen L. Petchey}$^{23\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
+\textbf{Christoph Metzner}$^{23\S}$\href{http://orcid.org/0000-0002-5933-2101}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Hans Ekkehard Plesser}$^{24\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
+\textbf{Owen L. Petchey}$^{24\S}$\href{http://orcid.org/0000-0002-7724-1633}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Timothée Poisot}$^{25\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
+\textbf{Hans Ekkehard Plesser}$^{25\ddagger}$\href{http://orcid.org/0000-0001-7843-5993}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Karthik Ram}$^{26\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
+\textbf{Timothée Poisot}$^{26\dagger}$\href{http://orcid.org/0000-0002-0735-5184}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Yoav Ram}$^{27\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
+\textbf{Karthik Ram}$^{27\dagger}$\href{http://orcid.org/0000-0002-0233-1757}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Etienne Roesch}$^{28\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
+\textbf{Yoav Ram}$^{28\ddagger}$\href{http://orcid.org/0000-0002-9653-4458}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Cyrille Rossant}$^{29\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
+\textbf{Etienne Roesch}$^{29\ddagger}$\href{http://orcid.org/0000-0002-8913-4173}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Vahid Rostami}$^{30\S}$\href{http://orcid.org/0000-0002-3851-0220}{\includegraphics[width=8pt]{orcid}},
+\textbf{Cyrille Rossant}$^{30\ddagger}$\href{http://orcid.org/0000-0003-2069-9093}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Aaron Shifman}$^{31\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
+\textbf{Vahid Rostami}$^{31\S}$\href{http://orcid.org/0000-0002-3851-0220}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Joseph Stachelek}$^{32\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
+\textbf{Aaron Shifman}$^{32\ddagger\S}$\href{http://orcid.org/0000-0003-2140-7590}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Marcel Stimberg}$^{33\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
+\textbf{Joseph Stachelek}$^{33\S}$\href{http://orcid.org/0000-0002-5924-2464}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Frank Stollmeier}$^{34\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
+\textbf{Marcel Stimberg}$^{34\ddagger}$\href{http://orcid.org/0000-0002-2648-4790}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Federico Vaggi}$^{35\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
+\textbf{Frank Stollmeier}$^{35\S}$\href{http://orcid.org/0000-0003-4858-0895}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Guillaume Viejo}$^{36\S}$,
+\textbf{Federico Vaggi}$^{36\ddagger}$\href{http://orcid.org/0000-0001-8100-158X}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Julien Vitay}$^{37\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
+\textbf{Guillaume Viejo}$^{37\S}$,
 %%
-\textbf{Anya Vostinar}$^{38\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
+\textbf{Julien Vitay}$^{38\ddagger\S}$\href{http://orcid.org/0000-0001-5229-2349}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Roman Yurchak}$^{39\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+\textbf{Anya Vostinar}$^{39\ddagger}$\href{http://orcid.org/0000-0001-7216-5283}{\includegraphics[width=8pt]{orcid}},
 %%
-\textbf{Tiziano Zito}$^{40\dagger}$\\
+\textbf{Roman Yurchak}$^{40\ddagger}$\href{http://orcid.org/0000-0002-2565-4444}{\includegraphics[width=8pt]{orcid}},
+%%
+\textbf{Tiziano Zito}$^{41\dagger}$\\

### 2017-07-10 draft.tex

--- 2017-07-10 draft.tex
@@
 
-\href{http://github.com/}{GitHub} is a commercial platform for
-collaborative software development based on the popular version
-control system \href{https://git-scm.com/}{git}. It offers unlimited
-free use to Open Source projects, defined as projects whose contents
-are accessible to everyone. All ReScience activities are organized
-around a few such Open Source projects hosted by GitHub. This is an
-unusual choice for a scientific journal, the only other journal hosted
-on GitHub being \href{http://joss.theoj.org/}{The Journal of Open
-Source Software}. In this section, we discuss the advantages and
-problems resulting from this choice, considering both technical and
-social issues.
+\href{http://github.com/}{GitHub} is a commercial platform for collaborative
+software development based on the popular version control system
+\href{https://git-scm.com/}{git}. It offers unlimited free use to Open Source
+projects, defined as projects whose contents are accessible to everyone. All
+ReScience activities are organized around a few such Open Source projects
+hosted by GitHub. This is an unusual choice for a scientific journal, the only
+other journal hosted on GitHub being The Journal of Open Source
+Software\citep{Smith:2017}. In this section, we discuss the advantages and
+problems resulting from this choice, considering both technical and social
+issues.
 

### 2017-07-10 parse-board.py
Rebuild PDF

@@ -58,7 +58,7 @@ reviewers = ["benoit-girard", "MehdiKhamassi", "vitay", "gdetor", "dmcglinn",
              "yoavram",  "FedericoV", "heplesser", "apdavison",
              "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
              "damiendr", "delsuc", "soolijoo", "benureau", "rth", "KamilSJaron",
-             "ChristophMetzner", "TiinaManninen",
+             "TiinaManninen", "ChristophMetzner",
 #             "ogrisel",
              "almarklein", "pietromarchesi", "anyaevostinar","ozancaglayan",
              "aaronshifman"]

### 2017-07-10 parse-board.py
Update parse-board.py
Adapted affiliation to give full lab name.

@@ -18,7 +18,7 @@ affiliations = {
     "mstimberg" : "Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France",
     "heplesser" : "Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany",
     "rth" : "Symerio, Palaiseau, France",
-    "delsuc" : "IGBMC, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France",
+    "delsuc" : "Institut de Génétique et de Biologie Moléculaire et Cellulaire, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France",
     "dmcglinn" : "Department of Biology, College of Charleston, Charleston, SC, USA",
     "labarba" : "Department of Mechanical and Aerospace Engineering, the George Washington University, Washington DC, USA",
     "pdebuyl" : "Instituut voor Theoretische Fysica, KU Leuven, Belgium -- PdB is a postdoctoral fellow of the Research Foundation -- Flanders (FWO)",

### 2017-07-11 authors-tag.py
PDF build

@@ -1,0 +1,23 @@
+chiefs = ["rougier", "khinsen"]
+editors = ["otizonaizit", "pdebuyl", "ctb", "ThomasA", "tpoisot",
+#          "emmanuelle"
+           "benoit-girard", "karthik", "oliviaguest", "labarba"]
+reviewers = ["benoit-girard", "MehdiKhamassi", "vitay", "gdetor", "dmcglinn",
+             "yoavram",  "FedericoV", "heplesser", "apdavison",
+             "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
+             "damiendr", "delsuc", "soolijoo", "benureau", "rth", "KamilSJaron",
+             "TiinaManninen",
+#             "ogrisel",
+             "almarklein", "pietromarchesi", "anyaevostinar","ozancaglayan",
+             "aaronshifman"]
+replicators = ["gviejo", "gdetor", "MehdiKhamassi", "benoit-girard", "opetchey",
+               "Vahidrostami", "jsta", "Fjanks", "ChristophMetzner", "vitay",
+               "akdiem", # "andruhamax",
+               "falex33", "aaronshifman", "RafaelNH"]
+
+authors = chiefs + editors + reviewers + replicators
+
+for author in authors:
+    print("@%s, " % author, end="")
+print()
+print(len(authors))

### 2017-07-11 parse-board.py

@@ -105,6 +105,7 @@ fullnames.sort(key=lambda s: s.split()[-1])
 fullnames = ["Nicolas P. Rougier", "Konrad Hinsen"] + fullnames
 
 
+txt_authors  = ""
 tex_authors  = ""
 tex_affiliations  = ""
 indexed_affiliations = collections.OrderedDict()
@@ -126,6 +127,7 @@ for i,name in enumerate(fullnames):
     else:
         index = 1+list(indexed_affiliations.values()).index(affiliation)
 
+    txt_authors += "%s; " % (name)
     tex_authors +=  "\\textbf{%s}" % (name)
     tex_authors +=  "$^{%d" % (index)
     if handle in editors or handle in chiefs:
@@ -152,3 +154,6 @@ with open("authors.tex", "w") as file:
 
 with open("affiliations.tex", "w") as file:
     file.write(tex_affiliations)
+
+with open("authors.txt", "w") as file:
+    file.write(txt_authors)

### 2017-07-11 draft.tex
Added failure to replicate case

@@
   \maketitle
-\begin{small}
+  \vspace{5mm}
   \noindent
-  \textbf{} \par
+  \textbf{Abstract.}
+  If computer science offers a large set of tools for prototyping, writing,
+  running, testing, validating, sharing and replicating results, computational
+  science still lags behind. In the best case, authors may provide the sources
+  of their research as a compressed archive and feel confident their research
+  is replicable. But this is not exactly true. Buckheit \& Donoho 1995
+  explained almost 20 years ago that, an article about computational result is
+  advertising, not scholarship. The actual scholarship is the full software
+  environment, code and data that produced the result. The computational part
+  in computational sciences implies the use of computers, operating systems,
+  tools, frameworks, libraries and data. This leads to such a large number of
+  combinations (taking into account the version for each component) that the
+  chances to have the exact same configuration as one of your colleagues are
+  nearly zero. This draws consequences in our respective computational
+  approaches in order to make sure that computational research can be actually
+  and faithfully replicated.
+  %
+  ReScience is a peer-reviewed journal that targets computational research and
+  encourages the explicit replication of already published research, promoting
+  new and open-source implementations in order to ensure that the original
+  research is reproducible. To achieve this goal, the whole publishing chain is
+  radically different from other traditional scientific journals. ReScience
+  lives on GitHub where each new implementation of a computational study is
+  made available together with comments, explanations and tests. Each
+  submission takes the form of a pull request that is publicly reviewed and
+  tested in order to guarantee that any researcher can re-use it. ReScience is
+  open and collaborative by design: everything can be modified.\\
+  % \begin{small}
+  % \vspace{10mm}
+
   \textbf{Keywords:} Open Science, Computational Science,
                      Reproducibility, Replicability, Journal, Publication
-\end{small}
-\vspace{10mm}
+  %\end{small}
+  %\vspace{10mm}
+  \vfill
 ]
 
+\clearpage
 \section*{Introduction}
@@
 Performing a replication is a daunting task that is traditionally not well
-rewarded. Nevertheless, some people are willing to replicate
-computational research. The motivations for doing so are very diverse (see Box 1). Students may want to familiarize themselves with
-a specific scientific domain, and acquire relevant practical experience by replicating important published work. Senior researchers may critically
-need a specific piece of code for a research project and therefore re-implement a published computational method. If these people write a brand new
-open source implementation of already published research, it is likely that this new
-implementation will be of interest for other people as well, including
-the original authors. The question is where to publish such a replication. To the
-best of our knowledge, no major journal accepts replications in computational science for publication. This was the main motivation for the
-creation of the ReScience journal (\href{https://rescience.github.io}{rescience.github.io}) by Konrad Hinsen and Nicolas P. Rougier in September 2015.\\
+rewarded. Nevertheless, some people are willing to replicate computational
+research. The motivations for doing so are very diverse (see Box 1). Students
+may want to familiarize themselves with a specific scientific domain, and
+acquire relevant practical experience by replicating important published
+work. Senior researchers may critically need a specific piece of code for a
+research project and therefore re-implement a published computational
+method. If these people write a brand new open source implementation of already
+published research, it is likely that this new implementation will be of
+interest for other people as well, including the original authors. The question
+is where to publish such a replication. To the best of our knowledge, no major
+journal accepts replications in computational science for publication. This was
+the main motivation for the creation of the ReScience journal
+(\href{https://rescience.github.io}{rescience.github.io}) by Konrad Hinsen and
+Nicolas P. Rougier in September 2015.\\
 
@@
 \item an explanation of why the authors think they have replicated the paper
-      (same figures, same graphics, same behavior, etc.),
+  (same figures, same graphics, same behavior, etc.) or why they have failed.
 \item a description of any difficulties encountered during the
@@
 
-For a submission to be accepted, both reviewers must consider it
-reproducible and a valid replication of the original work. As we
-explained earlier, this means that the reviewers
+For a successful submission (i.e. partial or full replication) to be accepted,
+both reviewers must consider it reproducible and a valid replication of the
+original work. As we explained earlier, this means that the reviewers
 \begin{itemize}
@@
 \item obtain the same results as indicated in the accompanying paper,
-\item consider these results sufficiently close to the ones reported in the original paper being replicated.
+\item consider these results sufficiently close to the ones reported in the
+  original paper being replicated.
 \end{itemize}
+
+For a failure to replicate submission to be accepted, we require extra steps.
+to be taken. In addition to scrutiny of the submission by reviewers and
+editors, we will try to contact the authors of the original research, and issue
+a challenge to the community to spot and report errors in the new implementation.
+If no errors are found, the submission will be accepted and the original
+research will be declared non-replicable.
+
 %

### 2017-07-11 draft.tex
abstract, small changes

@@
   \textbf{Abstract.}
-  If computer science offers a large set of tools for prototyping, writing,
-  running, testing, validating, sharing and replicating results, computational
-  science still lags behind. In the best case, authors may provide the sources
-  of their research as a compressed archive and feel confident their research
+  Computer science offers a large set of tools for prototyping, writing,
+  running, testing, validating, sharing and replicating results, however computational
+  science lags behind.
+  In the best case, authors may provide their source code as a compressed archive and they may feel confident their research
   is replicable. But this is not exactly true. Buckheit \& Donoho 1995
-  explained almost 20 years ago that, an article about computational result is
+  proposed more than 2 decades ago that, an article about computational results is
   advertising, not scholarship. The actual scholarship is the full software
-  environment, code and data that produced the result. The computational part
+  environment, code, and data that produced the result. The computational part
   in computational sciences implies the use of computers, operating systems,
-  tools, frameworks, libraries and data. This leads to such a large number of
-  combinations (taking into account the version for each component) that the
-  chances to have the exact same configuration as one of your colleagues are
-  nearly zero. This draws consequences in our respective computational
-  approaches in order to make sure that computational research can be actually
-  and faithfully replicated.
+  tools, frameworks, libraries, and data. This leads to a large number of
+  combinations thereof (taking into account the version for each component) that the
+  chances of having the exact same configuration as one of your colleagues are
+  practically zero. This has consequences for computational
+  approaches in order to make sure that computational research can be faithfully replicated.
   %
@@
   radically different from other traditional scientific journals. ReScience
-  lives on GitHub where each new implementation of a computational study is
-  made available together with comments, explanations and tests. Each
-  submission takes the form of a pull request that is publicly reviewed and
-  tested in order to guarantee that any researcher can re-use it. ReScience is
+  resides on GitHub where each new implementation of a computational study is
+  made available together with comments, explanations, and software tests. Each
+  submission takes the form of a ``pull request'' that is publicly reviewed and
+  tested in order to guarantee re-usability. ReScience is
   open and collaborative by design: everything can be modified.\\

### 2017-07-11 parse-board.py
Corrected doubled name in authors

@@ -52,30 +52,25 @@ affiliations = {
 # Commented names have declined or not answered yet
 chiefs = ["rougier", "khinsen"]
 editors = ["otizonaizit", "pdebuyl", "ctb", "ThomasA", "tpoisot",
-#          "emmanuelle"
            "benoit-girard", "karthik", "oliviaguest", "labarba"]
 reviewers = ["benoit-girard", "MehdiKhamassi", "vitay", "gdetor", "dmcglinn",
              "yoavram",  "FedericoV", "heplesser", "apdavison",
              "neuronalX", "piero-le-fou", "mstimberg", "rossant", "eroesch",
              "damiendr", "delsuc", "soolijoo", "benureau", "rth", "KamilSJaron",
-             "TiinaManninen", "ChristophMetzner",
-#             "ogrisel",
-             "almarklein", "pietromarchesi", "anyaevostinar","ozancaglayan",
-             "aaronshifman"]
+             "TiinaManninen", "ChristophMetzner", "almarklein", "pietromarchesi",
+             "anyaevostinar","ozancaglayan", "aaronshifman"]
 replicators = ["gviejo", "gdetor", "MehdiKhamassi", "benoit-girard", "opetchey",
                "Vahidrostami", "jsta", "Fjanks", "ChristophMetzner", "vitay",
-               "akdiem", # "andruhamax",
-               "falex33", "aaronshifman", "RafaelNH"]
+               "akdiem", "falex33", "aaronshifman", "RafaelNH"]
 
 
 # Adding names that are not part of the board
 board = {}
 board["Guillaume Viejo"] = ["gviejo", "---"]
-# board["Andrei Maksimov"] = ["andruhamax", "---"]
 board["Frédéric Alexandre"] = ["falex33", "0000-0002-6113-1878"]
 board["Rafael Neto Henriques"] = ["RafaelNH", "---"]
 board["Frank Stollmeier"] = ["Fjanks", "0000-0003-4858-0895"]
-board["Alexandra K. Diem"] = ["akdiem", "0000-0003-1719-1942"]
+# board["Alexandra K. Diem"] = ["akdiem", "0000-0003-1719-1942"]
 
 authors = list(set(editors+reviewers+replicators))
 fullnames = list(board.keys())

### 2017-07-13 draft.tex
make wording more formal #40

@@
 the original paper because I feel that working through code supplements to blog
-posts has really helped me learn how to science. I could have published my
-replication as a blog post but I wanted the exposure and permanency that goes
-along with journal articles. This was my first experience with formal
-replication. I think the review was useful because it forced me to consider how
-the replication would be used by people other than myself. I have not yet
-experienced any new interactions following publication. However, I did notify
-the author of the original implementation about the replication's
-publication. I think this may lead to future correspondence. The original
-author suggested that he would consider submitting his own replications to
+posts has really helped me learn the process of scientific analysis. I could 
+have published my replication as a blog post but I wanted the exposure and 
+permanency that goes along with journal articles. This was my first experience 
+with formal replication. I think the review was useful because it forced me to 
+consider how the replication would be used by people other than myself. I have 
+not yet experienced any new interactions following publication. However, I did 
+notify the author of the original implementation about the replication's 
+publication. I think this may lead to future correspondence. The original author suggested that he would consider submitting his own replications to
 ReScience in the future.\\

### 2017-07-13 draft.tex
Abstract rewrite

@@
   \textbf{Abstract.}
+  %
   Computer science offers a large set of tools for prototyping, writing,
-  running, testing, validating, sharing and replicating results, however computational
-  science lags behind.
-  In the best case, authors may provide their source code as a compressed archive and they may feel confident their research
-  is replicable. But this is not exactly true. Buckheit \& Donoho 1995
-  proposed more than 2 decades ago that, an article about computational results is
-  advertising, not scholarship. The actual scholarship is the full software
-  environment, code, and data that produced the result. The computational part
-  in computational sciences implies the use of computers, operating systems,
-  tools, frameworks, libraries, and data. This leads to a large number of
-  combinations thereof (taking into account the version for each component) that the
-  chances of having the exact same configuration as one of your colleagues are
-  practically zero. This has consequences for computational
-  approaches in order to make sure that computational research can be faithfully replicated.
+  running, testing, validating, sharing and replicating results, however
+  computational science lags behind.  In the best case, authors may provide
+  their source code as a compressed archive and they may feel confident their
+  research is reproducible. But this is not exactly true. James Buckheit and
+  David Donoho proposed more than 2 decades ago that an article about
+  computational results is advertising, not scholarship. The actual scholarship
+  is the full software environment, code, and data that produced the
+  result. This implies new workflows, in particular in peer-reviews. Existing
+  journals have been slow to adapt: source codes are rarely requested, hardly
+  ever actually executed to check that they produce the results advertised in
+  the article.
   %
@@
   new and open-source implementations in order to ensure that the original
-  research is reproducible. To achieve this goal, the whole publishing chain is
-  radically different from other traditional scientific journals. ReScience
-  resides on GitHub where each new implementation of a computational study is
-  made available together with comments, explanations, and software tests. Each
-  submission takes the form of a ``pull request'' that is publicly reviewed and
-  tested in order to guarantee re-usability. ReScience is
-  open and collaborative by design: everything can be modified.\\
-  % \begin{small}
-  % \vspace{10mm}
+  research can be replicated from its description. To achieve this goal, the
+  whole publishing chain is radically different from other traditional
+  scientific journals. ReScience resides on GitHub where each new
+  implementation of a computational study is made available together with
+  comments, explanations, and software tests.\\
 
@@
                      Reproducibility, Replicability, Journal, Publication
-  %\end{small}
   %\vspace{10mm}

### 2017-07-13 draft.tex
Added references from #39

@@
 \section*{Introduction}
-There is a replication crisis in Science. This crisis has been
-highlighted in fields as diverse as medicine \citep{ioannidis:2005},
-psychology \citep{nosek:2015}, the political sciences \citep{janz:2015},
-and recently in the biomedical sciences \citep{iqbal:2016}. The reasons
-behind such non-replicability are as diverse as the domains in which it occurs.
-In medicine, factors such as {\em study power and bias, the
-number of other studies on the same question, and importantly, the
-ratio of true to no relationships among the all relationships probed}
-have been highlighted as important causes \citep{ioannidis:2005}. 
-In psychology, non-replicability has been blamed on spurious p-values (p-hacking),
-while in the biomedical sciences \citep{iqbal:2016},
-a {\em lack of access to full datasets and detailed protocols for both
-clinical and non-clinical biomedical investigation} is seen as a
-critical factor.
-The same remarks were recently issued for chemistry \citep{coudert:2017}.
-Surprisingly, the computational sciences (in the broad
-sense) and computer sciences (in the strict sense) are no exception \citep{donoho:2009,Manninen:2017} despite the fact they rely on code and data rather than on experimental observations, which should make them immune to the aforementioned problems.\\
+There is a replication crisis in Science \citep{Baker:2016, Munaf:2017}. This
+crisis has been highlighted in fields as diverse as medicine
+\citep{ioannidis:2005}, psychology \citep{nosek:2015}, the political sciences
+\citep{janz:2015}, and recently in the biomedical sciences
+\citep{iqbal:2016}. The reasons behind such non-replicability are as diverse as
+the domains in which it occurs.  In medicine, factors such as {\em study power
+  and bias, the number of other studies on the same question, and importantly,
+  the ratio of true to no relationships among the all relationships probed}
+have been highlighted as important causes \citep{ioannidis:2005}.  In
+psychology, non-replicability has been blamed on spurious p-values (p-hacking),
+while in the biomedical sciences \citep{iqbal:2016}, a {\em lack of access to
+  full datasets and detailed protocols for both clinical and non-clinical
+  biomedical investigation} is seen as a critical factor.  The same remarks
+were recently issued for chemistry \citep{coudert:2017}.  Surprisingly, the
+computational sciences (in the broad sense) and computer sciences (in the
+strict sense) are no exception \citep{donoho:2009,Manninen:2017} despite the
+fact they rely on code and data rather than on experimental observations, which
+should make them immune to the aforementioned problems.\\
 

### 2017-07-13 draft.tex

@@
   research is reproducible. But this is not exactly true. James Buckheit and
-  David Donoho proposed more than 2 decades ago that an article about
+  David Donoho proposed more than two decades ago that an article about
   computational results is advertising, not scholarship. The actual scholarship
@@
 \href{https://elifesciences.org/elife-news/inside-elife-forking-software-used-elife-papers-github}{recent
-  annoucement} by eLife on forking (creating a linked copy of) software used in eLife papers to GitHub.
+  announcement} by eLife on forking (creating a linked copy of) software used in eLife papers to GitHub.
 Such policies help to ensure access to code and data in a well-defined format
@@
 \citeauthor{Mesnard:2016} explain
-\citep{Mesnard:2016} how difficult it can be to reproduce a two-year
-old computation even though all possible precautions were taken at the
+\citep{Mesnard:2016} how difficult it can be to reproduce a two-year-old
+computation even though all possible precautions were taken at the
 time to ensure reproducibility.  The most frequent obstacles are the
@@
 the field is a condition for judging if a replication is
-succesful. But this also means that our reviewers share a significant
+successful. But this also means that our reviewers share a significant
 common background with the authors, and that background often includes the

### 2017-07-24 affiliations.tex
PDF build
Minor affiliation correction for Thomas Arildsen

@@
 %%
-$^{3}$Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark
+$^{3}$Department of Electronic Systems, Technical Faculty of IT and Design, Aalborg University, Denmark
 %%
@@
 %%
-$^{9}$IGBMC, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France
+$^{9}$Institut de Génétique et de Biologie Moléculaire et Cellulaire, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France
 %%

### 2017-09-28 affiliations-overleaf.tex
Added necessary script for overleaf/F1000 sublmission

\affil[1]{INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France}
\affil[2]{Centre de Biophysique Moléculaire, CNRS UPR4301, Orléans, France -- Synchrotron SOLEIL, Division Expériences, Gif sur Yvette, France}
\affil[3]{Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark}
\affil[4]{Department of Mechanical and Aerospace Engineering, the George Washington University, Washington DC, USA}
\affil[5]{Department of Population Health and Reproduction, University of California Davis, Davis, CA, USA}
\affil[6]{Instituut voor Theoretische Fysica, KU Leuven, Belgium -- PdB is a postdoctoral fellow of the Research Foundation -- Flanders (FWO)}
\affil[7]{Laboratoire d'Informatique de l'Université du Maine (LIUM), Le Mans, France}
\affil[8]{Unité de Neurosciences, Information et Complexité, CNRS FRE 3693, Gif sur Yvette, France}
\affil[9]{Institut de Génétique et de Biologie Moléculaire et Cellulaire, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France}
\affil[10]{Department of Cognitive Sciences, University of California Irvine, USA}
\affil[11]{Computational Engineering and Design, Faculty of Engineering and the Environment, University of Southampton, UK}
\affil[12]{Department of Computer Science, Humboldt-Universität zu Berlin}
\affil[13]{Friedman Brain Institute, Icahn School of Medicine at Mount Sinai, NY, USA}
\affil[14]{Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France}
\affil[15]{Experimental Psychology, University College London, UK}
\affil[16]{UCL Great Ormond St Institute of Child Health. University College London, London, UK}
\affil[17]{MRC Cognition and Brain Sciences Unit, Cambridge, UK}
\affil[18]{Department of Ecology and Evolution, University of Lausanne, Lausanne, Switzerland}
\affil[19]{Independent scholar, Enschede, The Netherlands}
\affil[20]{BioMediTech Institute and Faculty of Biomedical Sciences and Engineering, Tampere University of Technology, Tampere, Finland}
\affil[21]{Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands}
\affil[22]{Department of Biology, College of Charleston, Charleston, SC, USA}
\affil[23]{Centre for Computer Science and Informatics Research, University of Hertfordshire, UK}
\affil[24]{Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland}
\affil[25]{Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany}
\affil[26]{Département de Sciences Biologiques, Université de Montréal, Montréal, Canada}
\affil[27]{Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA}
\affil[28]{Department of Biology, Stanford University, Stanford, CA, USA}
\affil[29]{Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK}
\affil[30]{Institute of Neurology, University College London, UK}
\affil[31]{Institute of Neuroscience \& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany}
\affil[32]{Department of Biology, University of Ottawa, Ottawa, Ontario, Canada}
\affil[33]{Department of Fisheries and Wildlife, Michigan State University, MI, USA}
\affil[34]{Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France}
\affil[35]{Network Dynamics, Max Planck Institute for Dynamics and Self-Organization, Germany}
\affil[36]{Amazon, Seattle, USA}
\affil[37]{Montreal Neurological Institute, McGill University, Montreal, Canada}
\affil[38]{Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany}
\affil[39]{Department of Computer Science, Grinnell College, IA, USA}
\affil[40]{Symerio, Palaiseau, France}
\affil[41]{Neural Information Processing Group, University of Tübingen, Germany}
\par

### 2017-09-28 draft.tex
Mid-sentence period removed
Attempt to move Fig. 1 closer to "Outlook" where it is referenced
Added necessary script for overleaf/F1000 sublmission

@@
   Computer science offers a large set of tools for prototyping, writing,
-  running, testing, validating, sharing and replicating results, however
+  running, testing, validating, sharing and reproducing results, however
   computational science lags behind.  In the best case, authors may provide
@@
 
-For a failure to replicate submission to be accepted, we require extra steps.
+For a failure to replicate submission to be accepted, we require extra steps
 to be taken. In addition to scrutiny of the submission by reviewers and
@@
 %\subsection*{An Utopia for Tomorrow}
-
-\begin{figure}
-  \includegraphics[width=1.0\columnwidth]{CoScience}
-  \caption{\textbf{A} The ReScience publication chain starts from an
-    original research article by authors A, published in a journal, in
-    conference proceedings, or as a preprint. This article constitutes
-    the base material for authors B, who attempt to replicate the work
-    based on its description. Success or failure to replicate is not a
-    criterion for acceptance or rejection, even though failure to
-    replicate requires more precaution to ensure this is not a
-    misunderstanding or a bug in the new code. After review, the
-    replication is published, and feedback is given to original
-    authors (and editors) to inform them the work has been replicated
-    (or not). \textbf{B} The CoScience proposal would require the
-    replication to happen \textit{before} the actual publication. In
-    case of failure, nothing will be published. In case of success,
-    the publication will be endorsed by authors A and authors B with
-    identified roles and will be certified as reproducible because it
-    has been replicated by an independent group.}
-  \label{fig:coscience}
-\end{figure}
 
@@
 
+\begin{figure}
+  \includegraphics[width=1.0\columnwidth]{CoScience}
+  \caption{\textbf{A} The ReScience publication chain starts from an
+    original research article by authors A, published in a journal, in
+    conference proceedings, or as a preprint. This article constitutes
+    the base material for authors B, who attempt to replicate the work
+    based on its description. Success or failure to replicate is not a
+    criterion for acceptance or rejection, even though failure to
+    replicate requires more precaution to ensure this is not a
+    misunderstanding or a bug in the new code. After review, the
+    replication is published, and feedback is given to original
+    authors (and editors) to inform them the work has been replicated
+    (or not). \textbf{B} The CoScience proposal would require the
+    replication to happen \textit{before} the actual publication. In
+    case of failure, nothing will be published. In case of success,
+    the publication will be endorsed by authors A and authors B with
+    identified roles and will be certified as reproducible because it
+    has been replicated by an independent group.}
+  \label{fig:coscience}
+\end{figure}
+
 \section*{Outlook}

### 2017-09-28 parse-board-overleaf.py

@@ -1,0 +1,155 @@
+import re
+import collections
+
+affiliations = {
+    "eroesch" : "Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK",
+    "ThomasA" : "Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark",
+    "ChristophMetzner" : "Centre for Computer Science and Informatics Research, University of Hertfordshire, UK",
+    "apdavison" : "Unité de Neurosciences, Information et Complexité, CNRS FRE 3693, Gif sur Yvette, France",
+    "MehdiKhamassi":  "Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",
+    "benoit-girard" : "Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France",    
+    "Vahidrostami": "Institute of Neuroscience \\& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany",
+    "neuronalX" : "INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France",
+    "pietromarchesi" : "Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands",
+    "vitay" :"Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany",
+    "rossant" : "Institute of Neurology, University College London, UK",
+    "soolijoo" : "UCL Great Ormond St Institute of Child Health. University College London, London, UK",
+    "oliviaguest" : "Experimental Psychology, University College London, UK",
+    "mstimberg" : "Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France",
[…]

### 2017-10-01 draft.tex
Adapted draft to PeerJ template (from overleaf)

@@
-\documentclass[a4paper,10pt, twocolumn]{article}
-
-% Wider margins (compared to default)
-\usepackage[margin=2.0cm]{geometry}
-
-% For misc. computations
+\documentclass[fleqn,10pt,lineno]{peerj}
 \usepackage{calc}
 \usepackage{enumitem}
-
-% English support (typography and hyphenation)
-\usepackage[american]{babel}
-\usepackage{csquotes}
-
-% For math
 \usepackage{amsmath}
@@
 \usepackage[utf8]{inputenc}
+\usepackage{graphicx}
+\usepackage{hyperref}
+% \usepackage{biblatex}
+% \bibliography{draft}
 
-% Color box
-\usepackage{tikz,lipsum,lmodern}
-\usepackage[most]{tcolorbox}
+\title{Sustainable computational science:\\the ReScience initiative}
+\author[1,$\dagger$,$\S$,$\star$]{Nicolas P. Rougier}
+\author[2,$\dagger$,$\star$]{Konrad Hinsen}
+\author[1,$\S$]{Frédéric Alexandre}
+\author[3,$\dagger$]{Thomas Arildsen}
+\author[4,$\dagger$]{Lorena Barba}
+\author[1,$\ddagger$]{Fabien C. Y. Benureau}
+\author[5,$\dagger$]{C. Titus Brown}
+\author[6,$\dagger$]{Pierre de Buyl}
+\author[7,$\ddagger$]{Ozan Caglayan}
+\author[8,$\ddagger$]{Andrew P. Davison}
+\author[9,$\ddagger$]{Marc André Delsuc}
+\author[10,$\ddagger$,$\S$]{Georgios Detorakis}
+\author[11,$\S$]{Alexandra K. Diem}
+\author[12,$\ddagger$]{Damien Drix}
+\author[13,$\ddagger$]{Pierre Enel}
+\author[14,$\dagger$,$\ddagger$,$\S$]{Benoît Girard}
+\author[15,$\dagger$]{Olivia Guest}
+\author[16,$\ddagger$]{Matt G. Hall}
+\author[17,$\S$]{Rafael Neto Henriques}
+\author[1,$\ddagger$]{Xavier Hinaut}
+\author[18,$\ddagger$]{Kamil S Jaron}
+\author[14,$\ddagger$,$\S$]{Mehdi Khamassi}
+\author[19,$\ddagger$]{Almar Klein}
+\author[20,$\ddagger$]{Tiina Manninen}
+\author[21,$\ddagger$]{Pietro Marchesi}
+\author[22,$\ddagger$]{Dan McGlinn}
+\author[23,$\ddagger$,$\S$]{Christoph Metzner}
+\author[24,$\S$]{Owen L. Petchey}
+\author[25,$\ddagger$]{Hans Ekkehard Plesser}
+\author[26,$\dagger$]{Timothée Poisot}
+\author[27,$\dagger$]{Karthik Ram}
+\author[28,$\ddagger$]{Yoav Ram}
+\author[29,$\ddagger$]{Etienne Roesch}
+\author[30,$\ddagger$]{Cyrille Rossant}
+\author[31,$\S$]{Vahid Rostami}
+\author[32,$\ddagger$,$\S$]{Aaron Shifman}
+\author[33,$\S$]{Joseph Stachelek}
+\author[34,$\ddagger$]{Marcel Stimberg}
+\author[35,$\S$]{Frank Stollmeier}
+\author[36,$\ddagger$]{Federico Vaggi}
+\author[37,$\S$]{Guillaume Viejo}
+\author[38,$\ddagger$,$\S$]{Julien Vitay}
+\author[39,$\ddagger$]{Anya Vostinar}
+\author[40,$\ddagger$]{Roman Yurchak}
+\author[41,$\dagger$]{Tiziano Zito}
+\affil[1]{INRIA Bordeaux Sud-Ouest Talence, France – Institut des Maladies Neurodégénératives, Université de Bordeaux, CNRS UMR 5293, Bordeaux, France – LaBRI, Université de Bordeaux, Bordeaux INP, CNRS UMR 5800, Talence, France}
+\affil[2]{Centre de Biophysique Moléculaire, CNRS UPR4301, Orléans, France -- Synchrotron SOLEIL, Division Expériences, Gif sur Yvette, France}
+\affil[3]{Department of Electronic Systems, Faculty of Engineering and Science, Aalborg University, Denmark}
+\affil[4]{Department of Mechanical and Aerospace Engineering, the George Washington University, Washington DC, USA}
+\affil[5]{Department of Population Health and Reproduction, University of California Davis, Davis, CA, USA}
+\affil[6]{Instituut voor Theoretische Fysica, KU Leuven, Belgium -- PdB is a postdoctoral fellow of the Research Foundation -- Flanders (FWO)}
+\affil[7]{Laboratoire d'Informatique de l'Université du Maine (LIUM), Le Mans, France}
+\affil[8]{Unité de Neurosciences, Information et Complexité, CNRS FRE 3693, Gif sur Yvette, France}
+\affil[9]{Institut de Génétique et de Biologie Moléculaire et Cellulaire, INSERM U964, CNRS UMR 7104, Université de Strasbourg, Illkirch, France}
+\affil[10]{Department of Cognitive Sciences, University of California Irvine, USA}
+\affil[11]{Computational Engineering and Design, Faculty of Engineering and the Environment, University of Southampton, UK}
+\affil[12]{Department of Computer Science, Humboldt-Universität zu Berlin}
+\affil[13]{Friedman Brain Institute, Icahn School of Medicine at Mount Sinai, NY, USA}
+\affil[14]{Institut des Systèmes Intelligent et de Robotique, Sorbonne Universités, UPMC Univ Paris 06, CNRS, Paris, France}
+\affil[15]{Experimental Psychology, University College London, UK}
+\affil[16]{UCL Great Ormond St Institute of Child Health. University College London, London, UK}
+\affil[17]{MRC Cognition and Brain Sciences Unit, Cambridge, UK}
+\affil[18]{Department of Ecology and Evolution, University of Lausanne, Lausanne, Switzerland}
+\affil[19]{Independent scholar, Enschede, The Netherlands}
+\affil[20]{BioMediTech Institute and Faculty of Biomedical Sciences and Engineering, Tampere University of Technology, Tampere, Finland}
+\affil[21]{Swammerdam Institute for Life Sciences, Center for Neuroscience, Faculty of Science, University of Amsterdam, Amsterdam, the Netherlands}
+\affil[22]{Department of Biology, College of Charleston, Charleston, SC, USA}
+\affil[23]{Centre for Computer Science and Informatics Research, University of Hertfordshire, UK}
+\affil[24]{Department of Evolutionary Biology and Environmental Studies, University of Zurich, Switzerland}
+\affil[25]{Faculty of Science and Technology, Norwegian University of Life Sciences, Aas, Norway -- Institute of Neuroscience and Medicine (INM-6), Jülich Research Centre, Jülich, Germany}
+\affil[26]{Département de Sciences Biologiques, Université de Montréal, Montréal, Canada}
+\affil[27]{Berkeley Institute for Data Science, University of California Berkeley, Berkeley, CA, USA}
+\affil[28]{Department of Biology, Stanford University, Stanford, CA, USA}
+\affil[29]{Centre for Integrative Neuroscience, School of Psychology, University of Reading, UK}
+\affil[30]{Institute of Neurology, University College London, UK}
+\affil[31]{Institute of Neuroscience \& Medicine (INM-6) and Institute for Advanced Simulation (IAS-6) -- JARA-Brain Institute I (INM-10), Jülich Research Center, Jülich, Germany}
+\affil[32]{Department of Biology, University of Ottawa, Ottawa, Ontario, Canada}
+\affil[33]{Department of Fisheries and Wildlife, Michigan State University, MI, USA}
+\affil[34]{Sorbonne Universités, UPMC Univ Paris 06, INSERM, CNRS, Institut de la Vision, Paris, France}
+\affil[35]{Network Dynamics, Max Planck Institute for Dynamics and Self-Organization, Germany}
+\affil[36]{Amazon, Seattle, USA}
+\affil[37]{Montreal Neurological Institute, McGill University, Montreal, Canada}
+\affil[38]{Professorship for Artificial Intelligence, Department of Computer Science, Chemnitz University of Technology, Chemnitz, Germany}
+\affil[39]{Department of Computer Science, Grinnell College, IA, USA}
+\affil[40]{Symerio, Palaiseau, France}
+\affil[41]{Neural Information Processing Group, University of Tübingen, Germany}
+\affil[$^{\star}$]{ReScience co-founder}
+\affil[$^{\dagger}$]{ReScience editor}
+\affil[$^{\ddagger}$]{ReScience reviewer}
+\affil[$^{\S}$]{ReScience author}
+\corrauthor[1]{Nicolas P. Rougier}{Nicolas.Rougier@inria.fr}
 
-% Better default font (Libertine and Inconsolata)
-\usepackage[ttscale=.875]{libertine}
-\usepackage[scaled=0.96]{zi4}
-
-%% \usepackage{mathspec}
-%% \setmainfont{Minion Pro Cond}
-%% \setmathsfont(Digits,Greek,Latin)[Numbers={Proportional}]{Minion Pro}
-%% \setmathrm{Minion Pro}
-%% \setsansfont{MyriadPro-Cond}
-
-\usepackage{nicefrac}
-
-% Biber
-\usepackage[backend=biber,
-            style=apa,
-%            maxcitenames=3,
-%            uniquelist=false,
-%            maxbibnames=99,
-%            apabackref=false,
-            apamaxprtauth=99,
-            natbib=true]{biblatex}
-\DeclareLanguageMapping{american}{american-apa}
-
-% Graphics
-\usepackage{graphicx}
-
-% Figure caption
-\usepackage[labelsep=period]{caption}
-\renewcommand{\captionfont}{\small\sffamily}
-\renewcommand{\captionlabelfont}{\small\sffamily\bfseries}
-
-% Hyperref
-\usepackage{xcolor}
-\definecolor{blendedblue}{rgb}{0.2, 0.2, 0.6}
-\definecolor{blendedred}{rgb}{0.8, 0.2, 0.2}
-\usepackage[bookmarks=true,
-            breaklinks=true,
-            pdfborder={0 0 0},
-            citecolor=blendedblue,
-            colorlinks=true,
-            linkcolor=blendedblue,
-            urlcolor=blendedblue,
-            citecolor=blendedblue,
-            linktocpage=false,
-            hyperindex=true,
-            linkbordercolor=white]{hyperref}
-\hypersetup{colorlinks=true}
-
-% Bibliography file
-\bibliography{draft.bib}
-
-% Headers
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-% \fancyhf{}
-\rhead{\footnotesize \sf page \thepage}
-\lhead{\footnotesize \sf Rougier, Hinsen et al. 2017
-       \textbullet~The ReScience Initiative}
-\rfoot{}
-\cfoot{}
-\lfoot{}
-
-\makeatletter
-\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
-\begin{flushleft}
-  \textbf{\huge\@title\\}
-  \vspace{5mm}
-  \@author
-\end{flushleft}\egroup
-}
-\makeatother
-
-%% \newtcbox{\orcid}{enhanced,nobeforeafter,tcbox raise base,boxrule=0.4pt,top=0mm,bottom=0mm,
-%%   right=0mm,left=4mm,arc=1pt,boxsep=2pt,before upper={\vphantom{dlg}},
-%%   colframe=green!50!black,coltext=green!25!black,colback=green!10!white,
-%%   overlay={\begin{tcbclipinterior}\fill[green!75!blue!50!white] (frame.south west)
-%%     rectangle node[text=white,font=\sffamily\bfseries\tiny,rotate=0] {ID} ([xshift=4mm]frame.north west);\end{tcbclipinterior}}}
-
-\newcommand{\hgap}{\hspace{1mm}}
-
-\usepackage{tikz}
-\usetikzlibrary{positioning,shapes,shadows,arrows}
-\newcommand{\orcid}[1]{
-    \tikz[baseline=-0.5ex]{ 
-        \tikzset{lib/.style={
-            rectangle split,
-            rectangle split parts=2,
-            rectangle split horizontal,
-            rectangle split part fill={green!75!blue!50!white,green!10!white},
-            rectangle split draw splits=false,
-            rounded corners=1pt,
-            rectangle split part align={right,right},
-            draw=green!50!black,
-            minimum height=8pt}
-        }
-        \node[lib] (var){
-        \nodepart[text=green!25!black]{two} \footnotesize \href{http://orcid.org/#1}{#1}};
-        \node[text=white,font=\sffamily\bfseries\footnotesize,rotate=0] at ([xshift=6pt]var.west) {ID};
-    }
-}
-
-\title{Sustainable computational science:\\
-       the ReScience initiative}
-\author{%
-  \begin{small}
-    \input{authors.tex}
-  \end{small}
-\begin{footnotesize}
-  \vspace{2mm}
-  \input{affiliations.tex}
-  \vspace{2mm}
-  $^{\star}$ReScience co-founder
-  $^{\dagger}$ReScience editor
-  $^{\ddagger}$ReScience reviewer
-  $^{\S}$ReScience author\\
-  Corresponding author:
-            \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
-  \end{footnotesize}
-}
-
-\date{}
-
-\begin{document}
-
-\twocolumn[
-  \maketitle
-  \vspace{5mm}
-  \noindent
-  \textbf{Abstract.}
-  %
+\begin{abstract}
   Computer science offers a large set of tools for prototyping, writing,
@@
   ever actually executed to check that they produce the results advertised in
-  the article.
-  %
-  ReScience is a peer-reviewed journal that targets computational research and
-  encourages the explicit replication of already published research, promoting
-  new and open-source implementations in order to ensure that the original
-  research can be replicated from its description. To achieve this goal, the
-  whole publishing chain is radically different from other traditional
-  scientific journals. ReScience resides on GitHub where each new
+  the article.  ReScience is a peer-reviewed journal that targets computational
+  research and encourages the explicit replication of already published
+  research, promoting new and open-source implementations in order to ensure
+  that the original research can be replicated from its description. To achieve
+  this goal, the whole publishing chain is radically different from other
+  traditional scientific journals. ReScience resides on GitHub where each new
   implementation of a computational study is made available together with
-  comments, explanations, and software tests.\\
+  comments, explanations, and software tests.
+\end{abstract}
 
-  \textbf{Keywords:} Open Science, Computational Science,
-                     Reproducibility, Replicability, Journal, Publication
-  %\vspace{10mm}
-  \vfill
-]
+\begin{document}
 
-\clearpage
+\flushbottom
+\maketitle
+\thispagestyle{empty}
+
 \section*{Introduction}
@@
 
-When Collberg and colleagues \citep{collberg:2014, collberg:2015} decided to measure the extent of the problem
+When Collberg and colleagues \citep{collberg:2016} decided to measure the extent of the problem
 precisely, they investigated the availability of code and data as well as {\em the extent to which this code would actually build with reasonable
@@
 
-\begin{tcolorbox}[breakable, pad at break*=1mm,
-                  colback=black!2.5, arc=0pt, outer arc=0pt, boxrule=.25pt]
-\begin{footnotesize}
+\begin{small}
 \textbf{Box 1.} Authors having  published in Rescience explain their motivation.\\
@@
 progress for all of us. \par
-\end{footnotesize}
-\end{tcolorbox}
+\end{small}
 
@@
 \begin{figure}
-  \includegraphics[width=1.0\columnwidth]{CoScience}
+  \includegraphics[width=0.75\columnwidth]{CoScience}
   \caption{\textbf{A} The ReScience publication chain starts from an
@@
 
-% -> Computational vs Experimental: ReScience X (Etienne Roesch)
+% -------------------------------------------------------------- References ---
 
-% -------------------------------------------------------------- References ---
-\renewcommand*{\bibfont}{\footnotesize}
-\printbibliography[title=References]
+\bibliography{draft}
 

### 2017-10-01 parse-csv.py

@@ -1,0 +1,9 @@
+import csv
+
+reader = csv.reader(open("authors.csv"))
+for row in reader:
+     for i,field in enumerate(row):
+          if i < len(row)-1:
+               print(field.strip(), end=", ")
+          else:
+               print(field.strip(), end="\n")

### 2017-11-07 replies_to_reviewers.md
Changes in reply to reviewer 2

# Replies to the reviewers' comments

## In reply to reviewer 1

## In reply to reviewer 2

We thank the reviewer for his enthusiastic comments, and we would be
happy to welcome him as a contributor to ReScience.

We have corrected the name of Jonathan Buckheit.

### 2017-11-08 replies_to_reviewers.md
Reproducibility of software environments
In reply to reviwer #1

@@
 ## In reply to reviewer 1
+
+We thank the reviewer for the in-depth examination of our work and for his useful suggestions for the future evolution of ReScience.
+
+Concerning what the reviewer calls a defeatist attitude towards computational reproducibility, that is not at all how we see our approach.
+The manuscript focuses on reporting our experiences with ReScience.
+Concerning reproducibility, we note that having it verified by reviewers is not sufficient.
+We are not aware of any practical experience demonstrating that some other approach is efficient, which is why we consider the reproducibility of software environments an unsolved problem.
+Many ideas are being explored at the moment, including containerization as the reviewer mentions.
+The effectiveness of these ideas cannot be judged yet.
+Nobody knows, for example, if five years from now, the then-current version Docker will still be able to handle today's container images.
+We see our attitude not as defeatist, but as prudent.
+Many of the authors are contributing to the development and evaluation of new ideas, and we will certainly try some of them out in the context of ReScience.
+
+We have reworded some of our statements to make clearer that our doubts about reproducibility apply only to today's state of the start.
+We have also added a new paragraph on the reproducibility of software environments to the Outlook section.
 

### 2017-11-08 draft.tex
Changes in reply to reviewer 2
Reproducibility of software environments
In reply to reviwer #1

--- 2017-09-28 draft.tex
@@
   their source code as a compressed archive and they may feel confident their
-  research is reproducible. But this is not exactly true. James Buckheit and
+  research is reproducible. But this is not exactly true. Jonathan Buckheit and
   David Donoho proposed more than two decades ago that an article about
@@
 authors that represent a workable compromise between reproducibility
-and implementation effort.\\
+and implementation effort. These recommendations will evolve over time,
+and we hope that with improving technology we will ultimately reach full
+reproducibility over a few decades.\\
 
@@
 did not escape the many problems one can face when trying to re-run a
-piece of code. As a consequence, the code newly produced for ReScience
-will likely cease to be functional at some point in the future.
-Therefore, the long-term value of a ReScience publication is not the
-actual code but the accompanying article. The combination of the
+piece of code. As a consequence, code that is written for ReScience
+today will likely cease to be functional at some point in the future.
+The long-term value of a ReScience publication lies not just in the
+actual code but also in the accompanying article. The combination of the
 original article and the replication article provide a complete and
@@
 
+% -> Reproducible software environments
+
+A fundamental technical issue is the difficulty of archiving or
+accurately describing the software environments in which computational
+scientists perform their work. A publication should be accompanied by
+both a human-readable description of this environment and an
+executable binary form. The human-readable description allows an
+inspection of the versions of all software packages that were used,
+for example to check for the impact of bugs that become known only
+after a study was published. The executable version enables other
+scientists to re-run the analyses and inspect intermediate
+results. Ideally, the human-readable description would permit
+rebuilding the executable version, in the same way that software
+source code permits rebuilding executable binaries. This approach is
+pursued for example by the package manager Guix \citep{Courtes:2015}.
+A more limited but still useful implementation of the same idea exists
+in the form of the conda package manager
+\citep{conda}. Containerization, as implemented e.g. by Docker
+\citep{docker} is currently much discussed, but provides only the
+executable version without a human-readable description. Moreover, the
+long-term stability of the container file format remains to be
+evaluated. History has shown that long-term stability in computing
+technology is achieved only by conventions for which it is a design
+priority, for example the Java Virtual Machine \citep{JVM}. Docker, on
+the contrary, is developed as a deployment technology with no ambition
+towards long-term archiving.
+
 % -> Long term storage: Software Heritage

### 2017-11-08 replies_to_reviewers.md
Correct description of the Github pricing model
In reply to reviewer #1
What replication authors are allowed to use
In reply to reviewer #1

@@
 
+We have corrected our description of the Github pricing model, referring to public projects rather than Open Source projects.
+
+We have also added a sentence stating that replication authors should base their work exclusively on the contents of the original article.
+In practice, we have not yet encountered a case where code for the original article was available.
+
 ## In reply to reviewer 2

### 2017-11-08 draft.tex
Correct description of the Github pricing model
In reply to reviewer #1
What replication authors are allowed to use
In reply to reviewer #1

@@
 work, ReScience does not allow authors to submit replications of their
-own research, nor the research of close collaborators. Mistakes in the
+own research, nor the research of close collaborators. Moreover,
+replication work should be based exclusively on the originally
+published paper, although exceptions are admitted if properly documented
+in the replication article. Mistakes in the
 implementation of computational models and methods are often due to
@@
 software development based on the popular version control system
-\href{https://git-scm.com/}{git}. It offers unlimited free use to Open Source
+\href{https://git-scm.com/}{git}. It offers unlimited free use to public
 projects, defined as projects whose contents are accessible to everyone. All

### 2017-11-09 replies_to_reviewers.md
Fixed two typos

@@
 The effectiveness of these ideas cannot be judged yet.
-Nobody knows, for example, if five years from now, the then-current version Docker will still be able to handle today's container images.
+Nobody knows, for example, if five years from now, the then-current version of Docker will still be able to handle today's container images.
 We see our attitude not as defeatist, but as prudent.
@@
 
-We have reworded some of our statements to make clearer that our doubts about reproducibility apply only to today's state of the start.
+We have reworded some of our statements to make clearer that our doubts about reproducibility apply only to today's state of the art.
 We have also added a new paragraph on the reproducibility of software environments to the Outlook section.

### 2017-11-09 draft.tex
Some more details on conda

@@
 A more limited but still useful implementation of the same idea exists
-in the form of the conda package manager
-\citep{conda}. Containerization, as implemented e.g. by Docker
-\citep{docker} is currently much discussed, but provides only the
-executable version without a human-readable description. Moreover, the
-long-term stability of the container file format remains to be
+in the form of the conda package manager \citep{conda}, which uses a
+so-called environment file to describe and reconstruct environments.
+The main limitation compared to Guix is that the packages that make up
+a conda environment are themselves not reproducible. For example, a
+conda environment file does not state which compiler versions were
+used to build a package.
+
+Containerization, as implemented e.g. by Docker \citep{docker} is
+currently much discussed, but provides only the executable version
+without a human-readable description. Moreover, the long-term
+stability of the container file format remains to be
 evaluated. History has shown that long-term stability in computing

### 2017-11-09 draft.tex
A few words on robustness

@@
 successful. But this also means that our reviewers share a significant
-common background with the authors, and that background often includes the
-software packages and programming languages adopted by their
+common background with the authors, and that background often includes
+the software packages and programming languages adopted by their
 community.  In particular, if both authors and reviewers have
@@
 form of a virtual machine), they represent an additional effort to
-authors and therefore discourage them from submitting replication work to
-ReScience.  Our goal is to develop a set of recommendations for
-authors that represent a workable compromise between reproducibility
-and implementation effort. These recommendations will evolve over time,
-and we hope that with improving technology we will ultimately reach full
-reproducibility over a few decades.\\
+authors and therefore discourage them from submitting replication work
+to ReScience. Moreover, the evaluation of \textit{de-facto}
+reproducibility (``works on my machine'') by reviewers is useful as
+well, because it tests the robustness of the code under small
+variations in the computational environments that are inevitable in
+real life. Our goal is to develop a set of recommendations for authors
+that represent a workable compromise between reproducibility,
+robustness, and implementation effort. These recommendations will
+evolve over time, and we hope that with improving technology we will
+ultimately reach full reproducibility over a few decades.\\
 

### 2017-11-09 draft.tex
Missing references and finishing touches

@@
 evaluated. History has shown that long-term stability in computing
-technology is achieved only by conventions for which it is a design
-priority, for example the Java Virtual Machine \citep{JVM}. Docker, on
-the contrary, is developed as a deployment technology with no ambition
-towards long-term archiving.
+technology is achieved only by technology for which it is a design
+priority, as in the case of the Java Virtual Machine
+\citep{JVM}. Docker, on the contrary, is promoted as a deployment
+technology with no visible ambition towards archiving of computational
+environments.
 

### 2017-11-09 draft.tex
Mention popularity of Python and R
Mini-statistics on the review process
Update some numbers

@@
 to provide the largest possible benefit to the scientific community, replications are
-required to be reproducible and open-source. In less than two years of existence, 12
-articles have been published and 3 are currently under review
+required to be reproducible and open-source. In two years of existence, 17
+articles have been published and 4 are currently under review
 (\href{https://github.com/ReScience/ReScience-submission/pull/20}{\#20},
-\href{https://github.com/ReScience/ReScience-submission/pull/27}{\#27},
-\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#30}). The
+\href{https://github.com/ReScience/ReScience-submission/pull/27}{\#39},
+\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#41},
+\href{https://github.com/ReScience/ReScience-submission/pull/30}{\#43}). The
 editorial board covers a wide range of computational sciences (see
@@
 are computational neuroscience, neuroimaging, computational ecology and
-computer graphics, with a majority in computational neuroscience. There is a
+computer graphics, with a majority in computational neuroscience. The most
+popular programming languages are Python and R. The review process takes about 100~days on average and involves about 50~comments. There is a
 strong bias towards successful replication (100\%); experience has

### 2017-11-10 replies_to_reviewers.md
Completed replies to reviewer #1

@@
 
+We do not discuss continuous analysis because ReScience remains a traditional journal in publishing "finished" articles with a time stamp and a DOI.
+Continuous analysis is part of a different line of improving on the current publishing model that proposes to replace static articles by dynamic and open development processes.
+This is an interesting idea but so far in a far more experimental state than any of the innovations in ReScience.
+ReScience repositories being open, anyone is free to base a continuous analysis project on a replication published in ReScience, and we would be happy to support such attempts, but it is not in the focus of our own work for the near future.
+
 We have corrected our description of the Github pricing model, referring to public projects rather than Open Source projects.
@@
 In practice, we have not yet encountered a case where code for the original article was available.
+
+The reviewer's proposal of a data-driven summary of ReScience operations is interesting but we do not wish to attempt any form of statistical analysis on a dataset of by now 17 entries.
+We did add a sentence stating the average duration and length (in numbers of comments) of the review process, but any more sophisticated analysis would be premature at this time.
 
